
```{r}
# Load relevant libraries 
library('dplyr')
library('corrplot')
library('writexl')
library('readxl')
library('seqinr')
library('ggplot2')
library('gridExtra')
library('ggfortify')
library('pheatmap')
library('Biostrings')
library('tidyverse')
library('igraph')
library('RColorBrewer')
```

```{r}
Plates22and27_RPKs <- read_xlsx('Plates22and27_Combined_df.xlsx')
Plates22and27_RPKs <- Plates22and27_RPKs[,1:63]
Plate23_RPKs <- read_xlsx('Plate23_BITE_BothTimepoints_Seropositive_RPKs_df.xlsx')
Plate28_RPKs <- read_xlsx('Plate28_Mali_BothTimepoints_Seropositive_RPKs_df.xlsx')
```

```{r}
combined <- Plates22and27_RPKs %>%
  full_join(Plate23_RPKs, by = "id") %>%
  full_join(Plate28_RPKs, by = "id")

plate23_cols <- setdiff(names(Plate23_RPKs), "id")

combined <- combined %>%
  mutate(across(all_of(plate23_cols), ~ replace_na(., 0)))

combined <- inner_join(combined, VectorScan_cleaned, by = 'id')

combined <- combined %>% relocate(id, .after = last_col())
```

```{r}
temp <- combined[as.logical(combined$Group == "Mosquito"),]
counts_of_interest <- data.frame(
  column = names(temp),
  n_counts  = colSums(temp > 0, na.rm = TRUE))
```

```{r}
temp <- combined[as.logical(combined$Family == "Falciparum"),]
counts_of_interest <- data.frame(
  column = names(temp),
  n_counts  = colSums(temp > 0, na.rm = TRUE))
```

```{r}
temp <- combined[as.logical(combined$Family == "Anopheles"),]
counts_of_interest <- data.frame(
  column = names(temp),
  n_counts  = colSums(temp > 0, na.rm = TRUE))
```

```{r}
Plates23_28_22and27_SeropositiveInAnyone <- combined[as.logical(rowSums(combined[,1:128])>0),]
```

Plasmodium analysis 

```{r}
# Find all the Falciparum-derived peptides that are seropositive in any of the human samples 

Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK <- Plates23_28_22and27_SeropositiveInAnyone[as.logical(Plates23_28_22and27_SeropositiveInAnyone$Family == "Falciparum"),]

Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK <- Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK[as.logical(rowSums(Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK[,1:128])>0),]

# Do the blastp search

setwd('filepath')
  
seqs <- AAStringSet(Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK$'AA Sequence')
names(seqs) <- paste0(Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK$Subject, "_", Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK$id)

in_file_name <- paste0('Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK.fasta')
txt_file_name <- paste0('Plates23_28_22and27_Master_Plasmodium_clusters.txt')
csv_file_name <- paste0('Plates23_28_22and27_Master_Plasmodium_clusters.csv')

writeXStringSet(seqs, filepath = in_file_name)
  
system(sprintf("ulimit -n unlimited"))
system(sprintf("makeblastdb -in %s -out db -dbtype prot", in_file_name))
system(sprintf("blastp -query %s -db db  -evalue 1 -max_hsps 1 -max_target_seqs 100000 -word_size 7 -outfmt 6 -out %s", 
                   in_file_name, txt_file_name))
system(sprintf("awk 'BEGIN{FS=\"\\t\"; OFS=\",\"} {print $1, $2, $3, $4, $5, $6, $7, $8, $9, $10, $11, $12}' %s > %s", 
                   txt_file_name, csv_file_name))
```

```{r}
# Do the network graph clustering based on sequence identity 

rm(membership_df)
rm(Plates23_28_22and27_Master_Plasmodium_clusters_morethan1_membership_df)

setwd('filepath')

Subject_BLAST <- read.csv('Plates23_28_22and27_Master_Plasmodium_clusters.csv', header = FALSE)
Subject_BLAST <- Subject_BLAST[as.logical(Subject_BLAST$V12 >= 40), ]

edge_list <- Subject_BLAST[, c("V1", "V2")]
g <- graph_from_data_frame(d = edge_list, directed = FALSE)
g <- simplify(g, remove.multiple = TRUE, remove.loops = TRUE)

# Do the Louvain clustering
set.seed(123)  # Makes the results reproducible for the sake of reproducing the findings in the paper, since sometimes the clustering can change by 1-2 clusters, which offsets the Cluster IDs 

clusters <- cluster_louvain(g)
membership_vector <- membership(clusters)

cluster_sizes <- table(membership_vector)

membership_df <- data.frame(
  name      = names(membership_vector),   
  ClusterID = as.integer(membership_vector),
  stringsAsFactors = FALSE
)

# Only keep clusters that have 2+ members, basically requiring that a peptide has similarity to another peptide to be included in downstream analyses 
cluster_threshold <- 2
valid_clusters <- names(cluster_sizes[cluster_sizes >= cluster_threshold])

vertices_to_keep <- which(membership_vector %in% valid_clusters)
g_filtered <- induced_subgraph(g, vids = vertices_to_keep)

filtered_membership_vector <- membership_vector[vertices_to_keep]

g_simplified <- simplify(g_filtered, remove.loops = TRUE)

vertex_names_plot <- V(g_simplified)$name
Plates23_28_22and27_Master_Plasmodium_clusters_morethan1_membership_df <- membership_df %>%
  filter(name %in% vertex_names_plot)

Plates23_28_22and27_Master_Plasmodium_clusters_morethan1_membership_df$id <- as.numeric(sub(".*_", "", Plates23_28_22and27_Master_Plasmodium_clusters_morethan1_membership_df$name))

Plates23_28_22and27_Master_Plasmodium_cluster_props <- Plates23_28_22and27_Master_Plasmodium_clusters_morethan1_membership_df %>%
  group_by(ClusterID) %>%
  summarise(
    n        = n(),
    .groups  = "drop"
  )
```

```{r}
Plates23_28_22and27_Master_Plasmodium_clusters_withRPK <- inner_join(Plates23_28_22and27_Master_Plasmodium_clusters_morethan1_membership_df, Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK, by = 'id')

Plates23_28_22and27_Master_Plasmodium_cluster_sums <- Plates23_28_22and27_Master_Plasmodium_clusters_withRPK %>%
  group_by(ClusterID) %>%
  summarise(
    across(3:130, \(x) sum(x, na.rm = TRUE)),
    .groups = "drop"
  )

Plates23_28_22and27_Master_Plasmodium_cluster_sums_IDs <- Plates23_28_22and27_Master_Plasmodium_cluster_sums$ClusterID

Plates23_28_22and27_Master_Plasmodium_cluster_sums <- data.frame((t((Plates23_28_22and27_Master_Plasmodium_cluster_sums[,2:129]))))
colnames(Plates23_28_22and27_Master_Plasmodium_cluster_sums) <- Plates23_28_22and27_Master_Plasmodium_cluster_sums_IDs

Plates23_28_22and27_Master_Plasmodium_cluster_sums$Cohort <- c(rep('US', 62), rep('US', 14), rep('Day44', 14), rep('Month0', 19), rep('Month7', 19))
```

```{r}
df_long <- Plates23_28_22and27_Master_Plasmodium_cluster_sums %>% 
  pivot_longer(
    cols = -c(Cohort),        
    names_to  = "ClusterID",
    values_to = "value"
  )

wilcox_res <- df_long %>%
  filter(Cohort %in% c("US", "Month7")) %>%
  group_by(ClusterID) %>%
  summarise(
    p_value = wilcox.test(value ~ Cohort)$p.value,
    median_US   = median(value[Cohort == "US"],   na.rm = TRUE),
    median_Mali = median(value[Cohort == "Month7"], na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    p_adj   = p.adjust(p_value, method = "BH"),
    log2FC  = log2((median_Mali + 1) / (median_US + 1))  # Mali / US
  )

sig_clusters <- wilcox_res %>%
  filter(p_adj < 0.05) %>%
  pull(ClusterID)

Plates23_28_22and27_Master_Plasmodium_sig_clusters <- sig_clusters

df_long_sig <- df_long %>%
  filter(ClusterID %in% sig_clusters)

ggplot(df_long_sig, aes(x = Cohort, y = log2(value+1), fill = Cohort)) +
   scale_fill_manual(values  = c("US" = "gray", "Mali" = "red"), 
                    name = "Cohort") +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(width = 0.15, alpha = 0.4, size = 1) +
  facet_wrap(~ ClusterID, scales = "free_y") +
  labs(x = "group", y = "Cluster sum (log2)", title = "Cluster values by group status") +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  )
```

```{r}
temp <- Plates23_28_22and27_Master_Plasmodium_clusters_morethan1_membership_df
temp <- inner_join(Plates23_28_22and27_Master_Plasmodium_clusters_morethan1_membership_df, VectorScan, by = 'id')
```

```{r}
Plates23_28_22and27_Master_Plasmodium_sig_clusters <- data.frame("ClusterID" = Plates23_28_22and27_Master_Plasmodium_sig_clusters)
Plates23_28_22and27_Master_Plasmodium_sig_clusters$n <- Plates23_28_22and27_Master_Plasmodium_cluster_props$n[match(Plates23_28_22and27_Master_Plasmodium_sig_clusters$ClusterID, Plates23_28_22and27_Master_Plasmodium_cluster_props$ClusterID)]
```

```{r}
# Plot the cluster reactivity scores from the significantly different clusters 

heat_mat <- Plates23_28_22and27_Master_Plasmodium_cluster_sums %>%
  dplyr::select(Plates23_28_22and27_Master_Plasmodium_sig_clusters$ClusterID,  
         Cohort) 

heat_mat <- heat_mat[,1:(ncol(heat_mat)-1)]/Plates23_28_22and27_Master_Plasmodium_sig_clusters$n

annotation_row <- data.frame(
  Cohort = c(rep('CDC', 62),  rep('NIH', 28), rep('Mali', 38))
)
rownames(annotation_row) <- rownames(heat_mat)

annotation_col <- annotation_row

heat_mat_num <- heat_mat %>%
  as.matrix()

annotation_colors <- list(
  Cohort = c("Mali" = "orange", "NIH" = "#3f8e57" , "CDC" = "#598BC5")
)
  
mat <- t(heat_mat_num)

# Fixing the color scale to make the clusters show up better since there's a pretty big range 
upper <- quantile(mat, 0.97, na.rm = TRUE)  
n_col  <- 50
cols   <- colorRampPalette(c("white", "red", "purple"))(n_col)
breaks <- seq(from = 0, to = upper, length.out = n_col + 1)
mat_capped <- pmin(mat, upper)

pheatmap(
   mat,
  cluster_rows      = TRUE,
  cluster_cols      = FALSE,
  annotation_col    = annotation_col,
  annotation_colors = annotation_colors,
  color             = cols,
  breaks            = breaks,
  show_rownames     = FALSE,
  show_colnames     = FALSE,
  main              = "Significant Plasmodium clusters (Mali > US)"
)
```

```{r}
Plates23_28_22and27_Master_Plasmodium_peptides_from_significant_clusters <- Plates23_28_22and27_Master_Plasmodium_clusters_morethan1_membership_df %>%
  filter( ClusterID %in% Plates23_28_22and27_Master_Plasmodium_sig_clusters$ClusterID)

Plates23_28_22and27_Master_Plasmodium_peptides_from_significant_clusters <- Plates23_28_22and27_Master_Plasmodium_peptides_from_significant_clusters %>%
  arrange(ClusterID)

Plates23_28_22and27_Master_Plasmodium_peptides_from_significant_clusters <- inner_join(Plates23_28_22and27_Master_Plasmodium_peptides_from_significant_clusters, VectorScan, by = 'id')
```

```{r}
Plates23_28_22and27_Master_Plasmodium_peptides_from_significant_clusters_RPKs <- inner_join(Plates23_28_22and27_Master_Plasmodium_peptides_from_significant_clusters, Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK, by = 'id') 
```

```{r}
setwd('filepath')

# Create an AAStringSet object
seqs <- AAStringSet(Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK$'AA Sequence')
  # Add names from the sequence header column
names(seqs) <- paste0(Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK$id)
writeXStringSet(seqs, filepath = "Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK.faa")
```

cd 'filepath' 

makeblastdb -in Source_of_Top_Pfal_Clusters.faa -out db -parse_seqids -dbtype prot 
blastp -query Plates23_28_22and27_Master_Plasmodium_SeropositiveInAnyone_RPK.faa -db db -outfmt 6 -max_hsps 1 -out Top_Pfal_Clusters_Mapped.txt 

awk 'BEGIN{FS="\t"; OFS=","} {print $1, $2, $3, $4, $5, $6, $7, $8, $9, $10, $11, $12}' Top_Pfal_Clusters_Mapped.txt > Top_Pfal_Clusters_Mapped.csv

```{r}
Top_Pfal_Clusters_Mapped <- read.csv('filepath/Top_Pfal_Clusters_Mapped.csv', header=FALSE)
Top_Pfal_Clusters_Mapped$seq_id <- Top_Pfal_Clusters_Mapped[,1]
Top_Pfal_Clusters_Mapped <- Top_Pfal_Clusters_Mapped[as.logical(Top_Pfal_Clusters_Mapped$V12 >= 40), ]

Top_Pfal_Clusters_Mapped <- Top_Pfal_Clusters_Mapped %>%
  separate( col   = seq_id, into  = c("id", "ClusterID"), sep   = "_", remove = TRUE ) %>% mutate(id = as.numeric(id)  )

Top_Pfal_Clusters_Mapped$AANumber <- Top_Pfal_Clusters_Mapped$V9  + (Top_Pfal_Clusters_Mapped$V8 - Top_Pfal_Clusters_Mapped$V7)/2
```

```{r}
Seroprevalence_month7 <- Plate28_RPKs[,20:ncol(Plate28_RPKs)]
Seroprevalence_month7$id <- Plate28_RPKs$id
Seroprevalence_month7$Num_seropositive <- rowSums(Seroprevalence_month7[,1:19]>0)
Seroprevalence_month7$Per_seropositive <- Seroprevalence_month7$Num_seropositive/19*100
```

```{r}
Top_Pfal_Clusters_Mapped$Per_seropositive <- Seroprevalence_month7$Per_seropositive[match(Top_Pfal_Clusters_Mapped$id,Seroprevalence_month7$id)]
```

```{r}
write_xlsx(Top_Pfal_Clusters_Mapped, "Top_Pfal_Clusters_Mapped.xlsx")
```

Mosquito analysis 

```{r}
# Find mosquito-derived peptides that are seroreactive in at least one sample 

Plates23_28_22and27_Master_Mosquito_SeropositiveInAnyone_RPK <- Plates23_28_22and27_SeropositiveInAnyone[as.logical(Plates23_28_22and27_SeropositiveInAnyone$Group == "Mosquito"),]

Plates23_28_22and27_Master_Mosquito_SeropositiveInAnyone_RPK <- Plates23_28_22and27_Master_Mosquito_SeropositiveInAnyone_RPK[as.logical(rowSums(Plates23_28_22and27_Master_Mosquito_SeropositiveInAnyone_RPK[,1:128])>0),]

setwd('filepath')
  
seqs <- AAStringSet(Plates23_28_22and27_Master_Mosquito_SeropositiveInAnyone_RPK$'AA Sequence')
names(seqs) <- paste0(Plates23_28_22and27_Master_Mosquito_SeropositiveInAnyone_RPK$Subject, "_", Plates23_28_22and27_Master_Mosquito_SeropositiveInAnyone_RPK$id)

in_file_name <- paste0('Plates23_28_22and27_Master_Mosquito_SeropositiveInAnyone_RPK.fasta')
txt_file_name <- paste0('Plates23_28_22and27_Master_Mosquito_clusters.txt')
csv_file_name <- paste0('Plates23_28_22and27_Master_Mosquito_clusters.csv')

writeXStringSet(seqs, filepath = in_file_name)
  
system(sprintf("ulimit -n unlimited"))
system(sprintf("makeblastdb -in %s -out db -dbtype prot", in_file_name))
system(sprintf("blastp -query %s -db db  -evalue 1 -max_hsps 1 -max_target_seqs 100000 -word_size 7 -outfmt 6 -out %s", 
                   in_file_name, txt_file_name))
system(sprintf("awk 'BEGIN{FS=\"\\t\"; OFS=\",\"} {print $1, $2, $3, $4, $5, $6, $7, $8, $9, $10, $11, $12}' %s > %s", 
                   txt_file_name, csv_file_name))
```

```{r}
setwd('filepath')

Subject_BLAST <- read.csv('Plates23_28_22and27_Master_Mosquito_clusters.csv', header = FALSE)
Subject_BLAST <- Subject_BLAST[as.logical(Subject_BLAST$V12 >= 40), ]

edge_list <- Subject_BLAST[, c("V1", "V2")]
g <- graph_from_data_frame(d = edge_list, directed = FALSE)
g <- simplify(g, remove.multiple = TRUE, remove.loops = TRUE)

set.seed(123) 
clusters <- cluster_louvain(g)
membership_vector <- membership(clusters)

cluster_sizes <- table(membership_vector)

membership_df <- data.frame(
  name      = names(membership_vector),          
  ClusterID = as.integer(membership_vector),
  stringsAsFactors = FALSE
)

cluster_threshold <- 2
valid_clusters <- names(cluster_sizes[cluster_sizes >= cluster_threshold])

vertices_to_keep <- which(membership_vector %in% valid_clusters)
g_filtered <- induced_subgraph(g, vids = vertices_to_keep)

filtered_membership_vector <- membership_vector[vertices_to_keep]

g_simplified <- simplify(g_filtered, remove.loops = TRUE)

vertex_names_plot <- V(g_simplified)$name
Plates23_28_22and27_Master_Mosquito_clusters_morethan1_membership_df <- membership_df %>%
  filter(name %in% vertex_names_plot)

Plates23_28_22and27_Master_Mosquito_clusters_morethan1_membership_df$id <- as.numeric(sub(".*_", "", Plates23_28_22and27_Master_Mosquito_clusters_morethan1_membership_df$name))

Plates23_28_22and27_Master_Mosquito_cluster_props <- Plates23_28_22and27_Master_Mosquito_clusters_morethan1_membership_df %>%
  group_by(ClusterID) %>%
  summarise(
    n        = n(),
    .groups  = "drop"
  )

```

```{r}
Plates23_28_22and27_Master_Mosquito_clusters_withRPK <- inner_join(Plates23_28_22and27_Master_Mosquito_clusters_morethan1_membership_df, Plates23_28_22and27_Master_Mosquito_SeropositiveInAnyone_RPK, by = 'id')

Plates23_28_22and27_Master_Mosquito_cluster_sums <- Plates23_28_22and27_Master_Mosquito_clusters_withRPK %>%
  group_by(ClusterID) %>%
  summarise(
    across(3:130, \(x) sum(x, na.rm = TRUE)),
    .groups = "drop"
  )

Plates23_28_22and27_Master_Mosquito_cluster_sums_IDs <- Plates23_28_22and27_Master_Mosquito_cluster_sums$ClusterID

Plates23_28_22and27_Master_Mosquito_cluster_sums <- data.frame((t((Plates23_28_22and27_Master_Mosquito_cluster_sums[,2:129]))))
colnames(Plates23_28_22and27_Master_Mosquito_cluster_sums) <- Plates23_28_22and27_Master_Mosquito_cluster_sums_IDs

Plates23_28_22and27_Master_Mosquito_cluster_sums$Cohort <- c(rep('US', 62), rep('US', 14), rep('Day44', 14), rep('Month0', 19), rep('Month7', 19))
```

```{r}
df_long <- Plates23_28_22and27_Master_Mosquito_cluster_sums %>% 
  pivot_longer(
    cols = -c(Cohort),      
    names_to  = "ClusterID",
    values_to = "value"
  )

wilcox_res <- df_long %>%
  filter(Cohort %in% c("US", "Month7")) %>%
  group_by(ClusterID) %>%
  summarise(
    p_value = wilcox.test(value ~ Cohort)$p.value,
    median_US   = median(value[Cohort == "US"],   na.rm = TRUE),
    median_Mali = median(value[Cohort == "Month7"], na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    p_adj   = p.adjust(p_value, method = "BH"),
    log2FC  = log2((median_Mali + 1) / (median_US + 1))  # Mali / US
  )

# Only looking at the clusters where the scores were significantly higher in Mali 
sig_clusters <- wilcox_res %>%
  filter(p_adj < 0.05) %>%
   filter(log2FC > 0) %>%
  pull(ClusterID)

Plates23_28_22and27_Master_Mosquito_sig_clusters <- sig_clusters

df_long_sig <- df_long %>%
  filter(ClusterID %in% sig_clusters)

ggplot(df_long_sig, aes(x = Cohort, y = log2(value+1), fill = Cohort)) +
   scale_fill_manual(values  = c("US" = "gray", "Mali" = "red"), 
                    name = "Cohort") +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(width = 0.15, alpha = 0.4, size = 1) +
  facet_wrap(~ ClusterID, scales = "free_y") +
  labs(x = "group", y = "Cluster sum (log2)", title = "Cluster values by group status") +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  )

Plates23_28_22and27_Master_Mosquito_sig_clusters <- data.frame("ClusterID" = Plates23_28_22and27_Master_Mosquito_sig_clusters)
Plates23_28_22and27_Master_Mosquito_sig_clusters$n <- Plates23_28_22and27_Master_Mosquito_cluster_props$n[match(Plates23_28_22and27_Master_Mosquito_sig_clusters$ClusterID, Plates23_28_22and27_Master_Mosquito_cluster_props$ClusterID)]
```

```{r}
# Heatmap of the significant clusters 

heat_mat <- Plates23_28_22and27_Master_Mosquito_cluster_sums %>%
  dplyr::select(Plates23_28_22and27_Master_Mosquito_sig_clusters$ClusterID,   # cluster columns
         Cohort)                                                     # keep Cohort for annotation

heat_mat <- heat_mat[,1:(ncol(heat_mat)-1)]/Plates23_28_22and27_Master_Mosquito_sig_clusters$n


annotation_row <- data.frame(
  Cohort = c(rep('CDC', 62),  rep('NIH', 28), rep('Mali', 38))
)
rownames(annotation_row) <- rownames(heat_mat)

annotation_col <- annotation_row

heat_mat_num <- heat_mat %>%
  as.matrix()

annotation_colors <- list(
  Cohort = c("Mali" = "orange", "NIH" = "#3f8e57" , "CDC" = "#598BC5")
)
  
mat <- t(heat_mat_num)

# Fixing the color scale to make the clusters show up better since there's a pretty big range 
upper <- quantile(mat, 0.97, na.rm = TRUE)  
n_col  <- 50
cols   <- colorRampPalette(c("white", "red", "purple"))(n_col)
breaks <- seq(from = 0, to = upper, length.out = n_col + 1)
mat_capped <- pmin(mat, upper)

pheatmap(
   mat,
  cluster_rows      = FALSE,
  cluster_cols      = FALSE,
  annotation_col    = annotation_col,
  annotation_colors = annotation_colors,
  color             = cols,
  breaks            = breaks,
  show_rownames     = TRUE,
  show_colnames     = FALSE,
  main              = "Significant Plasmodium clusters (Mali > US)"
)
```


```{r}
Plates23_28_22and27_Master_Mosquito_peptides_from_significant_clusters <- Plates23_28_22and27_Master_Mosquito_clusters_morethan1_membership_df %>%
  filter( ClusterID %in% Plates23_28_22and27_Master_Mosquito_sig_clusters$ClusterID)

Plates23_28_22and27_Master_Mosquito_peptides_from_significant_clusters <- Plates23_28_22and27_Master_Mosquito_peptides_from_significant_clusters %>%
  arrange(ClusterID)

Plates23_28_22and27_Master_Mosquito_peptides_from_significant_clusters_RPKs <- inner_join(Plates23_28_22and27_Master_Mosquito_peptides_from_significant_clusters, Plates23_28_22and27_Master_Mosquito_SeropositiveInAnyone_RPK, by = 'id') 
```

```{r}
# To identify if any mosquito genus has overrepresentation among these peptides 

df  <- Plates23_28_22and27_Master_Mosquito_peptides_from_significant_clusters_RPKs
larger_set <- Plates23_28_22and27_Master_Mosquito_clusters_withRPK

families <- sort(unique(larger_set$Family))

fisher_results_list <- lapply(families, function(group_to_test) {
  
  df2 <- df[df$Family == group_to_test, ]
  
  temp1 <- nrow(df2) # Clustered & in genus X 
  temp2 <- nrow(larger_set[larger_set$Family == group_to_test, ]) - temp1  # Not clustered & in genus X
  temp3 <- nrow(df) - temp1 # Clustered & not in genus X
  temp4 <- nrow(larger_set) - temp1 - temp2 - temp3  # Not clustered & not in genus X
  
  contingency_table <- matrix(c(temp1, temp2,
                                temp3, temp4),
                              nrow = 2,
                              byrow = TRUE,
                              dimnames = list(
                                Clustered = c("Yes", "No"),
                                Family    = c(group_to_test, "Other")
                              ))
  
  ft <- fisher.test(contingency_table)
  
  data.frame(
    Family       = group_to_test,
    clustered_in_genus  = temp1,
    not_clustered_in_genus   = temp2,
    clustered_not_genus = temp3,
    not_clustered_not_genus  = temp4,
    odds_ratio  = unname(ft$estimate),
    conf_low           = ft$conf.int[1],
    conf_high          = ft$conf.int[2],
    p_value     = ft$p.value,
    stringsAsFactors = FALSE
  )
})

fisher_results <- do.call(rbind, fisher_results_list)
fisher_results$p_adj <- p.adjust(fisher_results$p_value, method = "bonferroni") # Chose bonferroni because there is a small number of comparisons
fisher_results$significant <- fisher_results$p_adj < 0.05
fisher_results
```

Orthogroup analysis for the mosquito-derived peptides 

```{r}
Plates23_28_22and27_Master_Mosquito_peptides_from_significant_clusters_Orthogroups <- inner_join(Plates23_28_22and27_Master_Mosquito_peptides_from_significant_clusters, VectorScan_Mosquito_Orthogroups, by = 'id')
```

```{r}
nrow(VectorScan_cleaned)
nrow(VectorScan_cleaned[as.logical(VectorScan_cleaned$Group == "Mosquito"),])
nrow(Plates23_28_22and27_Master_Mosquito_SeropositiveInAnyone_RPK)
nrow(Plates23_28_22and27_Master_Mosquito_clusters_morethan1_membership_df)
```

```{r}
hits <- data.frame(id = Plates23_28_22and27_Master_Mosquito_clusters_morethan1_membership_df$id)
hits <- inner_join(hits, VectorScan_Mosquito_Orthogroups, by = 'id')

hits_table <- data.frame(table(hits$'OrthoMCL group id_from_Protein'))

VectorScan_Orthogroup_table <-  data.frame(table(VectorScan_Mosquito_Orthogroups$'OrthoMCL group id_from_Protein'))

hits_table <- inner_join(hits_table, VectorScan_Orthogroup_table, by = 'Var1')

colnames(hits_table) <- c("Annotation", "Annotation Hit", "VectorScan")

hits_table$'Annotation Not hit' <- hits_table$VectorScan - hits_table$'Annotation Hit'

hits_table$'Not Annotation Hit' <- sum(hits_table[,2])-hits_table$`Annotation Hit`

hits_table$'Not Annotation Not Hit' <- sum(VectorScan_Orthogroup_table[,2]) - hits_table$'Annotation Hit' - hits_table$'Annotation Not hit' - hits_table$'Not Annotation Hit'

temp <- hits_table 

temp_table_ordered <- temp %>%
  arrange(desc(`Annotation Hit`))

# Only plot the top 10 groups for the sake of the figure
top_temp <- head(temp_table_ordered, 10)

my_plot <- ggplot(top_temp, aes(x = reorder(Annotation, `Annotation Hit`), y = `Annotation Hit`)) +
  geom_bar(stat = "identity", fill = "#3A54A5") +
  coord_flip() +
  labs(
    title = "Orthogroups with the largest representation among clustered peptides",
    x = "Orthogroup Annotation",
    y = "Number of peptides from Orthogroup X"
  ) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 12, hjust = 1))  

print(my_plot)
```


```{r}
# Enrichment analysis 

hits_table$p_value <- NA

for (i in 1:nrow(hits_table)) {
  annotation_hit <- hits_table[i, "Annotation Hit"]
  annotation_not_hit <- hits_table[i, "Annotation Not hit"]
  not_annotation_hit <- hits_table[i, "Not Annotation Hit"]
  not_annotation_not_hit <- hits_table[i, "Not Annotation Not Hit"]
  
  contingency_table <- matrix(c(annotation_hit, annotation_not_hit,
                                not_annotation_hit, not_annotation_not_hit),
                              nrow = 2,
                              byrow = TRUE)
  
  test_result <- fisher.test(contingency_table)
  
  hits_table$p_value[i] <- test_result$p.value
}

hits_table$p_adj <- p.adjust(hits_table$p_value, method = "BH")
  
significant_hits_table <- hits_table[as.logical(hits_table$p_adj < 0.05),]
significant_hits_table$'-log10(p)' <- -log10(significant_hits_table$p_adj)

significant_hits_table_ordered <- significant_hits_table %>%
 arrange(desc(`-log10(p)`))
top_significant_hits <- head(significant_hits_table_ordered, 10)

my_plot <- ggplot(top_significant_hits, aes(x = reorder(Annotation, `-log10(p)`), y = `Annotation Hit`, fill = `-log10(p)`)) +
  geom_bar(stat = "identity") +
  coord_flip() + 
  labs(
    title = "Orthogroups with the most significant enrichment among clustered peptides",
    x = "Orthogroup Annotation",
    y = "Number of peptides from Orthogroup X"
  ) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 12, hjust = 1)) 

print(my_plot)
```