Plate 28 

Download the data from the Bauer Core via Globus

cd filepath
conda activate cutadapt
for fq in *R1_001.fastq.gz; do cutadapt -g CAGGTGTGATGCTCGGGGATCCAGGAATTCGGAGCGGT -o ${fq%%.*}.cut.fastq.gz $fq; done 
for fq in *R2_001.fastq.gz; do cutadapt -g GCTTATCGTCGTCATCCTTGTAATCGCGGCCGCAAGCTTGTCGAGTGCAGTG -o ${fq%%.*}.cut.fastq.gz $fq; done 

align_reads.sh -- 
#!/bin/bash
# Define a function that processes a pair of FASTQ files
align_paired_reads() {
  base=${1%_R1_001.cut.fastq.gz}
  fq1="${base}_R1_001.cut.fastq.gz"
  fq2="${base}_R2_001.cut.fastq.gz"
  # Run Bowtie2 and redirect standard output and error
  bowtie2 -x VectorScan_Bowtie --very-sensitive -1 "$fq1" -2 "$fq2" -S "${base}.sam" 2>&1 | tee "${base}_bowtie2.log"
}
# Export the function to be used by parallel
export -f align_paired_reads
# Find all R1 files and pass them to GNU Parallel
parallel align_paired_reads ::: *_R1_001.cut.fastq.gz

chmod +x align_reads.sh
./align_reads.sh

parallel '
  samtools view -bS {} |
  samtools view -b -f 0x2 |
  samtools sort -o {=s/\.sam$/.concordant.sorted.bam/=} - &&
  samtools index {=s/\.sam$/.concordant.sorted.bam/=} &&
  samtools idxstats {=s/\.sam$/.concordant.sorted.bam/=} |
    cut -f 1,3 |
    sed -e "/^\*\t/d" -e "1 i id\t${{=s/\.sam$//=}}" |
    tr "\\t" "," > {=s/\.sam$/.count.csv/=}
' ::: *.sam

Transfer the count files over 

cd 'filepath'
paste -d ',' *.count.csv >2025_09_22_Plate28_counts.csv

```{r}
# Load relevant libraries 
library('dplyr')
library('corrplot')
library('writexl')
library('readxl')
library('seqinr')
library('ggplot2')
library('gridExtra')
library('ggfortify')
library('pheatmap')
library('Biostrings')
library('tidyverse')
library('igraph')
library('RColorBrewer')
```

```{r}
setwd('filepath')
VectorScan <- read_xlsx("VectorScan_Library_1_2.xlsx") ## Or file name of the relevant file that contains the library information
VectorScan_cleaned <- read_xlsx("VectorScan_cleaned.xlsx")
```

```{r}
# Read in the counts file. Each column is a replicate, each row is a peptide in the library.
Plate28_VectorScan_counts <- read.csv("filepath")
cols_to_remove <- grepl("id", names(Plate28_VectorScan_counts))
Plate28_VectorScan_counts_cleaned <- Plate28_VectorScan_counts[, !cols_to_remove]

colnames(Plate28_VectorScan_counts_cleaned) <- c('kali0602_6351_m00','kali0038_0322_m07','kali0674_6698_m07','kali0605_6365_m00','kali0527_5529_m07','kali0602_6353_m07','kali0436_4430_m07','PBS','kali0545_5860_m07','kali0447_4561_m00','kali0472_4857_m07','kali0497_5148_m07','kali0627_6482_m00','kali0437_4439_m00','kali0627_6487_m07','kali0545_5854_m00','kali0674_6698_m07','kali0610_6414_m07','kali0674_6696_m00','kali0562_6004_m07','PBS','kali0048_0435_m07','kali0447_4563_m07','kali0436_4422_m00','kali0562_5993_m00','kali0527_5518_m00','kali0605_6373_m07','PBS','kali0497_5139_m00','kali0437_4442_m07','kali0038_0315_m00','kali0403_4040_m07','kali0497_5148_m07','kali0048_0429_m00','kali0437_4442_m07','kali0038_0315_m00','kali0048_0435_m07','kali0610_6410_m00','kali0031_0259_m00','kali0288_2931_m00','PBS','TUNE-32','kali0605_6373_m07','kali0562_5993_m00','kali0610_6414_m07','kali0403_4035_m00','kali0140_1486_m00','PBS','kali0472_4857_m07','kali0031_0262_m07','kali0627_6482_m00','TUNE-35','kali0048_0429_m00','kali0472_4849_m00','kali0447_4563_m07','kali0031_0259_m00','kali0674_6696_m00','kali0472_4849_m00','kali0288_2936_m07','kali0140_1494_m07','PBS','kali0527_5518_m00','kali0436_4422_m00','kali0602_6351_m00','kali0545_5854_m00','kali0140_1494_m07','kali0527_5529_m07','PBS','kali0545_5860_m07','kali0562_6004_m07','kali0403_4040_m07','TUNE-32','kali0288_2936_m07','kali0605_6365_m00','kali0140_1486_m00','kali0038_0322_m07','kali0031_0262_m07','kali0436_4430_m07','kali0602_6353_m07','TUNE-35','PBS','kali0288_2931_m00','kali0447_4561_m00','kali0627_6487_m07','kali0403_4035_m00','kali0497_5139_m00','kali0610_6410_m00','kali0437_4439_m00')
colnames(Plate28_VectorScan_counts_cleaned) <- make.names(colnames(Plate28_VectorScan_counts_cleaned), unique = TRUE)
Plate28_VectorScan_counts_cleaned <- Plate28_VectorScan_counts_cleaned[ , sort(names(Plate28_VectorScan_counts_cleaned))]

Plate28_VectorScan_counts_cleaned <- Plate28_VectorScan_counts_cleaned[ , sort(names(Plate28_VectorScan_counts_cleaned))]
```

```{r}
colnames(Plate28_VectorScan_counts_cleaned) <- c('kali0031_m00','kali0031_m00.1','kali0031_m07','kali0031_m07.1','kali0038_m00','kali0038_m00.1','kali0038_m07','kali0038_m07.1','kali0048_m00','kali0048_m00.1','kali0048_m07','kali0048_m07.1','kali0140_m00','kali0140_m00.1','kali0140_m07','kali0140_m07.1','kali0288_m00','kali0288_m00.1','kali0288_m07','kali0288_m07.1','kali0403_m00','kali0403_m00.1','kali0403_m07','kali0403_m07.1','kali0436_m00','kali0436_m00.1','kali0436_m07','kali0436_m07.1','kali0437_m00','kali0437_m00.1','kali0437_m07','kali0437_m07.1','kali0447_m00','kali0447_m00.1','kali0447_m07','kali0447_m07.1','kali0472_m00','kali0472_m00.1','kali0472_m07','kali0472_m07.1','kali0497_m00','kali0497_m00.1','kali0497_m07','kali0497_m07.1','kali0527_m00','kali0527_m00.1','kali0527_m07','kali0527_m07.1','kali0545_m00','kali0545_m00.1','kali0545_m07','kali0545_m07.1','kali0562_m00','kali0562_m00.1','kali0562_m07','kali0562_m07.1','kali0602_m00','kali0602_m00.1','kali0602_m07','kali0602_m07.1','kali0605_m00','kali0605_m00.1','kali0605_m07','kali0605_m07.1','kali0610_m00','kali0610_m00.1','kali0610_m07','kali0610_m07.1','kali0627_m00','kali0627_m00.1','kali0627_m07','kali0627_m07.1','kali0674_m00','kali0674_m00.1','kali0674_m07','kali0674_m07.1','PBS','PBS.1','PBS.2','PBS.3','PBS.4','PBS.5','PBS.6','PBS.7','TUNE.32','TUNE.32.1','TUNE.35','TUNE.35.1')
```

```{r}
selected_PBS_columns <- grep("PBS", names(Plate28_VectorScan_counts_cleaned), value = TRUE)
Plate28_counts_PBS <- Plate28_VectorScan_counts_cleaned[, selected_PBS_columns]

Plate28_PBS_RPK <- sweep(Plate28_counts_PBS, 2, colSums(Plate28_counts_PBS), FUN = "/") * 1e5
Plate28_PBS_RPK$mean <-  apply(Plate28_PBS_RPK, 1, mean) 
Plate28_PBS_RPK$stdev <-  apply(Plate28_PBS_RPK, 1, sd) 
Plate28_PBS_RPK$LOD <- Plate28_PBS_RPK$mean + 5*Plate28_PBS_RPK$stdev
```

```{r}
cor_matrix <- cor(Plate28_VectorScan_counts_cleaned,Plate28_VectorScan_counts_cleaned, method = "pearson")
corrplot(cor_matrix, method="shade", tl.cex = 0.4, tl.col = "black", col=COL2('RdBu'))
```

```{r}
selected_Mali_columns <- grep("kali", names(Plate28_VectorScan_counts_cleaned), value = TRUE)
Plate28_Mali_counts <- Plate28_VectorScan_counts_cleaned[, selected_Mali_columns]
```

```{r}
identifiers <- c('kali0031','kali0038','kali0048','kali0140','kali0288','kali0403','kali0436','kali0437','kali0447','kali0472','kali0497','kali0527','kali0545','kali0562','kali0602','kali0605','kali0610','kali0627','kali0674')

Plate28_Mali_VectorScan_All_results_list <- list()
Plate28_Mali_VectorScan_Seroreactive_results_list <- list()
Plate28_Mali_VectorScan_Discordance_results_list <-  list()
Plate28_Mali_VectorScan_ConcordantPeptides_results_list <- list()
discordance_temp <- data.frame()

# Loop over each identifier
for (identifier in identifiers) {
  
  Month0_Rep1_col <- paste0(identifier, "_m00")  
  Month0_Rep2_col <- paste0(identifier, "_m00.1")  
  Month7_Rep1_col <- paste0(identifier, "_m07")  
  Month7_Rep2_col <- paste0(identifier, "_m07.1")  
  
  selected_PBS_columns <- grep("PBS", names(Plate28_VectorScan_counts_cleaned), value = TRUE)
   
  selected_sample_columns <- c(Month0_Rep1_col, Month0_Rep2_col,
                       Month7_Rep1_col, Month7_Rep2_col) 
  
  Pt <- Plate28_Mali_counts[, selected_sample_columns]
  Pt <- cbind(Pt, Plate28_VectorScan_counts_cleaned[, selected_PBS_columns])
  
  Pt$id <- VectorScan$id

  Pt$PBS_LOD <- Plate28_PBS_RPK$LOD

  # To compare between timepoints, first take the RPK for each sample 
  
  Pt$Month0_Rep1_RPK <- Pt[[Month0_Rep1_col]]/sum(Pt[[Month0_Rep1_col]])*1e5
  Pt$Month0_Rep2_RPK <- Pt[[Month0_Rep2_col]]/sum(Pt[[Month0_Rep2_col]])*1e5
  
  Pt$Month7_Rep1_RPK <- Pt[[Month7_Rep1_col]]/sum(Pt[[Month7_Rep1_col]])*1e5
  Pt$Month7_Rep2_RPK <- Pt[[Month7_Rep2_col]]/sum(Pt[[Month7_Rep2_col]])*1e5
  
  # Find peptides that are seroreactive at each timepoint 
  
  # To be seroreactive, both replicates from that sample need to be above their noise threshold 
    # Also enforcing a count limit, where the peptide needs a count >= 5
  
  rep1_high <- (Pt$Month0_Rep1_RPK > Pt$PBS_LOD) &  (Pt[[Month0_Rep1_col]] >= 5)
  rep2_high <-  (Pt$Month0_Rep2_RPK > Pt$PBS_LOD)  &  (Pt[[Month0_Rep2_col]] >= 5)
  
  Pt$Month0_seroreactive <- ifelse(rep1_high == 1 & rep2_high == 1, 1, 0)
  Pt$Month0_Discordant <- ifelse(Pt$Month0_seroreactive == 0 & (rep1_high != rep2_high), 1, 0)
    
  rep1_high <- (Pt$Month7_Rep1_RPK > Pt$PBS_LOD) &  (Pt[[Month7_Rep1_col]] >= 5)
  rep2_high <-  (Pt$Month7_Rep2_RPK > Pt$PBS_LOD)  &  (Pt[[Month7_Rep2_col]] >= 5)
  
  Pt$Month7_seroreactive <- ifelse(rep1_high == 1 & rep2_high == 1, 1, 0)
  Pt$Month7_Discordant <- ifelse(Pt$Month7_seroreactive == 0 & (rep1_high != rep2_high), 1, 0)
  
  Pt$Discordant_in_both <- ifelse(Pt$Month0_Discordant == 1 & Pt$Month7_Discordant == 1, 1, 0)
  
  discordance_temp <- data.frame(Month0 = sum(Pt$Month0_Discordant), Month7 = sum(Pt$Month7_Discordant), Both = sum(Pt$Discordant_in_both))
 
  Plate28_Mali_VectorScan_Discordance_results_list[[identifier]] <- discordance_temp
  
  Plate28_Mali_VectorScan_All_results_list[[identifier]] <- Pt
    
  # Limit the peptides to the ones in the library that do not have long GS linkers and have representation in the original library
  # The number of peptides in this cleaned library (VectorScan_cleaned) should be the denominator for all future Fishers tests
  
  Pt <- inner_join(Pt, VectorScan_cleaned, by = 'id')
  
  Pt$ForAlignment <- paste0(">", Pt$id, "_", Pt$Species, " ", Pt$`AA Sequence`)
  
  # Want to limit the pool of peptides to ones that are concordant at both timepoints 
  
  Pt <- Pt[as.logical(Pt$Month0_Discordant == 0),]
  Pt <- Pt[as.logical(Pt$Month7_Discordant == 0),]
  
  Pt$Month0_Avg <- (Pt$Month0_Rep1_RPK + Pt$Month0_Rep2_RPK)/2
  Pt$Month7_Avg <- (Pt$Month7_Rep1_RPK + Pt$Month7_Rep2_RPK)/2
  Pt$Month7vMonth0_Difference <- (Pt$Month7_Avg+0.1) / (Pt$Month0_Avg+0.1)

  Pt$Month0_Seroreactive_Average <- Pt$Month0_Avg * Pt$Month0_seroreactive
  Pt$Month7_Seroreactive_Average <- Pt$Month7_Avg * Pt$Month7_seroreactive
  
  Plate28_Mali_VectorScan_ConcordantPeptides_results_list[[identifier]] <- Pt
  
  # Then want to limit the pool to ones that are seroreactive at one of the timepoints 
  
  Pt <- Pt[as.logical(Pt$Month0_seroreactive == 1 | Pt$Month7_seroreactive == 1),]
  
  Plate28_Mali_VectorScan_Seroreactive_results_list[[identifier]] <- Pt

}

```

```{r}
discordance_df <- bind_rows(Plate28_Mali_VectorScan_Discordance_results_list, .id = "source_df")
```

```{r}
Plate28_Mali_Month0_Seropositive_RPKs <- Plate28_Mali_VectorScan_ConcordantPeptides_results_list %>%
  map(~ dplyr::select(.x, id, Month0_Seroreactive_Average)) %>% 
      bind_rows(.id = "Sample") %>%
          pivot_wider(
            names_from = Sample, 
            values_from = Month0_Seroreactive_Average, 
            values_fill = 0  
          )

colnames(Plate28_Mali_Month0_Seropositive_RPKs) <- c('id','kali0031_Month0','kali0038_Month0','kali0048_Month0','kali0140_Month0','kali0288_Month0','kali0403_Month0','kali0436_Month0','kali0437_Month0','kali0447_Month0','kali0472_Month0','kali0497_Month0','kali0527_Month0','kali0545_Month0','kali0562_Month0','kali0602_Month0','kali0605_Month0','kali0610_Month0','kali0627_Month0','kali0674_Month0')


Plate28_Mali_Month7_Seropositive_RPKs <- Plate28_Mali_VectorScan_ConcordantPeptides_results_list %>%
  map(~ dplyr::select(.x, id, Month7_Seroreactive_Average)) %>% 
      bind_rows(.id = "Sample") %>%
          pivot_wider(
            names_from = Sample, 
            values_from = Month7_Seroreactive_Average, 
            values_fill = 0  
          )

colnames(Plate28_Mali_Month7_Seropositive_RPKs) <- c('id','kali0031_Month7','kali0038_Month7','kali0048_Month7','kali0140_Month7','kali0288_Month7','kali0403_Month7','kali0436_Month7','kali0437_Month7','kali0447_Month7','kali0472_Month7','kali0497_Month7','kali0527_Month7','kali0545_Month7','kali0562_Month7','kali0602_Month7','kali0605_Month7','kali0610_Month7','kali0627_Month7','kali0674_Month7')

Plate28_Mali_BothTimepoints_Seropositive_RPKs <- full_join(Plate28_Mali_Month0_Seropositive_RPKs, Plate28_Mali_Month7_Seropositive_RPKs)
```

```{r}
# Can't save because some of the columns are tibbles
# to fix that: 

Plate28_Mali_BothTimepoints_Seropositive_RPKs_df <- Plate28_Mali_BothTimepoints_Seropositive_RPKs

is_df_col <- vapply(Plate28_Mali_BothTimepoints_Seropositive_RPKs_df, is.data.frame, logical(1))
for (nm in names(Plate28_Mali_BothTimepoints_Seropositive_RPKs_df)[is_df_col]) {
  Plate28_Mali_BothTimepoints_Seropositive_RPKs_df[[nm]] <- Plate28_Mali_BothTimepoints_Seropositive_RPKs_df[[nm]][[1]]
}

write_xlsx(Plate28_Mali_BothTimepoints_Seropositive_RPKs_df, "Plate28_Mali_BothTimepoints_Seropositive_RPKs_df.xlsx")
```

```{r}
temp <- Plate28_Mali_BothTimepoints_Seropositive_RPKs  
temp <- inner_join(temp, VectorScan_cleaned, by = 'id')
temp <- temp[,2:39]
temp <- temp[as.logical(rowSums(temp) > 0),]
temp <- temp[, sort(names(temp))]
nrow(temp)

cor_matrix <- cor(temp,temp, method = "spearman")
corrplot(cor_matrix, method="shade", tl.cex = 0.4, tl.col = "black", col=COL2('RdBu'))
```

```{r}
# Measure mosquito breadth 

temp <- Plate28_Mali_BothTimepoints_Seropositive_RPKs
temp <- inner_join(temp, VectorScan_cleaned, by = 'id')

temp <- temp[as.logical(temp$Group == "Mosquito"),]
counts_of_interest <- data.frame(
  column = names(temp),
  n_counts  = colSums(temp > 0, na.rm = TRUE))
```

```{r}
Plate28_Metadata <- data.frame(
  Subject = c(rep('kali0288',2),rep('kali0403',2),rep('kali0545',2),rep('kali0140',2),rep('kali0048',2),rep('kali0038',2),rep('kali0562',2),rep('kali0436',2),rep('kali0031',2),rep('kali0605',2),rep('kali0627',2),rep('kali0674',2),rep('kali0497',2),rep('kali0610',2),rep('kali0472',2),rep('kali0527',2),rep('kali0437',2),rep('kali0447',2),rep('kali0602',2)),
  Timepoint = factor((rep(c("Month 0", "Month 7"), 19))), 
  Sickle = c(rep('AA',2),rep('AA',2),rep('AA',2),rep('AC',2),rep('AA',2),rep('AA',2),rep('AA',2),rep('AA',2),rep('AA',2),rep('AA',2),rep('AA',2),rep('AA',2),rep('AS',2),rep('AA',2),rep('AS',2),rep('AS',2),rep('AS',2),rep('AA',2),rep('AA',2)), 
  Age = c(rep(8,2),rep(7,2),rep(4,2),rep(10,2),rep(15,2),rep(12,2),rep(3,2),rep(7,2),rep(17,2),rep(2,2),rep(1,2),rep(0,2),rep(5,2),rep(2,2),rep(6,2),rep(4,2),rep(7,2),rep(7,2),rep(2,2)), 
  molFOI = c(rep(46,2),rep(43,2),rep(30,2),rep(28,2),rep(19,2),rep(18,2),rep(18,2),rep(14,2),rep(12,2),rep(9,2),rep(6,2),rep(6,2),rep(6,2),rep(4,2),rep(4,2),rep(2,2),rep(1,2),rep(1,2),rep(0,2)), 
  original_ID = c('kali0288_2931_m00','kali0288_2936_m07','kali0403_4035_m00','kali0403_4040_m07','kali0545_5854_m00','kali0545_5860_m07','kali0140_1486_m00','kali0140_1494_m07','kali0048_0429_m00','kali0048_0435_m07','kali0038_0315_m00','kali0038_0322_m07','kali0562_5993_m00','kali0562_6004_m07','kali0436_4422_m00','kali0436_4430_m07','kali0031_0259_m00','kali0031_0262_m07','kali0605_6365_m00','kali0605_6373_m07','kali0627_6482_m00','kali0627_6487_m07','kali0674_6696_m00','kali0674_6698_m07','kali0497_5139_m00','kali0497_5148_m07','kali0610_6410_m00','kali0610_6414_m07','kali0472_4849_m00','kali0472_4857_m07','kali0527_5518_m00','kali0527_5529_m07','kali0437_4439_m00','kali0437_4442_m07','kali0447_4561_m00','kali0447_4563_m07','kali0602_6351_m00','kali0602_6353_m07'))

```

```{r}
# Measure Falciparum breadth 

temp <- Plate28_Mali_BothTimepoints_Seropositive_RPKs
temp <- inner_join(temp, VectorScan_cleaned, by = 'id')
temp <- temp[as.logical(temp$Family == "Falciparum"),]

counts_of_interest <- data.frame(
  column = names(temp),
  breadth  = colSums(temp > 0, na.rm = TRUE)
)

counts_of_interest$Subject <- sub("\\_[^.]*$", "", counts_of_interest$column)
counts_of_interest$Timepoint <- sub(".*_", "", counts_of_interest$column)
counts_of_interest$molFOI <-  Plate28_Metadata$molFOI[match(counts_of_interest$Subject, Plate28_Metadata$Subject)]
counts_of_interest$Age <-  Plate28_Metadata$Age[match(counts_of_interest$Subject, Plate28_Metadata$Subject)]

temp_month0 <- counts_of_interest[as.logical(counts_of_interest$Timepoint == "Month0"),]
temp_month7 <- counts_of_interest[as.logical(counts_of_interest$Timepoint == "Month7"),]

# Fit a quasi-poisson model 

fit_quasipois <- glm(
  breadth ~ molFOI,
  family = quasipoisson,
  data = temp_month7
)

summary(fit_quasipois)

predicted_data <- data.frame(
  molFOI = seq(min(temp_month7$molFOI),
                          max(temp_month7$molFOI),
                          length.out = 100)
)

predicted_data$pred_breadth <- predict(fit_quasipois, newdata = predicted_data, type = "response")

ggplot(temp_month7, aes(x = molFOI, y = breadth)) +
  geom_point(alpha = 0.6) +
  geom_line(data = predicted_data, aes(x = molFOI, y = pred_breadth),
            color = "red", size = 1.1) +
  labs(
    x = "molFOI",
    y = "# seropositive P. falciparum peptides (Month 7)",
    title = "Relationship between molFOI and  P. falciparum breadth at Month 7 \n(quasi poisson)"
  ) +
  theme_bw()

```

```{r}
# Breadth of the Anopheles part of the library  

temp <- Plate28_Mali_BothTimepoints_Seropositive_RPKs
temp <- inner_join(temp, VectorScan_cleaned, by = 'id')
temp <- temp[as.logical(temp$Family == "Anopheles"),]

counts_of_interest <- data.frame(
  column = names(temp),
  breadth  = colSums(temp > 0, na.rm = TRUE)
)

counts_of_interest$Subject <- sub("\\_[^.]*$", "", counts_of_interest$column)
counts_of_interest$Timepoint <- sub(".*_", "", counts_of_interest$column)
counts_of_interest$molFOI <-  Plate28_Metadata$molFOI[match(counts_of_interest$Subject, Plate28_Metadata$Subject)]
counts_of_interest$Age <-  Plate28_Metadata$Age[match(counts_of_interest$Subject, Plate28_Metadata$Subject)]

temp_month0 <- counts_of_interest[as.logical(counts_of_interest$Timepoint == "Month0"),]
temp_month7 <- counts_of_interest[as.logical(counts_of_interest$Timepoint == "Month7"),]

# Fit a quasi-poisson model

fit_quasipois <- glm(
  breadth ~ molFOI,
  family = quasipoisson,
  data = temp_month7
)

summary(fit_quasipois)

predicted_data <- data.frame(
  molFOI = seq(min(temp_month7$molFOI),
                          max(temp_month7$molFOI),
                          length.out = 100)
)

predicted_data$pred_breadth <- predict(fit_quasipois, newdata = predicted_data, type = "response")

ggplot(temp_month7, aes(x = molFOI, y = breadth)) +
  geom_point(alpha = 0.6) +
  geom_line(data = predicted_data, aes(x = molFOI, y = pred_breadth),
            color = "red", size = 1.1) +
  labs(
    x = "molFOI",
    y = "# seropositive Anopheles peptides (Month 7)",
    title = "Relationship between molFOI and Anopheles breadth at Month 7 \n(NB regression)"
  ) +
  theme_bw()

```