CDC Analysis for Revision

Plate 22: TUNE plate 1

Plate 27: TUNE plate 2

```{r}
# Load relevant libraries 
library(Biostrings)
library('dplyr')
library('corrplot')
library('writexl')
library('readxl')
library('seqinr')
library(ggplot2)
library(gridExtra)
library(ggfortify)
library(pheatmap)
library(Biostrings)
library(tidyverse)
library(igraph)
library(RColorBrewer)
library(reshape2)
```

```{r}
setwd('filepath')
VectorScan <- read_xlsx("VectorScan_Library_1_2.xlsx") ## Or file name of the relevant file that contains the library information

setwd('filepath')
VectorScan_cleaned <- read_xlsx("VectorScan_cleaned.xlsx")
```

Bauer Core run Plates 22 and 27

Download the data from the Bauer Core via Globus

cd filepath conda activate cutadapt for fq
in *R1_001.fastq.gz; do cutadapt -g
CAGGTGTGATGCTCGGGGATCCAGGAATTCGGAGCGGT -o \${fq%%.*}.cut.fastq.gz \$fq;
done for fq in *R2_001.fastq.gz; do cutadapt -g
GCTTATCGTCGTCATCCTTGTAATCGCGGCCGCAAGCTTGTCGAGTGCAGTG -o
\${fq%%.*}.cut.fastq.gz \$fq; done

On the cluster: conda activate bio-env

align_reads.sh -- #!/bin/bash \# Define a function that processes a pair
of FASTQ files align_paired_reads() { base=${1%_R1_001.cut.fastq.gz}
  fq1="${base}\_R1_001.cut.fastq.gz" fq2="${base}_R2_001.cut.fastq.gz"
  # Run Bowtie2 and redirect standard output and error
  bowtie2 -x VectorScan_Bowtie --very-sensitive -1 "$fq1" -2
"$fq2" -S "${base}.sam" 2\>&1 \| tee "\${base}\_bowtie2.log" } \# Export
the function to be used by parallel export -f align_paired_reads \# Find
all R1 files and pass them to GNU Parallel parallel align_paired_reads
::: \*\_R1_001.cut.fastq.gz

cd filepath

chmod +x align_reads.sh ./align_reads.sh

On the cluster: parallel ' samtools view -bS {} \| samtools view -b -f
0x2 \| samtools sort -o {=s/.sam$/.concordant.sorted.bam/=} - &&
  samtools index {=s/\.sam$/.concordant.sorted.bam/=} && samtools
idxstats {=s/.sam$/.concordant.sorted.bam/=} |
    cut -f 1,3 |
    sed -e "/^\*\t/d" -e "1 i id\t${{=s/.sam$//=}}" |
    tr "\\t" "," > {=s/\.sam$/.count.csv/=} ' ::: \*.sam

paste -d ',' \*.count.csv \>2025_10_17_Plates22and27_counts.csv

cd 'filepath'

```{r}
AllCounts <- read.csv('filepath/2025_10_17_Plates22and27_counts.csv') 

cols_to_remove <- grepl("id", names(AllCounts))
AllCounts <- AllCounts[, !cols_to_remove]

colnames(AllCounts) <- c('P22_PBS','P22_TUNE-24','P22_TUNE-52','P22_TUNE-32','P22_TUNE-26','P22_PBS','P22_TUNE-40','P22_TUNE-25','P22_TUNE-37','P22_TUNE-27','P22_TUNE-45','P22_TUNE-33','P22_TUNE-46','P22_TUNE-29','P22_TUNE-38','P22_TUNE-42','P22_TUNE-49','P22_TUNE-69','P22_TUNE-30','P22_TUNE-35','P22_TUNE-39','P22_TUNE-34','P22_TUNE-28','P22_TUNE-36','P22_PBS','P22_TUNE-73','P22_TUNE-51','P22_TUNE-27','P22_TUNE-74','P22_PBS','P22_TUNE-43','P22_TUNE-72','P22_TUNE-26','P22_TUNE-48','P22_TUNE-41','P22_TUNE-31','P22_TUNE-68','P22_TUNE-33','P22_TUNE-39','P22_TUNE-70','P22_TUNE-44','P22_TUNE-47','P22_TUNE-50','P22_TUNE-31','P22_TUNE-48','P22_TUNE-50','P22_TUNE-36','P22_TUNE-34','P22_PBS','P22_TUNE-76','P22_TUNE-29','P22_TUNE-75','P22_TUNE-32','P22_TUNE-71','P22_TUNE-46','P22_TUNE-77','P22_TUNE-25','P22_TUNE-75','P22_TUNE-43','P22_TUNE-24','P22_TUNE-77','P22_TUNE-35','P22_TUNE-52','P22_TUNE-40','P22_PBS','P22_TUNE-38','P22_TUNE-71','P22_TUNE-47','P22_TUNE-51','P22_TUNE-76','P22_TUNE-78','P22_TUNE-68','P22_PBS','P22_TUNE-73','P22_TUNE-45','P22_TUNE-42','P22_TUNE-44','P22_TUNE-69','P22_TUNE-74','P22_TUNE-30','P22_TUNE-72','P22_TUNE-37','P22_TUNE-78','P22_PBS','P22_TUNE-49','P22_TUNE-28','P22_TUNE-70','P22_TUNE-41','P27_TUNE-16','P27_TUNE-69','P27_TUNE-73','P27_TUNE-74','P27_TUNE-15','P27_TUNE-20','P27_TUNE-23','P27_PBS','P27_TUNE-14','P27_TUNE-10','P27_TUNE-11','P27_TUNE-30','P27_TUNE-32','P27_TUNE-23','P27_TUNE-17','P27_TUNE-11','P27_TUNE-75','P27_TUNE-7','P27_TUNE-68','P27_TUNE-69','P27_PBS','P27_TUNE-5','P27_TUNE-3','P27_TUNE-74','P27_TUNE-18','P27_TUNE-7','P27_TUNE-18','P27_PBS','P27_TUNE-14','P27_TUNE-78','P27_TUNE-9','P27_TUNE-77','P27_TUNE-73','P27_TUNE-70','P27_TUNE-21','P27_TUNE-78','P27_TUNE-35','P27_TUNE-76','P27_TUNE-5','P27_TUNE-30','P27_PBS','P27_TUNE-3','P27_TUNE-36','P27_TUNE-4','P27_TUNE-15','P27_TUNE-19','P27_TUNE-8','P27_PBS','P27_TUNE-76','P27_TUNE-37','P27_TUNE-72','P27_TUNE-13','P27_TUNE-6','P27_TUNE-22','P27_TUNE-2','P27_TUNE-70','P27_TUNE-13','P27_TUNE-1','P27_TUNE-22','P27_TUNE-71','P27_PBS','P27_TUNE-4','P27_TUNE-2','P27_TUNE-36','P27_TUNE-17','P27_TUNE-16','P27_TUNE-6','P27_PBS','P27_TUNE-12','P27_TUNE-37','P27_TUNE-79','P27_TUNE-12','P27_TUNE-72','P27_TUNE-77','P27_TUNE-79','P27_TUNE-1','P27_TUNE-35','P27_TUNE-20','P27_TUNE-21','P27_TUNE-68','P27_PBS','P27_TUNE-9','P27_TUNE-8','P27_TUNE-32','P27_TUNE-75','P27_TUNE-19','P27_TUNE-10','P27_TUNE-71')

colnames(AllCounts) <- make.unique(colnames(AllCounts))

AllCounts <- AllCounts[, order(names(AllCounts))]

cor_matrix <- cor(AllCounts,AllCounts, method = "pearson")
corrplot(cor_matrix, method="shade", tl.cex = 0.4, tl.col = "black", col=COL2('RdBu'))
```

Plate 22 - TUNE-49 has poor concordance between replicates --> remove 
Plate 27 - TUNE-8 has poor concordance between replicates --> remove 

```{r}
cols_to_remove <- grepl("TUNE-49", names(AllCounts))
AllCounts <- AllCounts[, !cols_to_remove]

cols_to_remove <- grepl("TUNE-8", names(AllCounts))
AllCounts <- AllCounts[, !cols_to_remove]

cor_matrix <- cor(AllCounts,AllCounts, method = "pearson")
corrplot(cor_matrix, method="shade", tl.cex = 0.4, tl.col = "black", col=COL2('RdBu'))
```

```{r}
# Make the correlation matrix for Plate 22 only 
cols_to_keep <- grepl("P22", names(AllCounts))
temp <- AllCounts[, cols_to_keep]
cor_matrix <- cor(temp,temp, method = "pearson")
corrplot(cor_matrix, method="shade", tl.cex = 0.4, tl.col = "black", col=COL2('RdBu'))
```

```{r}
# Make the correlation matrix for Plate 27 only 
cols_to_keep <- grepl("P27", names(AllCounts))
temp <- AllCounts[, cols_to_keep]
cor_matrix <- cor(temp,temp, method = "pearson")
corrplot(cor_matrix, method="shade", tl.cex = 0.4, tl.col = "black", col=COL2('RdBu'))
```

```{r}
# Define seroreactivity for peptides in the Plate 22 samples 

selected_Plate22_columns <- grep("P22_", names(AllCounts), value = TRUE)
Plate22_counts <- AllCounts[, selected_Plate22_columns]

selected_PBS_columns <- grep("PBS", names(Plate22_counts), value = TRUE)
Plate22_counts_PBS <- Plate22_counts[, selected_PBS_columns]

Plate22_PBS_RPK <- sweep(Plate22_counts_PBS, 2, colSums(Plate22_counts_PBS), FUN = "/") * 1e5
Plate22_PBS_RPK$mean <-  apply(Plate22_PBS_RPK, 1, mean) 
Plate22_PBS_RPK$stdev <-  apply(Plate22_PBS_RPK, 1, sd) 
Plate22_PBS_RPK$LOD <- Plate22_PBS_RPK$mean + 5*Plate22_PBS_RPK$stdev

identifiers <- paste0("P22_",unique(str_extract(names(Plate22_counts), "TUNE-\\d+")))
identifiers <- identifiers[identifiers != "P22_NA"]

Plate22_VectorScan_All_results_list <- list()
Plate22_VectorScan_Discordance_results_list <-  list()
Plate22_VectorScan_ConcordantPeptides_results_list <- list()
Plate22_VectorScan_Seroreactive_results_list <- list()

# Loop over each identifier
for (identifier in identifiers) {
  Rep1_col <- paste0(identifier) 
  Rep2_col <- paste0(identifier, ".1") 
  
  selected_PBS_columns <- grep("PBS", names(Plate22_counts), value = TRUE)
  
  selected_sample_columns <- c(Rep1_col, Rep2_col, selected_PBS_columns) 

  Pt <- Plate22_counts[, selected_sample_columns]
  
  Pt$id <- VectorScan$id
  
  Pt$PBS_LOD <- Plate22_PBS_RPK$LOD
  
  # Get the RPK for each replicate 
  Pt$Rep1_RPK <- Pt[[Rep1_col]]/sum(Pt[[Rep1_col]])*1e5
  Pt$Rep2_RPK <- Pt[[Rep2_col]]/sum(Pt[[Rep2_col]])*1e5
  
  Pt <- inner_join(Pt, VectorScan, by = 'id')
    
  Pt$ForAlignment <- paste0(">", Pt$id, "_", Pt$Species, " ", Pt$`AA Sequence`)

  # To be seroreactive, both replicates from that sample need to be above the noise threshold 
  # Also enforcing a count limit, where the peptide needs a count >= 5
  
  rep1_high <- (Pt$Rep1_RPK > Pt$PBS_LOD) &  (Pt[[Rep1_col]] >= 5)
  rep2_high <- (Pt$Rep2_RPK > Pt$PBS_LOD)  &  (Pt[[Rep2_col]] >= 5)

  Pt$Seropositive <- ifelse(rep1_high == 1 & rep2_high == 1, 1, 0)
  
  # If the peptide is seronegative, want to determine if it's because the replicates are inconsistent (pos/neg v. neg/pos, vs. both negative)
  Pt$Discordant <- ifelse(Pt$Seropositive == 0 & (rep1_high != rep2_high), 1, 0)

  discordance_temp <- sum(Pt$Discordant)
  
  Plate22_VectorScan_Discordance_results_list[[identifier]] <- discordance_temp
 
  Plate22_VectorScan_All_results_list[[identifier]] <- Pt
  
  # Limit the peptides to the ones in the library that do not have long GS linkers and have representation in the original library
  # The number of peptides in this cleaned library (VectorScan_cleaned) should be the denominator for all future Fishers tests
  
  Pt <- inner_join(Pt, VectorScan_cleaned, by = 'id')
  
  # Want to limit the pool of peptides to ones that are concordant at both timepoints 
  
  Pt <- Pt[as.logical(Pt$Discordant == 0),]
  
  Pt$Average <- (Pt$Rep1_RPK + Pt$Rep2_RPK)/2
  
  Pt$Seropositive_Average <- Pt$Average * Pt$Seropositive
    
  Plate22_VectorScan_ConcordantPeptides_results_list[[identifier]] <- Pt
  
  Pt <- Pt[as.logical(Pt$Seropositive == 1),]
  
  Plate22_VectorScan_Seroreactive_results_list[[identifier]] <- Pt
  
}
```

```{r}
# Define seroreactivity for peptides in the Plate 27 samples 

selected_Plate27_columns <- grep("P27_", names(AllCounts), value = TRUE)
Plate27_counts <- AllCounts[, selected_Plate27_columns]

selected_PBS_columns <- grep("PBS", names(Plate27_counts), value = TRUE)
Plate27_counts_PBS <- Plate27_counts[, selected_PBS_columns]

Plate27_PBS_RPK <- sweep(Plate27_counts_PBS, 2, colSums(Plate27_counts_PBS), FUN = "/") * 1e5
Plate27_PBS_RPK$mean <-  apply(Plate27_PBS_RPK, 1, mean) 
Plate27_PBS_RPK$stdev <-  apply(Plate27_PBS_RPK, 1, sd) 
Plate27_PBS_RPK$LOD <- Plate27_PBS_RPK$mean + 5*Plate27_PBS_RPK$stdev

identifiers <- paste0("P27_",unique(str_extract(names(Plate27_counts), "TUNE-\\d+")))
identifiers <- identifiers[identifiers != "P27_NA"]

Plate27_VectorScan_All_results_list <- list()
Plate27_VectorScan_Discordance_results_list <-  list()
Plate27_VectorScan_ConcordantPeptides_results_list <- list()
Plate27_VectorScan_Seroreactive_results_list <- list()

# Loop over each identifier
for (identifier in identifiers) {
  Rep1_col <- paste0(identifier) 
  Rep2_col <- paste0(identifier, ".1") 
  
  selected_PBS_columns <- grep("PBS", names(Plate27_counts), value = TRUE)
  
  selected_sample_columns <- c(Rep1_col, Rep2_col, selected_PBS_columns) 

  Pt <- Plate27_counts[, selected_sample_columns]
  
  Pt$id <- VectorScan$id
  
  Pt$PBS_LOD <- Plate27_PBS_RPK$LOD
  
  # Get the RPK for each replicate 
  Pt$Rep1_RPK <- Pt[[Rep1_col]]/sum(Pt[[Rep1_col]])*1e5
  Pt$Rep2_RPK <- Pt[[Rep2_col]]/sum(Pt[[Rep2_col]])*1e5
  
  Pt <- inner_join(Pt, VectorScan, by = 'id')
    
  Pt$ForAlignment <- paste0(">", Pt$id, "_", Pt$Species, " ", Pt$`AA Sequence`)

  # To be seroreactive, both replicates from that sample need to be above the noise threshold 
  # Also enforcing a count limit, where the peptide needs a count >= 5
  
  rep1_high <- (Pt$Rep1_RPK > Pt$PBS_LOD) &  (Pt[[Rep1_col]] >= 5)
  rep2_high <-  (Pt$Rep2_RPK > Pt$PBS_LOD)  &  (Pt[[Rep2_col]] >= 5)
  
  Pt$Seropositive <- ifelse(rep1_high == 1 & rep2_high == 1, 1, 0)
  
  # If the peptide is seronegative, want to determine if it's because the replicates are inconsistent (pos/neg v. neg/pos, vs. both negative)
  Pt$Discordant <- ifelse(Pt$Seropositive == 0 & (rep1_high != rep2_high), 1, 0)

  discordance_temp <-  sum(Pt$Discordant)
  
  Plate27_VectorScan_Discordance_results_list[[identifier]] <- discordance_temp
 
  Plate27_VectorScan_All_results_list[[identifier]] <- Pt
  
  # Limit the peptides to the ones in the library that do not have long GS linkers and have representation in the original library
  # The number of peptides in this cleaned library (VectorScan_cleaned) should be the denominator for all future Fishers tests
  
  Pt <- inner_join(Pt, VectorScan_cleaned, by = 'id')
  
  # Want to limit the pool of peptides to ones that are concordant at both timepoints 
  
  Pt <- Pt[as.logical(Pt$Discordant == 0),]
  
  Pt$Average <- (Pt$Rep1_RPK + Pt$Rep2_RPK)/2
  
  Pt$Seropositive_Average <- Pt$Average * Pt$Seropositive
    
  Plate27_VectorScan_ConcordantPeptides_results_list[[identifier]] <- Pt
  
  Pt <- Pt[as.logical(Pt$Seropositive == 1),]
  
  Plate27_VectorScan_Seroreactive_results_list[[identifier]] <- Pt
  
}
```

```{r} 
# Combining the lists into single dataframes with the data from each sample that can be used to do all the downstream analyses
# Peptides that are seronegative in a sample have values artificially set to 0

Plate22_Seropositive_RPKs <- Plate22_VectorScan_ConcordantPeptides_results_list %>%
  map(~ dplyr::select(.x, id, Seropositive_Average)) %>% 
      bind_rows(.id = "Sample") %>%
          pivot_wider(
            names_from = Sample, 
            values_from = Seropositive_Average, 
            values_fill = 0  
          )

Plate22_Seropositive_RPKs <- Plate22_Seropositive_RPKs %>% relocate(id, .after = last_col())

Plate22_Seropositive_Binary <- Plate22_VectorScan_ConcordantPeptides_results_list %>%
    map(~ dplyr::select(.x, id, Seropositive)) %>% 
      bind_rows(.id = "Sample") %>%
          pivot_wider(
            names_from = Sample, 
            values_from = Seropositive, 
            values_fill = 0  
          )

Plate22_Seropositive_Binary <- Plate22_Seropositive_Binary %>% relocate(id, .after = last_col())

Plate27_Seropositive_RPKs <- Plate27_VectorScan_ConcordantPeptides_results_list %>%
  map(~ dplyr::select(.x, id, Seropositive_Average)) %>% 
      bind_rows(.id = "Sample") %>%
          pivot_wider(
            names_from = Sample, 
            values_from = Seropositive_Average, 
            values_fill = 0  
          )

Plate27_Seropositive_RPKs <- Plate27_Seropositive_RPKs %>% relocate(id, .after = last_col())

Plate27_Seropositive_Binary <- Plate27_VectorScan_ConcordantPeptides_results_list %>%
    map(~ dplyr::select(.x, id, Seropositive)) %>% 
      bind_rows(.id = "Sample") %>%
          pivot_wider(
            names_from = Sample, 
            values_from = Seropositive, 
            values_fill = 0  
          )

Plate27_Seropositive_Binary <- Plate27_Seropositive_Binary %>% relocate(id, .after = last_col())

Plates22and27_RPKs <- inner_join(Plate22_Seropositive_RPKs, Plate27_Seropositive_RPKs, by = 'id')

Plates22and27_RPKs <- Plates22and27_RPKs %>% relocate(id, .after = last_col())

Plates22and27_RPKs <- inner_join(Plates22and27_RPKs, VectorScan, by = 'id')

Plates22and27_Binary <- inner_join(Plate22_Seropositive_Binary, Plate27_Seropositive_Binary, by = 'id')

Plates22and27_Binary <- Plates22and27_Binary %>% relocate(id, .after = last_col())

Plates22and27_Binary <- inner_join(Plates22and27_Binary, VectorScan, by = 'id')
```

```{r}
# Manual checks of technical reproducibility after all this normalization

# Making sure that there is concordance between the actual quantitative RPK values when the same sample is run on different plates 
temp1 <- data.frame('P22_TUNE-32' = Plates22and27_RPKs$`P22_TUNE-32`, 'P27_TUNE-32' = Plates22and27_RPKs$`P27_TUNE-32`)
temp1 <- temp1[as.logical(rowSums(temp1)>0),]
plot(temp1[,1], temp1[,2])

# Making sure that there is concordance between the actual quantitative RPK values when the same sample is run on different plates 
temp1 <- data.frame('P22_TUNE-36' = Plates22and27_RPKs$`P22_TUNE-36`, 'P27_TUNE-36' = Plates22and27_RPKs$`P27_TUNE-36`)
temp1 <- temp1[as.logical(rowSums(temp1)>0),]
plot(temp1[,1], temp1[,2])

# Making sure that there is concordance between the actual quantitative RPK values when the same sample is run on different plates 
temp1 <- data.frame('P22_TUNE-68' = Plates22and27_RPKs$`P22_TUNE-68`, 'P27_TUNE-68' = Plates22and27_RPKs$`P27_TUNE-68`)
temp1 <- temp1[as.logical(rowSums(temp1)>0),]
plot(temp1[,1], temp1[,2])

# Making sure that there is concordance between the actual quantitative RPK values when the same sample is run on different plates 
temp1 <- data.frame('P22_TUNE-69' = Plates22and27_RPKs$`P22_TUNE-69`, 'P27_TUNE-69' = Plates22and27_RPKs$`P27_TUNE-69`)
temp1 <- temp1[as.logical(rowSums(temp1)>0),]
plot(temp1[,1], temp1[,2])

# Making sure that there is concordance between the actual quantitative RPK values when the same sample is run on different plates 
temp1 <- data.frame('P22_TUNE-70' = Plates22and27_RPKs$`P22_TUNE-70`, 'P27_TUNE-70' = Plates22and27_RPKs$`P27_TUNE-70`)
temp1 <- temp1[as.logical(rowSums(temp1)>0),]
plot(temp1[,1], temp1[,2])

# Making sure that there is concordance between the actual quantitative RPK values when the same sample is run on different plates 
temp1 <- data.frame('P22_TUNE-30' = Plates22and27_RPKs$`P22_TUNE-30`, 'P27_TUNE-30' = Plates22and27_RPKs$`P27_TUNE-30`)
temp1 <- temp1[as.logical(rowSums(temp1)>0),]
plot(temp1[,1], temp1[,2])

# Making sure that there is concordance between the actual quantitative RPK values when the same sample is run on different plates 
temp1 <- data.frame('P22_TUNE-75' = Plates22and27_RPKs$`P22_TUNE-75`, 'P27_TUNE-75' = Plates22and27_RPKs$`P27_TUNE-75`)
temp1 <- temp1[as.logical(rowSums(temp1)>0),]
plot(temp1[,1], temp1[,2])
```

```{r}
# Make the correlation matrix to see if the samples have consistent peptide-wise signal across plates 
# The samples that were run on both plates should have high correlation 

temp <- Plates22and27_RPKs[, 1:78]
temp <- temp[as.logical(rowSums(temp) >0),]
cor_matrix <- cor(temp,temp, method = "spearman")
corrplot(cor_matrix, method="shade", tl.cex = 0.4, tl.col = "black", col=COL2('RdBu'))
```

```{r}
# Average the RPKs for the samples that were run on both plates 

# Looking at all signal
Plates22and27_Combined <- Plates22and27_RPKs
Plates22and27_Combined$sum <- rowSums(Plates22and27_Combined[,1:78])

heatmap_data <- Plates22and27_Combined

# Average the RPKs for the samples that were run on both plates 
df <- Plates22and27_Combined[,1:78]

cols <- colnames(df)

tune_id <- sub(".*(TUNE\\-\\d+)$", "\\1", cols)
unique_ids <- unique(tune_id)

result <- data.frame(row_index = seq_len(nrow(df)))

for(id in unique_ids) {
  
  group_cols <- df[, tune_id == id, drop = FALSE]
  
  if (ncol(group_cols) == 1) {
    
    original_name <- colnames(group_cols)[1]
    result[[original_name]] <- group_cols[, 1]
  
  } else {
    
    averaged <- rowMeans(group_cols, na.rm = TRUE)
    newname <- paste0("P22and27_", id)
    result[[newname]] <- as.numeric(averaged)
  }
}

result$row_index <- NULL

result$id <- Plates22and27_Combined$id

Plates22and27_Combined <- result

Plates22and27_Combined <- inner_join(Plates22and27_Combined, VectorScan, by = 'id')

```

```{r}
# Can't save because some of the columns are tibbles
# to fix that: 

Plates22and27_Combined_df <- Plates22and27_Combined

is_df_col <- vapply(Plates22and27_Combined_df, is.data.frame, logical(1))
for (nm in names(Plates22and27_Combined_df)[is_df_col]) {
  Plates22and27_Combined_df[[nm]] <- Plates22and27_Combined_df[[nm]][[1]]
}

write_xlsx(Plates22and27_Combined_df, "Plates22and27_Combined_df.xlsx")
```

```{r}
Plates22and27_Combined <- read_xlsx('Plates22and27_Combined_df.xlsx')
```


```{r}
# To look at the seroprevalence of a particular peptide across all 62 samples 

peptide <- "245872"
temp <- Plates22and27_Combined[as.logical(Plates22and27_Combined$id == peptide),]
sum(temp[,1:62]>0)/62*100
```

```{r}
Plate22_metadata <- data.frame(Plate = c(rep('22', 39)), 
  Subject = c('TUNE-24','TUNE-25','TUNE-26','TUNE-27','TUNE-28','TUNE-29','TUNE-30','TUNE-31','TUNE-32','TUNE-33','TUNE-34','TUNE-35','TUNE-36','TUNE-37','TUNE-38','TUNE-39','TUNE-40','TUNE-41','TUNE-42','TUNE-43','TUNE-44','TUNE-45','TUNE-46','TUNE-47','TUNE-48','TUNE-50','TUNE-51','TUNE-52','TUNE-68','TUNE-69','TUNE-70','TUNE-71','TUNE-72','TUNE-73','TUNE-74','TUNE-75','TUNE-76','TUNE-77','TUNE-78'),
  Recent_Illness = c(rep('No', 39)),
  DENV_IgG = c('pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg'), 
  CHIKV_IgG = c('pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg'),
  DENV_IgM = c('not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','neg','neg','neg','neg','neg','not tested','not tested','not tested','not tested','not tested'), 
  CHIKV_IgM = c(rep('neg', 39)))

Plate27_metadata <- data.frame(Plate = c(rep('27', 39)), 
  Subject = c('TUNE-1','TUNE-10','TUNE-11','TUNE-12','TUNE-13','TUNE-14','TUNE-15','TUNE-16','TUNE-17','TUNE-18','TUNE-19','TUNE-2','TUNE-20','TUNE-21','TUNE-22','TUNE-23','TUNE-3','TUNE-30','TUNE-32','TUNE-35','TUNE-36','TUNE-37','TUNE-4','TUNE-5','TUNE-6','TUNE-68','TUNE-69','TUNE-7','TUNE-70','TUNE-71','TUNE-72','TUNE-73','TUNE-74','TUNE-75','TUNE-76','TUNE-77','TUNE-78','TUNE-79','TUNE-9'),
  Recent_Illness = c('No','Yes','Yes','Yes','Yes','Yes','Yes','Yes','Yes','Yes','Yes','No','Yes','Yes','Yes','Yes','No','No','No','No','No','No','No','Yes','Yes','No','No','Yes','No','No','No','No','No','No','No','No','No','No','Yes'),
  DENV_IgG = c('neg','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','neg','not tested','not tested','not tested','not tested','neg','pos','pos','pos','pos','pos','neg','not tested','not tested','neg','neg','not tested','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','not tested'), 
  CHIKV_IgG = c('pos','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','not tested','pos','not tested','not tested','not tested','not tested','pos','pos','pos','pos','pos','pos','pos','not tested','not tested','neg','neg','not tested','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','not tested'),
  DENV_IgM = c('not tested','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','not tested','neg','neg','neg','neg','not tested','not tested','not tested','not tested','not tested','not tested','not tested','neg','neg','not tested','neg','neg','neg','neg','neg','neg','not tested','not tested','not tested','not tested','not tested','not tested','neg'), 
  CHIKV_IgM = c('neg','pos','pos','pos','pos','pos','pos','pos','pos','pos','pos','neg','pos','pos','pos','pos','neg','neg','neg','neg','neg','neg','pos','pos','pos','neg','neg','pos','neg','neg','neg','neg','neg','neg','neg','neg','neg','neg','pos'))

# The TUNE-1 CHIKV IgM result was "eqv", so it is treated as negative since it is not positive but was tested 

# Joining all the metadata from the two plates together, and then fixing the resulting naming issues since the same column names are used in both dataframes 

Plates22and27_metadata <- full_join(Plate22_metadata, Plate27_metadata, by = "Subject")

Plates22and27_metadata <- Plates22and27_metadata %>%
  mutate(
    DENV_IgG = coalesce(DENV_IgG.x, DENV_IgG.y),
    CHIKV_IgG = coalesce(CHIKV_IgG.x, CHIKV_IgG.y),
    DENV_IgM = coalesce(DENV_IgM.x, DENV_IgM.y),
    CHIKV_IgM = coalesce(CHIKV_IgM.x, CHIKV_IgM.y),
    Recent_Illness = coalesce(Recent_Illness.x, Recent_Illness.y),
    Plate = coalesce(Plate.x, Plate.y)
  )

Plates22and27_metadata$Exposed <- (Plates22and27_metadata$CHIKV_IgG == "pos" | Plates22and27_metadata$DENV_IgG == "pos")
```

```{r}
# Measure CHIKV breadth 
temp <- Plates22and27_Combined[as.logical(Plates22and27_Combined$Species == "CV"),]
temp <- temp[,1:62]
counts_of_interest <- data.frame(
  column = names(temp),
  n_counts  = colSums(temp > 0, na.rm = TRUE))
counts_of_interest <- cbind(counts_of_interest, Plates22and27_metadata)
```

```{r}
# Measure DENV breadth 
temp <- Plates22and27_Combined[as.logical(Plates22and27_Combined$Species == "DV"),]
temp <- temp[,1:62]
counts_of_interest <- data.frame(
  column = names(temp),
  n_counts  = colSums(temp > 0, na.rm = TRUE))
counts_of_interest <- cbind(counts_of_interest, Plates22and27_metadata)
```

CHIKV IgG+ v IgG- analysis 

```{r}
# Species-wise Mann-Whitney tests for comparing CHIKV IgG+ v IgG-

temp <- Plates22and27_Combined[,1:62]
temp <- data.frame(t(temp))
colnames(temp) <- Plates22and27_Combined$id

# Only analyze signal from peptides that are seroreactive in at least 1 of the samples
temp <- temp[,as.logical(colSums(temp)>0)]
temp$CHIKV_IgG <- Plates22and27_metadata$CHIKV_IgG

temp_CHIKV_IgG_Pos <- temp[as.logical(temp$CHIKV_IgG == "pos"),]

CHIKV_IgG_means <- data.frame(Pos_Means = colMeans(temp_CHIKV_IgG_Pos[,1:(ncol(temp_CHIKV_IgG_Pos)-1)]))

temp_CHIKV_IgG_Neg <- temp[as.logical(temp$CHIKV_IgG == "neg"),]

CHIKV_IgG_means$Neg_means <- colMeans(temp_CHIKV_IgG_Neg[,1:(ncol(temp_CHIKV_IgG_Neg)-1)])

CHIKV_IgG_means$Diff <- log2((CHIKV_IgG_means$Pos_Means+0.1)/(CHIKV_IgG_means$Neg_means+0.1))

CHIKV_IgG_means <- CHIKV_IgG_means %>% arrange(-CHIKV_IgG_means$Diff)

CHIKV_IgG_means$rank <- seq(1, nrow(CHIKV_IgG_means))
CHIKV_IgG_means$id <- as.numeric(rownames(CHIKV_IgG_means))
CHIKV_IgG_means$Species <- VectorScan_cleaned$Species[match(CHIKV_IgG_means$id,VectorScan_cleaned$id)]

df <- CHIKV_IgG_means

# All relevant species 
species_vec <- unique(df$Species)

mw_results <- map_df(species_vec, function(sp) {
  
  # Label the peptides that are from the species that's being analyzed 
  df$flag <- (df$Species == sp)
  
  # Only run the Mann-Whitney analysis if there are more than 2 peptides, otherwise there's not a distribution to compare
  if (length(unique(df$flag)) < 2) {
    return(data.frame(
      Species   = sp,
      W         = NA_real_,
      p_value   = NA_real_
    ))
  }
  
  # Run the Mann-Whitney test 
  test_res <- wilcox.test(
    Diff ~ flag,
    data = df,
    alternative = "less"
  )
  
  # Results from the test 
  data.frame(
    Species = sp,
    W       = unname(test_res$statistic),
    p_value = test_res$p.value
  )
})

# Benjamini-Hochberg p-value adjustment 
mw_results$padj <- p.adjust(mw_results$p_value, method = "BH")

mw_results$log10adjusted <- -log10(mw_results$padj)

CHIKV_IgG_mw_results_Species <- mw_results

# Want to make the plot for CHIKV, specifically 

df$flag <- (df$Species == "CV" )

# Mann–Whitney test
mw_res <- wilcox.test(Diff ~ flag,
                      data = df, 
                      alternative = "less")  

# Print the p-value from this directed test 
mw_res$p.value

pval_lab <- paste0("Mann–Whitney p = ", signif(mw_res$p.value, 3))

ggplot(df, aes(x = rank, y = Diff)) +
  geom_jitter(
    data  = subset(df, flag == FALSE),
    color = "gray60",
    alpha = 0.1,
    size  = 1.5,
    height = 0.1
  ) +
  geom_jitter(
    data  = subset(df, flag == TRUE),
    color = "purple",
    alpha = 0.2,
    size  = 1.5,
    height = 0.1
  ) +
  labs(
    title = "Difference in signal between CHIKV IgG+/-",
    y = "Fold change difference",
    x = "Rank"
  ) +
  theme_minimal()

```

```{r}
# Species-wise Mann-Whitney tests for comparing DENV IgG+ v IgG-

temp <- Plates22and27_Combined[,1:62]
temp <- data.frame(t(temp))
colnames(temp) <- Plates22and27_Combined$id

# Only analyze signal from peptides that are seroreactive in at least 1 of the samples
temp <- temp[,as.logical(colSums(temp)>0)]
temp$DENV_IgG <- Plates22and27_metadata$DENV_IgG

temp_DENV_IgG_Pos <- temp[as.logical(temp$DENV_IgG == "pos"),]

DENV_IgG_means <- data.frame(Pos_Means = colMeans(temp_DENV_IgG_Pos[,1:(ncol(temp_DENV_IgG_Pos)-1)]))

temp_DENV_IgG_Neg <- temp[as.logical(temp$DENV_IgG == "neg"),]

DENV_IgG_means$Neg_means <- colMeans(temp_DENV_IgG_Neg[,1:(ncol(temp_DENV_IgG_Neg)-1)])

DENV_IgG_means$Diff <- log2((DENV_IgG_means$Pos_Means+0.1)/(DENV_IgG_means$Neg_means+0.1))

DENV_IgG_means <- DENV_IgG_means %>% arrange(-DENV_IgG_means$Diff)

DENV_IgG_means$rank <- seq(1, nrow(DENV_IgG_means))
DENV_IgG_means$id <- as.numeric(rownames(DENV_IgG_means))
DENV_IgG_means$Species <- VectorScan_cleaned$Species[match(DENV_IgG_means$id,VectorScan_cleaned$id)]

df <- DENV_IgG_means

# All relevant species 
species_vec <- unique(df$Species)

mw_results <- map_df(species_vec, function(sp) {
  
  # Label the peptides that are from the species that's being analyzed 
  df$flag <- (df$Species == sp)
  
  # Only run the Mann-Whitney analysis if there are more than 2 peptides, otherwise there's not a distribution to compare
  if (length(unique(df$flag)) < 2) {
    return(data.frame(
      Species   = sp,
      W         = NA_real_,
      p_value   = NA_real_
    ))
  }
  
  # Run the Mann-Whitney test 
  test_res <- wilcox.test(
    Diff ~ flag,
    data = df,
    alternative = "less"
  )
  
  # Results from the test 
  data.frame(
    Species = sp,
    W       = unname(test_res$statistic),
    p_value = test_res$p.value
  )
})

# Benjamini-Hochberg p-value adjustment 
mw_results$padj <- p.adjust(mw_results$p_value, method = "BH")

mw_results$log10adjusted <- -log10(mw_results$padj)

DENV_IgG_mw_results_Species <- mw_results

# Want to make the plot for DENV, specifically 

df$flag <- (df$Species == "DV" )

# Mann–Whitney test
mw_res <- wilcox.test(Diff ~ flag,
                      data = df, 
                      alternative = "less")  

# Print the p-value from this directed test 
mw_res$p.value

pval_lab <- paste0("Mann–Whitney p = ", signif(mw_res$p.value, 3))

ggplot(df, aes(x = rank, y = Diff)) +
  geom_jitter(
    data  = subset(df, flag == FALSE),
    color = "gray60",
    alpha = 0.1,
    size  = 1.5,
    height = 0.1
  ) +
  geom_jitter(
    data  = subset(df, flag == TRUE),
    color = "#7f2421",
    alpha = 0.2,
    size  = 1.5,
    height = 0.1
  ) +
  labs(
    title = "Difference in signal between DENV IgG+/-",
    y = "Fold change difference",
    x = "Rank"
  ) +
  theme_minimal()

```

```{r}
# Find all the CHIKV peptides that are seroreactive in any of the samples 
temp <- Plates22and27_Combined
temp <- temp[as.logical(temp$Species == "CV"),]
temp <- temp[as.logical(rowSums(temp[,1:62])>0),]
temp_ids <- temp$id 

CHIKV_peptides_of_interest <- data.frame(id = temp_ids)
CHIKV_peptides_of_interest <- inner_join(CHIKV_peptides_of_interest, VectorScan, by = 'id')

setwd('filepath')

# Create an AAStringSet object
seqs <- AAStringSet(CHIKV_peptides_of_interest$'AA Sequence')
  # Add names from the sequence header column
names(seqs) <- paste0(CHIKV_peptides_of_interest$id)
writeXStringSet(seqs, filepath = "CHIKV_peptides_of_interest.faa")

```

The commands used to run the blastp search: 

cd 'filepath' 

makeblastdb -in CHIKV_peptides_of_interest.faa -out db -parse_seqids -dbtype prot 
blastp -query CHIKV_peptides_of_interest.faa -db db -outfmt 6 -max_hsps 1 -out CHIKV_peptides_of_interest.txt 

awk 'BEGIN{FS="\t"; OFS=","} {print $1, $2, $3, $4, $5, $6, $7, $8, $9, $10, $11, $12}' CHIKV_peptides_of_interest.txt > CHIKV_peptides_of_interest.csv


```{r}
setwd('filepath')

# Get rid of  priors to make sure that the clustering is clean
rm(membership_df)
rm(membership_vector)
rm(edge_list)
rm(g)
rm(CHIKV_relevant_clusters)
rm(Plates22and27_CHIKV_cluster_sums)

# Cluster the peptides that come out of the blastp analysis 
Subject_BLAST <- read.csv('CHIKV_peptides_of_interest.csv', header = FALSE)
Subject_BLAST <- Subject_BLAST[as.logical(Subject_BLAST$V12 >= 40), ]

edge_list <- Subject_BLAST[, c("V1", "V2")]
g <- graph_from_data_frame(d = edge_list, directed = FALSE)
g <- simplify(g, remove.multiple = TRUE, remove.loops = TRUE)

# Do the Louvain clustering
set.seed(123)  # Makes the results reproducible for the sake of reproducing the findings in the paper, since sometimes the clustering can change by 1-2 clusters, which offsets the Cluster IDs 

clusters <- cluster_louvain(g)
membership_vector <- membership(clusters)

cluster_sizes <- table(membership_vector)

membership_df <- data.frame(
  name      = names(membership_vector),         
  ClusterID = as.integer(membership_vector),
  stringsAsFactors = FALSE
)

# Only keep clusters that have 2+ members, basically requiring that a peptide has similarity to another peptide to be included in downstream analyses 
cluster_threshold <- 2
valid_clusters <- names(cluster_sizes[cluster_sizes >= cluster_threshold])

vertices_to_keep <- which(membership_vector %in% valid_clusters)
g_filtered <- induced_subgraph(g, vids = vertices_to_keep)

filtered_membership_vector <- membership_vector[vertices_to_keep]

g_simplified <- simplify(g_filtered, remove.loops = TRUE)

vertex_names_plot <- V(g_simplified)$name
CHIKV_relevant_clusters <- membership_df %>%
  filter(name %in% vertex_names_plot)

CHIKV_relevant_clusters$id <- as.numeric(CHIKV_relevant_clusters$name)

# Get the RPK counts for all the peptides that ended up in clusters
CHIKV_relevant_clusters <- inner_join(CHIKV_relevant_clusters, Plates22and27_Combined, by = 'id')

# Calculate the cluster reactivity scores 
Plates22and27_CHIKV_cluster_sums <- CHIKV_relevant_clusters %>%
  group_by(ClusterID) %>%
  summarise(
    across(3:64, \(x) sum(x, na.rm = TRUE)),
    .groups = "drop"
  )
```

```{r}
temp <- Plates22and27_CHIKV_cluster_sums %>% as.data.frame()

heatmap_data <- temp[,2:63]
rownames(heatmap_data) <- as.character(temp$ClusterID)

annotation_col <- data.frame(
  DENV_IgG  = factor(Plates22and27_metadata$DENV_IgG, levels = c("pos", "neg", "not tested")),
  CHIKV_IgG = factor(Plates22and27_metadata$CHIKV_IgG, levels = c("pos", "neg", "not tested")),
  CHIKV_IgM = factor(Plates22and27_metadata$CHIKV_IgM, levels = c("pos", "neg", "not tested")) 
)
rownames(annotation_col) <- colnames(heatmap_data)

annotation_colors <- list(
  DENV_IgG = c("pos" = "#6c2525", "neg" = "lightgray",  "not tested" = '#a27d56'),
  CHIKV_IgG = c("pos" = "#5f308c", "neg" = "lightgray", "not tested" = "#a27d56"),
  CHIKV_IgM = c("pos" = "#b079ae", "neg" = "lightgray", "not tested" = "#a27d56")

)

# Order the columns to make interpretation more intuitive
# First CHIKV_IgG, then by DENV_IgG
ord <- order(annotation_col$CHIKV_IgG, annotation_col$DENV_IgG)

heatmap_data            <- heatmap_data[, ord]
annotation_col_ord  <- annotation_col[ord, ]

cutoff <- 100      # Set a cutoff for the score to make the colors of the heatmap more useful
n_col  <- 50       # Number of color steps below the cutoff

# Define the color palette: last color will be used for all values >= cutoff
my_cols <- colorRampPalette(c("white", "red", "purple"))(n_col)
min_val <- min(heatmap_data, na.rm = TRUE)
breaks <- seq(min_val, cutoff, length.out = n_col + 1)

pheatmap(
  (heatmap_data),
  cluster_rows = FALSE,
  cluster_cols = FALSE,
  show_rownames = TRUE, # each rowname is the Cluster ID 
  show_colnames = FALSE,
  border_color = NA,
  annotation_col = annotation_col_ord,
  annotation_colors = annotation_colors,
  color = my_cols,
  breaks = breaks,
  clustering_method = "average",
  fontsize_col = 6,
  main = "Cluster scores of each sample"
)
```

```{r}
# Find clusters with significantly different scores between CHIKV IgG+ and IgG- people 

# Set up the dataframe to do the tests
Plates22and27_CHIKV_cluster_sums_t <- data.frame(t(Plates22and27_CHIKV_cluster_sums[,2:63]))
colnames(Plates22and27_CHIKV_cluster_sums_t) <- Plates22and27_CHIKV_cluster_sums$ClusterID
Plates22and27_CHIKV_cluster_sums_t$Subject <- rownames(Plates22and27_CHIKV_cluster_sums_t)
Plates22and27_CHIKV_cluster_sums_t$CHIKV_IgG <- Plates22and27_metadata$CHIKV_IgG

df_long <- Plates22and27_CHIKV_cluster_sums_t %>%
  pivot_longer(
    cols = -c(Subject, CHIKV_IgG),        
    names_to  = "ClusterID",
    values_to = "value"
  ) %>%
  mutate(ClusterID = as.numeric(ClusterID)) 

# Run the Wilcoxon test on a cluster-wise basis 
wilcox_res <- df_long %>%
  filter(CHIKV_IgG %in% c('neg', 'pos')) %>%
  group_by(ClusterID) %>%
  summarise(
    p_value = wilcox.test(value ~ CHIKV_IgG)$p.value,
    .groups = "drop"
  ) %>%
  mutate(p_adj = p.adjust(p_value, method = "BH"))   # BH correction

# Calculate log2 fold‑change between IgG+ vs IgG- using means, to make a volcano plot
logfc_res <- df_long %>%
  filter(CHIKV_IgG %in% c("neg", "pos")) %>%
  group_by(ClusterID, CHIKV_IgG) %>%
  summarise(
    mean_val = mean(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from  = CHIKV_IgG,
    values_from = mean_val
  ) %>%
  mutate(
    log2FC_pos_vs_neg = log2((pos + 1) / (neg + 1))   
  )

# Combine things together to get a dataframe that can be used to make the volcano plot
wilcox_res <- wilcox_res %>%
  left_join(logfc_res, by = "ClusterID")

wilcox_res$log10 <- -log10(wilcox_res$p_adj)

# Keep only significant clusters
sig_clusters <- wilcox_res %>%
  filter(p_adj < 0.05) %>%
  pull(ClusterID)

df_long_sig <- df_long %>%
  filter(ClusterID %in% sig_clusters)

# Added this so I could take the values and plot them in GraphPad instead of using the R graphs below (for the sake of vectorization)
df_long_sig$log2 <- log2(df_long_sig$value+1)

# Plot the cluster reactivity scores for each sample 
ggplot(df_long_sig, aes(x = CHIKV_IgG, y = log2(value + 1), fill = CHIKV_IgG)) +
  scale_fill_manual(
    values = c("neg" = "gray", "not tested" = "#b079ae", "pos" = "#5f308c"),
    name   = "CHIKV_IgG"
  ) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(width = 0.15, alpha = 0.4, size = 1) +
  facet_wrap(~ ClusterID, scales = "free_y") +
  labs(
    x = "group",
    y = "Cluster sum (log2+1)",
    title = "Cluster values by group status"
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  )

```

```{r}
# Three significant clusters came out of this analysis 
# Want to align them to the CHIKV proteome to see what parts of the virus are being targeted by antibodies 

CHIKV_IgG_significant_clusters <- CHIKV_relevant_clusters[as.logical(CHIKV_relevant_clusters$ClusterID == "22" | 
                                                                              CHIKV_relevant_clusters$ClusterID == "23" |
                                                                              CHIKV_relevant_clusters$ClusterID == "24"),]

CHIKV_IgG_significant_clusters$ForAlignment <- paste0(">", CHIKV_IgG_significant_clusters$id, " ", CHIKV_IgG_significant_clusters$`AA Sequence`)

setwd('filepath')

# Create an AAStringSet object
seqs <- AAStringSet(CHIKV_IgG_significant_clusters$'AA Sequence')
  # Add names from the sequence header column
names(seqs) <- paste0(CHIKV_IgG_significant_clusters$id, "_Cluster", CHIKV_IgG_significant_clusters$ClusterID)
writeXStringSet(seqs, filepath = "CHIKV_IgG_significant_clusters.faa")
```

cd 'filepath' 

makeblastdb -in CHIKV_Structural_Polyprotein.faa -out db -parse_seqids -dbtype prot 
blastp -query CHIKV_IgG_significant_clusters.faa -db db -outfmt 6 -max_hsps 1 -out CHIKV_IgG_significant_clusters.txt 

awk 'BEGIN{FS="\t"; OFS=","} {print $1, $2, $3, $4, $5, $6, $7, $8, $9, $10, $11, $12}' CHIKV_IgG_significant_clusters.txt > CHIKV_IgG_significant_clusters.csv

```{r}
CHIKV_IgG_significant_clusters_peptides <- read.csv('filepath/CHIKV_IgG_significant_clusters.csv', header=FALSE)
CHIKV_IgG_significant_clusters_peptides$seq_id <- CHIKV_IgG_significant_clusters_peptides[,1]

CHIKV_IgG_significant_clusters_peptides <- CHIKV_IgG_significant_clusters_peptides %>%
  separate( col   = seq_id, into  = c("id"), sep   = "_", remove = TRUE ) %>% mutate(id = as.numeric(id)  )

CHIKV_IgG_significant_clusters_peptides$Species <- VectorScan$Species[match(CHIKV_IgG_significant_clusters_peptides$id, VectorScan$id)]
CHIKV_IgG_significant_clusters_peptides$Protein <- VectorScan$Protein[match(CHIKV_IgG_significant_clusters_peptides$id, VectorScan$id)]
CHIKV_IgG_significant_clusters_peptides$AA <- VectorScan$'AA Sequence'[match(CHIKV_IgG_significant_clusters_peptides$id, VectorScan$id)]
CHIKV_IgG_significant_clusters_peptides$ForAlignment <- paste0(">", CHIKV_IgG_significant_clusters_peptides$V2, " ",CHIKV_IgG_significant_clusters_peptides$AA)
CHIKV_IgG_significant_clusters_peptides$AANumber <- CHIKV_IgG_significant_clusters_peptides$V9  + (CHIKV_IgG_significant_clusters_peptides$V8 - CHIKV_IgG_significant_clusters_peptides$V7)/2
CHIKV_IgG_significant_clusters_peptides$ClusterID <- CHIKV_IgG_significant_clusters$ClusterID[match(CHIKV_IgG_significant_clusters_peptides$id, CHIKV_IgG_significant_clusters$id)]

CHIKV_IgG_significant_clusters_peptides <- CHIKV_IgG_significant_clusters_peptides[as.logical(CHIKV_IgG_significant_clusters_peptides$ClusterID != "1"),]
```

```{r}
# Looking at the peptides that make up Cluster 22, specifically 

CHIKV_IgG_cluster22 <- CHIKV_IgG_significant_clusters[as.logical(CHIKV_IgG_significant_clusters$ClusterID == "22"),]

temp <- CHIKV_IgG_cluster22

heatmap_data <- temp[,4:65]
rownames(heatmap_data) <- temp$id

annotation_col <- data.frame(
  DENV_IgG  = factor(Plates22and27_metadata$DENV_IgG, levels = c("pos", "neg", "not tested")),
  CHIKV_IgG = factor(Plates22and27_metadata$CHIKV_IgG, levels = c("pos", "neg", "not tested")),
  CHIKV_IgM = factor(Plates22and27_metadata$CHIKV_IgM, levels = c("pos", "neg", "not tested")) 
)
rownames(annotation_col) <- colnames(heatmap_data)


annotation_colors <- list(
  DENV_IgG = c("pos" = "#6c2525", "neg" = "lightgray",  "not tested" = '#a27d56'),
  CHIKV_IgG = c("pos" = "#5f308c", "neg" = "lightgray", "not tested" = "#a27d56"),
  CHIKV_IgM = c("pos" = "#b079ae", "neg" = "lightgray", "not tested" = "#a27d56")

)

ord <- order(annotation_col$CHIKV_IgG, annotation_col$DENV_IgG)
heatmap_data            <- heatmap_data[, ord]
annotation_col_ord  <- annotation_col[ord, ]

cutoff <- 500
n_col  <- 50 

my_cols <- colorRampPalette(c("white", "red", "purple"))(n_col)
min_val <- min(heatmap_data, na.rm = TRUE)
breaks <- seq(min_val, cutoff, length.out = n_col + 1)

pheatmap(
  (heatmap_data),
  cluster_rows = FALSE,
  cluster_cols = FALSE,
  show_rownames = TRUE,
  show_colnames = FALSE,
  border_color = NA,
  annotation_col = annotation_col,
  annotation_colors = annotation_colors,
  color = my_cols,
  breaks = breaks,
  clustering_method = "average",
  fontsize_col = 6,
  main = "Cluster reactivity scores of each sample"
)
```

Use the same proteome to compare where the ElliPro hits are:

ElliPro E2
hit 1: YKCNCGGSNEGLTTTDKVINNCKVDQCH
hit 2: LSYRNMGEEPNYQEEWVMHKKEVVLTVPTEGLEVT

E1 
hit 1: DYSCKVFTGVYPFMWGGAYCFCDAENTQLSE

cd 'filepath' 

makeblastdb -in CHIKV_Structural_Polyprotein.faa -out db -parse_seqids -dbtype prot 
blastp -query ElliPro_CV_hits.faa -db db -outfmt 6 -max_hsps 1 -out ElliPro_CV_hits.txt 

awk 'BEGIN{FS="\t"; OFS=","} {print $1, $2, $3, $4, $5, $6, $7, $8, $9, $10, $11, $12}' ElliPro_CV_hits.txt > ElliPro_CV_hits.csv

```{r}
ElliPro_CV_hits <- read.csv('filepath/ElliPro_CV_hits.csv', header=FALSE)
ElliPro_CV_hits$seq_id <- ElliPro_CV_hits[,1]
```


CHIKV IgM+ v IgM- analysis -- Mosquito focused 

```{r}
# Find all the mosquito-derived peptides that are seroreactive in at least 1 sample 
temp <- Plates22and27_Combined
temp <- temp[as.logical(temp$Group == "Mosquito"),]
temp <- temp[as.logical(rowSums(temp[,1:62])>0),]

counts_of_interest <- data.frame(
  column = names(temp[,1:62]),
  n_counts  = colSums(temp[,1:62] > 0, na.rm = TRUE))
counts_of_interest <- cbind(counts_of_interest, Plates22and27_metadata)

# To get the mosquito breadth
depth <- data.frame(
  column = names(temp[,1:62]),
  n_counts  = colSums(temp[,1:62], na.rm = TRUE))
depth <- cbind(depth, Plates22and27_metadata)

# Set up everything to do clustering of the mosquito peptides 

temp_ids <- temp$id 

Mosquito_peptides_of_interest <- data.frame(id = temp_ids)
Mosquito_peptides_of_interest <- inner_join(Mosquito_peptides_of_interest, VectorScan, by = 'id')

setwd('filepath')

# Create an AAStringSet object
seqs <- AAStringSet(Mosquito_peptides_of_interest$'AA Sequence')
  # Add names from the sequence header column
names(seqs) <- paste0(Mosquito_peptides_of_interest$id)
writeXStringSet(seqs, filepath = "Mosquito_peptides_of_interest.faa")
```

cd 'filepath' 

makeblastdb -in Mosquito_peptides_of_interest.faa -out db -parse_seqids -dbtype prot 
blastp -query Mosquito_peptides_of_interest.faa -db db -outfmt 6 -max_hsps 1 -out Mosquito_peptides_of_interest.txt 

awk 'BEGIN{FS="\t"; OFS=","} {print $1, $2, $3, $4, $5, $6, $7, $8, $9, $10, $11, $12}' Mosquito_peptides_of_interest.txt > Mosquito_peptides_of_interest.csv

```{r}
# Make the clusters, using the same base code as above 

rm(membership_df)
rm(membership_vector)
rm(edge_list)
rm(g)
rm(Mosquito_relevant_clusters)
rm(Plates22and27_Mosquito_cluster_sums)

setwd('filepath')

Subject_BLAST <- read.csv('Mosquito_peptides_of_interest.csv', header = FALSE)
Subject_BLAST <- Subject_BLAST[as.logical(Subject_BLAST$V12 >= 40), ]

edge_list <- Subject_BLAST[, c("V1", "V2")]
g <- graph_from_data_frame(d = edge_list, directed = FALSE)
g <- simplify(g, remove.multiple = TRUE, remove.loops = TRUE)

set.seed(123)  
clusters <- cluster_louvain(g)
membership_vector <- membership(clusters)

cluster_sizes <- table(membership_vector)

membership_df <- data.frame(
  name      = names(membership_vector),          
  ClusterID = as.integer(membership_vector),
  stringsAsFactors = FALSE
)

cluster_threshold <- 2
valid_clusters <- names(cluster_sizes[cluster_sizes >= cluster_threshold])

vertices_to_keep <- which(membership_vector %in% valid_clusters)
g_filtered <- induced_subgraph(g, vids = vertices_to_keep)

filtered_membership_vector <- membership_vector[vertices_to_keep]

g_simplified <- simplify(g_filtered, remove.loops = TRUE)

vertex_names_plot <- V(g_simplified)$name
Mosquito_relevant_clusters <- membership_df %>%
  filter(name %in% vertex_names_plot)

Mosquito_relevant_clusters$id <- as.numeric(Mosquito_relevant_clusters$name)

Mosquito_relevant_clusters <- inner_join(Mosquito_relevant_clusters, Plates22and27_Combined, by = 'id')

Plates22and27_Mosquito_cluster_sums <- Mosquito_relevant_clusters %>%
  group_by(ClusterID) %>%
  summarise(
    across(3:64, \(x) sum(x, na.rm = TRUE)),
    .groups = "drop"
  )
```


```{r}
temp <- Plates22and27_Mosquito_cluster_sums

heatmap_data <- temp[,2:63]
rownames(heatmap_data) <- temp$ClusterID

annotation_col <- data.frame(
  DENV_IgG  = factor(Plates22and27_metadata$DENV_IgG, levels = c("pos", "neg", "not tested")),
  CHIKV_IgG = factor(Plates22and27_metadata$CHIKV_IgG, levels = c("pos", "neg", "not tested")),
  CHIKV_IgM = factor(Plates22and27_metadata$CHIKV_IgM, levels = c("pos", "neg", "not tested")) 
)
rownames(annotation_col) <- colnames(heatmap_data)


annotation_colors <- list(
  DENV_IgG = c("pos" = "#6c2525", "neg" = "lightgray",  "not tested" = '#a27d56'),
  CHIKV_IgG = c("pos" = "#5f308c", "neg" = "lightgray", "not tested" = "#a27d56"),
  CHIKV_IgM = c("pos" = "#b079ae", "neg" = "lightgray", "not tested" = "#a27d56")

)

ord <- order(annotation_col$CHIKV_IgG, annotation_col$DENV_IgG)
heatmap_data            <- heatmap_data[, ord]
annotation_col_ord  <- annotation_col[ord, ]

cutoff <- 50
n_col  <- 50

my_cols <- colorRampPalette(c("white", "red", "purple"))(n_col)
min_val <- min(heatmap_data, na.rm = TRUE)
breaks <- seq(min_val, cutoff, length.out = n_col + 1)

pheatmap(
  (heatmap_data),
  cluster_rows = TRUE,
  cluster_cols = FALSE,
  show_rownames = FALSE,
  show_colnames = FALSE,
  border_color = NA,
  annotation_col = annotation_col,
  annotation_colors = annotation_colors,
  color = my_cols,
  breaks = breaks,
  clustering_method = "average",
  fontsize_col = 6,
  main = "Cluster scores of each sample"
)

```

```{r}
# Find the clusters that have a significant difference in scores between IgM+ and IgM- people 

Plates22and27_Mosquito_cluster_sums_t <- data.frame(t(Plates22and27_Mosquito_cluster_sums[,2:63]))
colnames(Plates22and27_Mosquito_cluster_sums_t) <- Plates22and27_Mosquito_cluster_sums$ClusterID
Plates22and27_Mosquito_cluster_sums_t$Subject <- rownames(Plates22and27_Mosquito_cluster_sums_t)
Plates22and27_Mosquito_cluster_sums_t$CHIKV_IgM <- Plates22and27_metadata$CHIKV_IgM

df_long <- Plates22and27_Mosquito_cluster_sums_t %>%
  pivot_longer(
    cols = -c(Subject, CHIKV_IgM),
    names_to  = "ClusterID",
    values_to = "value"
  )

wilcox_res <- df_long %>%
  filter(CHIKV_IgM %in% c('neg', 'pos')) %>%
  group_by(ClusterID) %>%
  summarise(
    p_value = wilcox.test(value ~ CHIKV_IgM)$p.value,
    .groups = "drop"
  ) %>%
  mutate(p_adj = p.adjust(p_value, method = "BH"))   # FDR correction

logfc_res <- df_long %>%
  filter(CHIKV_IgM %in% c("neg", "pos")) %>%
  group_by(ClusterID, CHIKV_IgM) %>%
  summarise(
    median_val = mean(value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from  = CHIKV_IgM,
    values_from = median_val
  ) %>%
  mutate(
    log2FC_pos_vs_neg = log2((pos + 1) / (neg + 1)) 
  )

wilcox_res <- wilcox_res %>%
  left_join(logfc_res, by = "ClusterID")

wilcox_res$`-log10(padj)` <- -log10(wilcox_res$p_adj)
  
sig_clusters <- wilcox_res %>%
  filter(p_adj < 0.05) %>%
  pull(ClusterID)

df_long_sig <- df_long %>%
  filter(ClusterID %in% sig_clusters)

df_long_sig$log2 <- log2(df_long_sig$value+1)

# This is a much bigger list of clusters, so saving it externally to be able to make the volcano plot in GraphPad 
setwd('filepath')
write_xlsx(wilcox_res, "Mosquito_wilcox_res.xlsx")

wilcox_res$Significant <- (wilcox_res$p_adj < 0.05)
p_threshold <- 0.05 

ggplot(wilcox_res, aes(x = log2FC_pos_vs_neg, y = -log10(p_adj), color = Significant)) +
  geom_point(alpha = 1) +
  scale_color_manual(values = c("gray", "red")) +
  geom_vline(xintercept = c(0), linetype = "dashed", color = "gray") +
  geom_hline(yintercept = -log10(p_threshold), linetype = "dashed", color = "gray") +
  theme_minimal() +
  theme(panel.grid.major = element_blank()) +
  labs(
    x = "log2 Fold Change (IgM+ vs. IgM-)",
    y = "-log10(padj)",
    title = "Volcano Plot: CHIKV IgM+ vs IgM-"
  )

ggplot(df_long_sig, aes(x = CHIKV_IgM, y = log2(value + 1), fill = CHIKV_IgM)) +
  scale_fill_manual(
    values = c("neg" = "gray", "pos" = "#b079ae"),
    name   = "CHIKV_IgG"
  ) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(width = 0.15, alpha = 0.4, size = 1) +
  facet_wrap(~ ClusterID, scales = "free_y") +
  labs(
    x = "group",
    y = "Cluster sum (log2)",
    title = "Cluster values by group status"
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  )
```

```{r}
# Looking more at the mosquito-derived clusters

Mosquito_IgM_significant_clusters <- Mosquito_relevant_clusters[as.logical(Mosquito_relevant_clusters$ClusterID == "1574" | 
                                                                              Mosquito_relevant_clusters$ClusterID == "3568"),]

Mosquito_IgM_significant_clusters$ForAlignment <- paste0(">", Mosquito_IgM_significant_clusters$id, " ", Mosquito_IgM_significant_clusters$`AA Sequence`)
```

```{r}
temp <- Mosquito_IgM_significant_clusters[as.logical(Mosquito_IgM_significant_clusters$ClusterID == "1574"),]

heatmap_data <- temp[,4:65]
rownames(heatmap_data) <- temp$id

annotation_col <- data.frame(
  DENV_IgG  = factor(Plates22and27_metadata$DENV_IgG, levels = c("pos", "neg", "not tested")),
  CHIKV_IgG = factor(Plates22and27_metadata$CHIKV_IgG, levels = c("pos", "neg", "not tested")),
  CHIKV_IgM = factor(Plates22and27_metadata$CHIKV_IgM, levels = c("pos", "neg", "not tested")) 
)
rownames(annotation_col) <- colnames(heatmap_data)


annotation_colors <- list(
  DENV_IgG = c("pos" = "#6c2525", "neg" = "lightgray",  "not tested" = '#a27d56'),
  CHIKV_IgG = c("pos" = "#5f308c", "neg" = "lightgray", "not tested" = "#a27d56"),
  CHIKV_IgM = c("pos" = "#b079ae", "neg" = "lightgray", "not tested" = "#a27d56")

)

ord <- order(annotation_col$CHIKV_IgG, annotation_col$DENV_IgG)
heatmap_data            <- heatmap_data[, ord]
annotation_col_ord  <- annotation_col[ord, ]

cutoff <- 50
n_col  <- 50

my_cols <- colorRampPalette(c("white", "red", "purple"))(n_col)
min_val <- min(heatmap_data, na.rm = TRUE)
breaks <- seq(min_val, cutoff, length.out = n_col + 1)

pheatmap(
  (heatmap_data),
  cluster_rows = FALSE,
  cluster_cols = FALSE,
  show_rownames = TRUE,
  show_colnames = FALSE,
  border_color = NA,
  annotation_col = annotation_col,
  annotation_colors = annotation_colors,
  color = my_cols,
  breaks = breaks,
  clustering_method = "average",
  fontsize_col = 6,
  main = "Cluster scores of each sample"
)
```

```{r}
temp <- Mosquito_IgM_significant_clusters[as.logical(Mosquito_IgM_significant_clusters$ClusterID == "3568"),]

heatmap_data <- temp[,4:65]
rownames(heatmap_data) <- temp$id

annotation_col <- data.frame(
  DENV_IgG  = factor(Plates22and27_metadata$DENV_IgG, levels = c("pos", "neg", "not tested")),
  CHIKV_IgG = factor(Plates22and27_metadata$CHIKV_IgG, levels = c("pos", "neg", "not tested")),
  CHIKV_IgM = factor(Plates22and27_metadata$CHIKV_IgM, levels = c("pos", "neg", "not tested")) 
)
rownames(annotation_col) <- colnames(heatmap_data)


annotation_colors <- list(
  DENV_IgG = c("pos" = "#6c2525", "neg" = "lightgray",  "not tested" = '#a27d56'),
  CHIKV_IgG = c("pos" = "#5f308c", "neg" = "lightgray", "not tested" = "#a27d56"),
  CHIKV_IgM = c("pos" = "#b079ae", "neg" = "lightgray", "not tested" = "#a27d56")

)

ord <- order(annotation_col$CHIKV_IgG, annotation_col$DENV_IgG)
heatmap_data            <- heatmap_data[, ord]
annotation_col_ord  <- annotation_col[ord, ]

cutoff <- 50
n_col  <- 50

my_cols <- colorRampPalette(c("white", "red", "purple"))(n_col)
min_val <- min(heatmap_data, na.rm = TRUE)
breaks <- seq(min_val, cutoff, length.out = n_col + 1)

pheatmap(
  (heatmap_data),
  cluster_rows = FALSE,
  cluster_cols = FALSE,
  show_rownames = TRUE,
  show_colnames = FALSE,
  border_color = NA,
  annotation_col = annotation_col,
  annotation_colors = annotation_colors,
  color = my_cols,
  breaks = breaks,
  clustering_method = "average",
  fontsize_col = 6,
  main = "Cluster scores of each sample"
)
```

```{r}
# Do the fisher tests to determine whether specific genera are overrepresented among the peptides in these clusters 

df <- Mosquito_IgM_significant_clusters # The peptides that are in these significant clusters
larger_set <- Mosquito_relevant_clusters # All peptides that clustered 

families <- sort(unique(larger_set$Family))

fisher_results_list <- lapply(families, function(group_to_test) {
  
  df2 <- df[df$Family == group_to_test, ]
  
  temp1 <- nrow(df2) # Clustered & in genus X 
  temp2 <- nrow(larger_set[larger_set$Family == group_to_test, ]) - temp1  # Not clustered & in genus X
  temp3 <- nrow(df) - temp1 # Clustered & not in genus X
  temp4 <- nrow(larger_set) - temp1 - temp2 - temp3  # Not clustered & not in genus X
  
  contingency_table <- matrix(c(temp1, temp2,
                                temp3, temp4),
                              nrow = 2,
                              byrow = TRUE,
                              dimnames = list(
                                Clustered = c("Yes", "No"),
                                Family    = c(group_to_test, "Other")
                              ))
  
  ft <- fisher.test(contingency_table)
  
  data.frame(
    Family       = group_to_test,
    clustered_in_genus  = temp1,
    not_clustered_in_genus   = temp2,
    clustered_not_genus = temp3,
    not_clustered_not_genus  = temp4,
    odds_ratio  = unname(ft$estimate),
    conf_low           = ft$conf.int[1],
    conf_high          = ft$conf.int[2],
    p_value     = ft$p.value,
    stringsAsFactors = FALSE
  )
})

fisher_results <- do.call(rbind, fisher_results_list)
fisher_results$p_adj <- p.adjust(fisher_results$p_value, method = "bonferroni") # Chose bonferroni because there is a small number of comparisons
fisher_results$significant <- fisher_results$p_adj < 0.05
fisher_results
```


