```{r}
# Load relevant libraries 
library(Biostrings)
library('dplyr')
library('corrplot')
library('writexl')
library('readxl')
library('seqinr')
library(ggplot2)
library(gridExtra)
library(ggfortify)
library(pheatmap)
library(Biostrings)
library(tidyverse)
library(igraph)
library(RColorBrewer)
library(reshape2)
library(ggvenn)
library(eulerr)
```

ANALYSIS OF NHP DATA (PLATE 13)
----

After getting the demultiplexed fastq files back from the Bauer core, the following workflow was used to align to bowtie 

In terminal: 
cd [[Path to fastq files]]

Cut off the first part so that only the actual peptide part is there:
for fq in *.fastq.gz; do cutadapt -g TCCAGTCAGGTGTGATGCTCGGGGATCCAGGAATTCGGAGCGGT -o ${fq%%.*}.cut.fastq.gz $fq; done 

```{r}
Bowtie_38bp_fasta <- data.frame(id = VectorScan$id, Seq = substr(VectorScan$'DNA Sequence', 1, 38))
seqs <- AAStringSet(Bowtie_38bp_fasta$Seq)
names(seqs) <- paste0(Bowtie_38bp_fasta$id)
writeXStringSet(seqs, filepath ="VectorScan_Bowtie_38bp.fasta")
```

In terminal again: 

Make the bowtie2 index: 
bowtie2-build -f VectorScan_Bowtie_38bp.fasta VectorScan_38bp

Perform the alignment: 
for fq in *.cut.fastq.gz; do bowtie2 -x VectorScan_38bp --very-sensitive -U $fq -S ${fq%%.*}.sam; done

Turn into count files
for i in *.sam; do samtools view -bS $i > ${i%.*}.bam; done
for i in *.bam; do samtools sort $i -o ${i%.*}.sorted.bam; done
for i in *.sorted.bam; do samtools index $i; done
for i in *.sorted.bam; do samtools idxstats $i | cut -f 1,3 | gsed -e'/^\*\t/d' -e'1 i id\t'${i%%.*}| tr "\\t" "," > ${i%%.*}.count.csv; done

Gzip the counts files with the following command.
for i in *count.csv; do gzip $i; done

Combine the count files together for each sample

for i in *L001_R1_001.count.csv.gz; do python combine_two_lanes.py $i ${i%1_R1_001.count.csv.gz}2_R1_001.count.csv.gz ${i%1_R1_001.count.csv.gz}1_2_R1_001.count.csv; done

for i in *L003_R1_001.count.csv.gz; do python combine_two_lanes.py $i ${i%3_R1_001.count.csv.gz}4_R1_001.count.csv.gz ${i%3_R1_001.count.csv.gz}3_4_R1_001.count.csv; done

for i in *L001_2_R1_001.count.csv; do python combine_two_lanes.py $i ${i%1_2_R1_001.count.csv}3_4_R1_001.count.csv ${i%1_2_R1_001.count.csv}1_2_3_4_R1_001.count.combined.csv; done

Combine all the count files together 
paste -d ',' *.count.combined.csv >2024_11_12_VectorScan_Plate13_VectorScan_counts.csv

Read in the library and the cleaned library to do analysis 
```{r}
setwd('/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision')
VectorScan <- read_xlsx("VectorScan_Library_1_2.xlsx")  ## Path to the library file
VectorScan_cleaned <- read_xlsx("VectorScan_cleaned.xlsx") ## Path to the cleaned library file generated via "Plate 07 analysis" code
```

```{r}
# Read in the counts file. Each column is a replicate, each row is a peptide in the library.
Plate13_VectorScan_counts <- read.csv("/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision/Data to upload/2024_11_12_VectorScan_Plate13_VectorScan_counts.csv")
cols_to_remove <- grepl("id", names(Plate13_VectorScan_counts))
Plate13_VectorScan_counts_cleaned <- Plate13_VectorScan_counts[, !cols_to_remove]
colnames(Plate13_VectorScan_counts_cleaned) <- make.unique(c('PBS', 'PBS', 'PI1', 'PI1', 'PI2', 'PI2', 'PBS', 'PBS', 'PI4', 'PI4', 'EI1', 'EI1', 'EI2', 'EI2', 'EI3', 'EI3', 'EI4', 'EI4', 'LI1', 'LI1', 'LI2', 'LI2', 'LI3', 'LI3', 'LI4', 'LI4', 'PBS', 'PBS'))
cols_to_remove <- grepl("I3", colnames(Plate13_VectorScan_counts_cleaned))
Plate13_VectorScan_counts_cleaned <- Plate13_VectorScan_counts_cleaned[,!cols_to_remove]
```

```{r}
desired_order <- c('PI1', 'PI1.1', 'EI1', 'EI1.1', 'LI1', 'LI1.1', 'PI2', 'PI2.1', 'EI2', 'EI2.1', 'LI2', 'LI2.1','PI4', 'PI4.1', 'EI4', 'EI4.1', 'LI4', 'LI4.1', 'PBS', 'PBS.1', 'PBS.2', 'PBS.3', 'PBS.4', 'PBS.5')
temp <- Plate13_VectorScan_counts_cleaned
temp <- temp[, desired_order, drop = FALSE]
cor_matrix <- cor(temp,temp, method = "pearson")
corrplot(cor_matrix, method="shade", tl.cex = 1, tl.col = "black", col=COL2('RdBu'))
```

```{r}
selected_PBS_columns <- grep("PBS", names(Plate13_VectorScan_counts_cleaned), value = TRUE)
Plate13_PBS <- Plate13_VectorScan_counts_cleaned[, selected_PBS_columns]

Plate13_PBS_RPK <- sweep(Plate13_PBS, 2, colSums(Plate13_PBS), FUN = "/") * 1e5
Plate13_PBS_RPK$mean <-  apply(Plate13_PBS_RPK, 1, mean) 
Plate13_PBS_RPK$stdev <-  apply(Plate13_PBS_RPK, 1, sd) 
Plate13_PBS_RPK$LOD <- Plate13_PBS_RPK$mean + 5*Plate13_PBS_RPK$stdev
```

```{r}
identifiers <- c('I1', 'I2', 'I4')

# Placeholder for results
Plate13_VectorScan_All_results_list <- list()
Plate13_VectorScan_Seroreactive_results_list <- list()
Plate13_VectorScan_Discordance_results_list <-  list()
Plate13_VectorScan_ConcordantPeptides_results_list <- list()
Plate13_VectorScan_Seroreactive_results_list <- list()
Plate13_VectorScan_Up_EarlyvPre_list <- list()
Plate13_VectorScan_Up_LatevPre_list <- list()
Plate13_VectorScan_Up_LatevEarly_list <- list()
Plate13_VectorScan_Up_PostExposure_Generally_list <- list()
Plate13_VectorScan_Seroconverted_post_exposure_list <- list()

for (identifier in identifiers) {
  # Subset columns containing the specific identifier substring
  
  PreImmune_Rep1_col <- paste0("P",identifier)  
  PreImmune_Rep2_col <- paste0("P",identifier, ".1")
  EarlyImmune_Rep1_col <- paste0("E",identifier)
  EarlyImmune_Rep2_col <- paste0("E",identifier, ".1")
  LateImmune_Rep1_col <- paste0("L",identifier)
  LateImmune_Rep2_col <- paste0("L",identifier,".1")
  
  selected_PBS_columns <- grep("PBS", names(Plate13_VectorScan_counts_cleaned), value = TRUE)
  
  selected_sample_columns <- c(PreImmune_Rep1_col, PreImmune_Rep2_col,
                       EarlyImmune_Rep1_col, EarlyImmune_Rep2_col,
                       LateImmune_Rep1_col, LateImmune_Rep2_col,
                       selected_PBS_columns) 
  
  Pt <- Plate13_VectorScan_counts_cleaned[, selected_sample_columns]
  Pt$id <- VectorScan$id
  
  Pt$PBS_LOD <- Plate13_PBS_RPK$LOD

  # To compare between timepoints, first take the RPK for each sample 

  Pt$PreImmune_Rep1_RPK <- Pt[[PreImmune_Rep1_col]]/sum(Pt[[PreImmune_Rep1_col]])*1e5
  Pt$PreImmune_Rep2_RPK <- Pt[[PreImmune_Rep2_col]]/sum(Pt[[PreImmune_Rep2_col]])*1e5
  
  Pt$EarlyImmune_Rep1_RPK <- Pt[[EarlyImmune_Rep1_col]]/sum(Pt[[EarlyImmune_Rep1_col]])*1e5
  Pt$EarlyImmune_Rep2_RPK <- Pt[[EarlyImmune_Rep2_col]]/sum(Pt[[EarlyImmune_Rep2_col]])*1e5
  
  Pt$LateImmune_Rep1_RPK <- Pt[[LateImmune_Rep1_col]]/sum(Pt[[LateImmune_Rep1_col]])*1e5
  Pt$LateImmune_Rep2_RPK <- Pt[[LateImmune_Rep2_col]]/sum(Pt[[LateImmune_Rep2_col]])*1e5


  # Find peptides that are seropositive at each timepoint 
  
  # To be seropositive, both replicates from that sample need to be above their noise threshold 
    # Also enforcing a count limit, where the peptide needs a count >= 5
  
 # Pre-immune 
  rep1_high <- (Pt$PreImmune_Rep1_RPK > Pt$PBS_LOD) & (Pt[[PreImmune_Rep1_col]]>=5)
  rep2_high <- (Pt$PreImmune_Rep2_RPK > Pt$PBS_LOD) & (Pt[[PreImmune_Rep2_col]]>=5)
  
  Pt$PreImmune_seropositive <- ifelse(rep1_high == 1 & rep2_high == 1, 1, 0)
  Pt$PreImmune_Discordant <- ifelse(Pt$PreImmune_seropositive == 0 & (rep1_high != rep2_high), 1, 0)
  
   # Early-immune 
  rep1_high <- (Pt$EarlyImmune_Rep1_RPK > Pt$PBS_LOD) & (Pt[[EarlyImmune_Rep1_col]]>=5)
  rep2_high <- (Pt$EarlyImmune_Rep2_RPK > Pt$PBS_LOD) & (Pt[[EarlyImmune_Rep2_col]]>=5)
  
  Pt$EarlyImmune_seropositive <- ifelse(rep1_high == 1 & rep2_high == 1, 1, 0)
  Pt$EarlyImmune_Discordant <- ifelse(Pt$EarlyImmune_seropositive == 0 & (rep1_high != rep2_high), 1, 0)

   # Late-immune 
  rep1_high <- (Pt$LateImmune_Rep1_RPK > Pt$PBS_LOD) & (Pt[[LateImmune_Rep1_col]]>=5)
  rep2_high <- (Pt$LateImmune_Rep2_RPK > Pt$PBS_LOD) & (Pt[[LateImmune_Rep2_col]]>=5)
  
  Pt$LateImmune_seropositive <- ifelse(rep1_high == 1 & rep2_high == 1, 1, 0)
  Pt$LateImmune_Discordant <- ifelse(Pt$LateImmune_seropositive == 0 & (rep1_high != rep2_high), 1, 0)

   Pt$Discordant_in_all <- ifelse(Pt$PreImmune_Discordant == 1 & Pt$EarlyImmune_Discordant == 1 & Pt$LateImmune_Discordant == 1, 1, 0)
   
  discordance_temp <- data.frame(PreImmune = sum(Pt$PreImmune_Discordant), EarlyImmune = sum(Pt$EarlyImmune_Discordant), LateImmune = sum(Pt$LateImmune_Discordant), All = sum(Pt$Discordant_in_all))
 
  Plate13_VectorScan_Discordance_results_list[[identifier]] <- discordance_temp
 
  Plate13_VectorScan_All_results_list[[identifier]] <- Pt
    
  # Limit the peptides to the ones in the library that do not have long GS linkers and have representation in the original library
  # The number of peptides in this cleaned library (VectorScan_cleaned) should be the denominator for all future Fishers tests
  
  Pt <- inner_join(Pt, VectorScan_cleaned, by = 'id')
  
  Pt$ForAlignment <- paste0(">", Pt$id, "_", Pt$Species, " ", Pt$`AA Sequence`)
  
  # Want to limit the pool of peptides to ones that are concordant at all timepoints 
  
  Pt <- Pt[as.logical(Pt$PreImmune_Discordant == 0),]
  Pt <- Pt[as.logical(Pt$EarlyImmune_Discordant == 0),]
  Pt <- Pt[as.logical(Pt$LateImmune_Discordant == 0),]
    
  Pt$PreImmune_Avg <- (Pt$PreImmune_Rep1_RPK + Pt$PreImmune_Rep2_RPK)/2
  Pt$EarlyImmune_Avg <- (Pt$EarlyImmune_Rep1_RPK + Pt$EarlyImmune_Rep2_RPK)/2
  Pt$Early_v_Pre_Difference <- (Pt$EarlyImmune_Avg+0.1) / (Pt$PreImmune_Avg+0.1)
  
  Pt$LateImmune_Avg <- (Pt$LateImmune_Rep1_RPK + Pt$LateImmune_Rep2_RPK)/2
  Pt$Late_v_Pre_Difference <- (Pt$LateImmune_Avg+0.1) / (Pt$PreImmune_Avg+0.1)
  
  Pt$Late_v_Early_Difference <- (Pt$LateImmune_Avg+0.1) / (Pt$EarlyImmune_Avg+0.1)
  
  Pt$PreImmune_Seropositive_Average <- Pt$PreImmune_Avg * Pt$PreImmune_seropositive
  Pt$EarlyImmune_Seropositive_Average <- Pt$EarlyImmune_Avg * Pt$EarlyImmune_seropositive
  Pt$LateImmune_Seropositive_Average <- Pt$LateImmune_Avg * Pt$LateImmune_seropositive
  
  Plate13_VectorScan_ConcordantPeptides_results_list[[identifier]] <- Pt
  
  # Then want to limit the pool to ones that are seroreactive at one of the timepoints 
  
  Pt <- Pt[as.logical(Pt$PreImmune_seropositive == 1 | Pt$EarlyImmune_seropositive == 1 | Pt$LateImmune_seropositive == 1),]
  
  # To find peptides that have seroconverted beteween the Early timepoint compared to the pre timepoint
  Pt$Seroconverted_Pre_to_Early <- ifelse(Pt$PreImmune_seropositive == 0 & Pt$EarlyImmune_seropositive == 1, 1, 0)

  # To find peptides that have seroconverted beteween the Late timepoint compared to the pre timepoint
  Pt$Seroconverted_Pre_to_Late <- ifelse(Pt$PreImmune_seropositive == 0 & Pt$LateImmune_seropositive == 1, 1, 0)
   
  Plate13_VectorScan_Seroreactive_results_list[[identifier]] <- Pt
  
  Plate13_VectorScan_Seroconverted_post_exposure_list[[identifier]] <- Pt[as.logical(Pt$Seroconverted_Pre_to_Early == 1 | Pt$Seroconverted_Pre_to_Late == 1 ),]
}
  
```

```{r}
Plate13_PreImmune_Seropositive_RPKs <- Plate13_VectorScan_ConcordantPeptides_results_list %>%
  map(~ dplyr::select(.x, id, PreImmune_Seropositive_Average)) %>% 
      bind_rows(.id = "Sample") %>%
          pivot_wider(
            names_from = Sample, 
            values_from = PreImmune_Seropositive_Average, 
            values_fill = 0  
          )

colnames(Plate13_PreImmune_Seropositive_RPKs) <- c('id', 'DENV1_Pre', 'DENV2_Pre', 'DENV4_Pre')

Plate13_EarlyImmune_Seropositive_RPKs <- Plate13_VectorScan_ConcordantPeptides_results_list %>%
  map(~ dplyr::select(.x, id, EarlyImmune_Seropositive_Average)) %>% 
      bind_rows(.id = "Sample") %>%
          pivot_wider(
            names_from = Sample, 
            values_from = EarlyImmune_Seropositive_Average, 
            values_fill = 0  
          )

colnames(Plate13_EarlyImmune_Seropositive_RPKs) <- c('id', 'DENV1_Early', 'DENV2_Early', 'DENV4_Early')

Plate13_LateImmune_Seropositive_RPKs <- Plate13_VectorScan_ConcordantPeptides_results_list %>%
  map(~ dplyr::select(.x, id, LateImmune_Seropositive_Average)) %>% 
      bind_rows(.id = "Sample") %>%
          pivot_wider(
            names_from = Sample, 
            values_from = LateImmune_Seropositive_Average, 
            values_fill = 0  
          )

colnames(Plate13_LateImmune_Seropositive_RPKs) <- c('id', 'DENV1_Late', 'DENV2_Late', 'DENV4_Late')

Plate13_AllTimepointsTogether_Seropositive_RPKs <- Plate13_PreImmune_Seropositive_RPKs
Plate13_AllTimepointsTogether_Seropositive_RPKs <- full_join(Plate13_AllTimepointsTogether_Seropositive_RPKs, Plate13_EarlyImmune_Seropositive_RPKs)
Plate13_AllTimepointsTogether_Seropositive_RPKs <- full_join(Plate13_AllTimepointsTogether_Seropositive_RPKs, Plate13_LateImmune_Seropositive_RPKs)
```

```{r}
setwd('/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision/Data to upload/')
write_xlsx(Plate13_AllTimepointsTogether_Seropositive_RPKs, "Plate13_AllTimepointsTogether_Seropositive_RPKs.xlsx")
```

```{r}
# To make the correlation plots 

desired_order <- c('DENV1_Pre', 'DENV1_Early', 'DENV1_Late', 'DENV2_Pre', 'DENV2_Early', 'DENV2_Late','DENV4_Pre', 'DENV4_Early', 'DENV4_Late')
temp <- Plate13_AllTimepointsTogether_Seropositive_RPKs[,2:ncol(Plate13_AllTimepointsTogether_Seropositive_RPKs)]
temp <- temp[, desired_order, drop = FALSE]
temp <- temp[as.logical(rowSums(temp) >0),]

cor_matrix <- cor(temp,temp, method = "pearson")

corrplot(
  cor_matrix,
  method = "shade",
  tl.cex = 1,
  tl.col = "black",
  col = COL2("RdBu")
)

cor_matrix <- cor(temp,temp, method = "spearman")

corrplot(
  cor_matrix,
  method = "shade",
  tl.cex = 1,
  tl.col = "black",
  col = COL2("RdBu")
)


temp2 <- temp[,1:3]
temp2 <- temp2[as.logical(rowSums(temp2) >0),]
nrow(temp2)
cor_matrix <- cor(temp2,temp2, method = "spearman")

corrplot(
  cor_matrix,
  method = "shade",
  tl.cex = 1,
  tl.col = "black",
  col = COL2("RdBu"),
  col.lim = c(0,1)
)

temp2 <- temp[,4:6]
temp2 <- temp2[as.logical(rowSums(temp2) >0),]
nrow(temp2)
cor_matrix <- cor(temp2,temp2, method = "spearman")

corrplot(
  cor_matrix,
  method = "shade",
  tl.cex = 1,
  tl.col = "black",
  col = COL2("RdBu"),
  col.lim = c(-0.1,1)
)

temp2 <- temp[,7:9]
temp2 <- temp2[as.logical(rowSums(temp2) >0),]
nrow(temp2)
cor_matrix <- cor(temp2,temp2, method = "spearman")

corrplot(
  cor_matrix,
  method = "shade",
  tl.cex = 1,
  tl.col = "black",
  col = COL2("RdBu"),
  col.lim = c(0,1)
)
```

```{r}
# To get the venn diagram in Fig. 2B 

NHP1_Hits <- Plate13_VectorScan_Seroreactive_results_list[["I1"]]

NHP2_Hits <- Plate13_VectorScan_Seroreactive_results_list[["I2"]]

NHP4_Hits <- Plate13_VectorScan_Seroreactive_results_list[["I4"]]

venn_list <- list(
  NHP1 = NHP1_Hits$id,
  NHP2 = NHP2_Hits$id,
  NHP4 = NHP4_Hits$id
)

fit <- euler(venn_list)  # computes area‑proportional diagram

plot(
  fit,
  fills = list(fill = c("#96362E", "#CB713C", "#A6C392"), alpha = 0.6),
  quantities = list(cex = 1.2),
  labels = list(font = 2, 
                cex = 1.6)
)
```

```{r}
# To get 2D & 2E 

NHP1_Hits <- Plate13_VectorScan_Seroreactive_results_list[["I1"]]

temp1 <- NHP1_Hits[as.logical(NHP1_Hits$PreImmune_seropositive == 1 ),]
temp1 <- temp1[as.logical(temp1$Species == "DV"),]
print(nrow(temp1))

temp2 <- NHP1_Hits[as.logical(NHP1_Hits$EarlyImmune_seropositive == 1 ),]
temp2 <- temp2[as.logical(temp2$Species == "DV"),]
print(nrow(temp2))

temp3 <- NHP1_Hits[as.logical(NHP1_Hits$LateImmune_seropositive == 1 ),]
temp3 <- temp3[as.logical(temp3$Species == "DV"),]
print(nrow(temp3))

temp2_long <- temp2 %>%
  dplyr::select(PreImmune_Avg, EarlyImmune_Avg, LateImmune_Avg) %>%
  pivot_longer(
    cols = everything(),
    names_to = "Timepoint",
    values_to = "Value"
  )

temp2_long$log2_value <- log2(temp2_long$Value+1)

temp2_long$Timepoint <- factor(
  temp2_long$Timepoint,
  levels = c("PreImmune_Avg", "EarlyImmune_Avg", "LateImmune_Avg")
)

NHP1_EarlyTimepoints <- temp2_long
NHP1_EarlyTimepoints <- NHP1_EarlyTimepoints %>% arrange(NHP1_EarlyTimepoints$Timepoint)
write_xlsx(NHP1_EarlyTimepoints, "NHP1_EarlyTimepoints.xlsx")
```

```{r}
NHP2_Hits <- Plate13_VectorScan_Seroreactive_results_list[["I2"]]

temp1 <- NHP2_Hits[as.logical(NHP2_Hits$PreImmune_seropositive == 1 ),]
temp1 <- temp1[as.logical(temp1$Species == "DV"),]
print(nrow(temp1))

temp2 <- NHP2_Hits[as.logical(NHP2_Hits$EarlyImmune_seropositive == 1 ),]
temp2 <- temp2[as.logical(temp2$Species == "DV"),]
print(nrow(temp2))

temp3 <- NHP2_Hits[as.logical(NHP2_Hits$LateImmune_seropositive == 1 ),]
temp3 <- temp3[as.logical(temp3$Species == "DV"),]
print(nrow(temp3))

temp2_long <- temp2 %>%
  dplyr::select(PreImmune_Avg, EarlyImmune_Avg, LateImmune_Avg) %>%
  pivot_longer(
    cols = everything(),
    names_to = "Timepoint",
    values_to = "Value"
  )

temp2_long$log2_value <- log2(temp2_long$Value+1)

temp2_long$Timepoint <- factor(
  temp2_long$Timepoint,
  levels = c("PreImmune_Avg", "EarlyImmune_Avg", "LateImmune_Avg")
)

NHP2_EarlyTimepoints <- temp2_long
NHP2_EarlyTimepoints <- NHP2_EarlyTimepoints %>% arrange(NHP2_EarlyTimepoints$Timepoint)
write_xlsx(NHP2_EarlyTimepoints, "NHP2_EarlyTimepoints.xlsx")
```

```{r}
NHP4_Hits <- Plate13_VectorScan_Seroreactive_results_list[["I4"]]

temp1 <- NHP4_Hits[as.logical(NHP4_Hits$PreImmune_seropositive == 1 ),]
temp1 <- temp1[as.logical(temp1$Species == "DV"),]
print(nrow(temp1))

temp2 <- NHP4_Hits[as.logical(NHP4_Hits$EarlyImmune_seropositive == 1 ),]
temp2 <- temp2[as.logical(temp2$Species == "DV"),]
print(nrow(temp2))

temp3 <- NHP4_Hits[as.logical(NHP4_Hits$LateImmune_seropositive == 1 ),]
temp3 <- temp3[as.logical(temp3$Species == "DV"),]
print(nrow(temp3))

temp2_long <- temp2 %>%
  dplyr::select(PreImmune_Avg, EarlyImmune_Avg, LateImmune_Avg) %>%
  pivot_longer(
    cols = everything(),
    names_to = "Timepoint",
    values_to = "Value"
  )

temp2_long$log2_value <- log2(temp2_long$Value+1)

temp2_long$Timepoint <- factor(
  temp2_long$Timepoint,
  levels = c("PreImmune_Avg", "EarlyImmune_Avg", "LateImmune_Avg")
)

NHP4_EarlyTimepoints <- temp2_long
NHP4_EarlyTimepoints <- NHP4_EarlyTimepoints %>% arrange(NHP4_EarlyTimepoints$Timepoint)
write_xlsx(NHP4_EarlyTimepoints, "NHP4_EarlyTimepoints.xlsx")
```

Species level Mann-Whitney analysis: Early v Pre
```{r}
species_vec <- unique(VectorScan_cleaned$Species)

run_mw_for_df <- function(df, species_vec) {
  df <- df %>%
    arrange(-Early_v_Pre_Difference)

  df$rank      <- seq_len(nrow(df))
  df$log2_diff <- log2(df$Early_v_Pre_Difference)

  mw_results <- map_df(species_vec, function(sp) {

    df$flag <- (df$Species == sp)

    if (length(unique(df$flag)) < 2) {
      return(data.frame(
        Species = sp,
        W       = NA_real_,
        p_value = NA_real_
      ))
    }

    test_res <- wilcox.test(
      log2_diff ~ flag,
      data = df,
      alternative = "less"
    )

    data.frame(
      Species = sp,
      W       = unname(test_res$statistic),
      p_value = test_res$p.value
    )
  })

  mw_results$Signif        <- mw_results$p_value <= 0.05
  mw_results$padj          <- p.adjust(mw_results$p_value, method = "BH")
  mw_results$log10adjusted <- -log10(mw_results$padj)

  mw_results
}

Plate13_mw_results_all <- imap_dfr(
  Plate13_VectorScan_Seroreactive_results_list,
  ~ run_mw_for_df(.x, species_vec) %>%
      mutate(Sample = .y),   
  .id = NULL
)

Plate13_mw_Early_v_Pre_results_all_Species <- Plate13_mw_results_all

Plate13_mw_Early_v_Pre_results_all_Species$padj_global <- p.adjust(Plate13_mw_Early_v_Pre_results_all_Species$p_value, method = "BH")

Plate13_mw_Early_v_Pre_results_all_Species$`-log10p` <- -log10(Plate13_mw_Early_v_Pre_results_all_Species$padj_global)

Plate13_mw_Early_v_Pre_results_all_Species$Significant <- Plate13_mw_Early_v_Pre_results_all_Species$`-log10p` >=1.3

Plate13_mw_Early_v_Pre_results_all_Species$Group <- VectorScan$Group[match(Plate13_mw_Early_v_Pre_results_all_Species$Species, VectorScan$Species)]

Plate13_mw_Early_v_Pre_results_all_Species <- Plate13_mw_Early_v_Pre_results_all_Species %>% arrange(Plate13_mw_Early_v_Pre_results_all_Species$Group) %>% arrange(Plate13_mw_Early_v_Pre_results_all_Species$Sample)

write_xlsx(Plate13_mw_Early_v_Pre_results_all_Species, '/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision/Data to upload/Plate13_mw_Early_v_Pre_results_all_Species.xlsx')
```

Species level Mann-Whitney analysis: Late v Pre
```{r}
run_mw_for_df <- function(df, species_vec) {
  df <- df %>%
    arrange(-Late_v_Pre_Difference)

  df$rank      <- seq_len(nrow(df))
  df$log2_diff <- log2(df$Late_v_Pre_Difference)

  mw_results <- map_df(species_vec, function(sp) {

    df$flag <- (df$Species == sp)

    if (length(unique(df$flag)) < 2) {
      return(data.frame(
        Species = sp,
        W       = NA_real_,
        p_value = NA_real_
      ))
    }

    test_res <- wilcox.test(
      log2_diff ~ flag,
      data = df,
      alternative = "less"
    )

    data.frame(
      Species = sp,
      W       = unname(test_res$statistic),
      p_value = test_res$p.value
    )
  })

  mw_results$Signif        <- mw_results$p_value <= 0.05
  mw_results$padj          <- p.adjust(mw_results$p_value, method = "BH")
  mw_results$log10adjusted <- -log10(mw_results$padj)

  mw_results
}

Plate13_mw_results_all <- imap_dfr(
  Plate13_VectorScan_Seroreactive_results_list,
  ~ run_mw_for_df(.x, species_vec) %>%
      mutate(Sample = .y),   # .y is the list element name (e.g. "I2")
  .id = NULL
)

# after you have one big data frame with every sample and species
Plate13_mw_Late_v_Pre_results_all_Species <- Plate13_mw_results_all

Plate13_mw_Late_v_Pre_results_all_Species$padj_global <- p.adjust(Plate13_mw_Late_v_Pre_results_all_Species$p_value, method = "BH")

Plate13_mw_Late_v_Pre_results_all_Species$`-log10p` <- -log10(Plate13_mw_Late_v_Pre_results_all_Species$padj_global)

Plate13_mw_Late_v_Pre_results_all_Species$Significant <- Plate13_mw_Late_v_Pre_results_all_Species$`-log10p` >=1.3

Plate13_mw_Late_v_Pre_results_all_Species$Group <- VectorScan$Group[match(Plate13_mw_Late_v_Pre_results_all_Species$Species, VectorScan$Species)]

Plate13_mw_Late_v_Pre_results_all_Species <- Plate13_mw_Late_v_Pre_results_all_Species %>% arrange(Plate13_mw_Late_v_Pre_results_all_Species$Group) %>% arrange(Plate13_mw_Late_v_Pre_results_all_Species$Sample)

write_xlsx(Plate13_mw_Late_v_Pre_results_all_Species, '/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision/Data to upload/Plate13_mw_Late_v_Pre_results_all_Species.xlsx')
```

```{r}
# NHP 1
df <- Plate13_VectorScan_Seroreactive_results_list[["I1"]] %>%
  arrange(-Early_v_Pre_Difference)

df$rank      <- seq_len(nrow(df))
df$log2_diff <- log2(df$Early_v_Pre_Difference)

df$flag <- (df$Species == "DV" )

 mw_res <- wilcox.test(log2_diff ~ flag,
                       data = df, 
                       alternative = "less")  
mw_res$p.value

pval_lab <- paste0("Mann–Whitney p = ", signif(mw_res$p.value, 3))

ggplot(df, aes(x = rank, y = log2_diff)) +
  geom_jitter(
    data  = subset(df, flag == FALSE),
    color = "gray60",
    alpha = 0.1,
    size  = 1.5,
    height = 0.1
  ) +
  geom_jitter(
    data  = subset(df, flag == TRUE),
    color = "#7f2421",
    alpha = 0.2,
    size  = 1.5,
    height = 0.1
  ) +
  labs(
    title = "Peptides seropositive at any timepoint: NHP1",
    y = "log2(Fold change in RPK\npre-immune v. early-immune)",
    x = "Rank"
  ) +
  theme_minimal()

```

Mapping back the hits to the DENV genome 

```{r}
setwd("/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision/NHP")
VectorScan_Dengue <- VectorScan_cleaned[as.logical(VectorScan_cleaned$Species == "DV"),]
VectorScan_Dengue_Proteins <- data.frame(unique(VectorScan_Dengue$Protein))

# Create an AAStringSet object
seqs <- AAStringSet(VectorScan_Dengue$'AA Sequence')
  # Add names from the sequence header column
names(seqs) <- VectorScan_Dengue$id
writeXStringSet(seqs, filepath = "VectorScan_Dengue.faa")
```

In terminal: 
 cd '/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision/NHP'
 
makeblastdb -in DENV1.faa -out db -parse_seqids -dbtype prot
blastp -query VectorScan_Dengue.faa -db db -outfmt 6 -max_hsps 1 -out VectorScan_Dengue1.txt
awk 'BEGIN{FS="\t"; OFS=","} {print $1, $2, $3, $4, $5, $6, $7, $8, $9, $10, $11, $12}' VectorScan_Dengue1.txt > VectorScan_Dengue1.csv

makeblastdb -in DENV2.faa -out db -parse_seqids -dbtype prot
blastp -query VectorScan_Dengue.faa -db db -outfmt 6 -max_hsps 1 -out VectorScan_Dengue2.txt
awk 'BEGIN{FS="\t"; OFS=","} {print $1, $2, $3, $4, $5, $6, $7, $8, $9, $10, $11, $12}' VectorScan_Dengue2.txt > VectorScan_Dengue2.csv

makeblastdb -in DENV4.faa -out db -parse_seqids -dbtype prot
blastp -query VectorScan_Dengue.faa -db db -outfmt 6 -max_hsps 1 -out VectorScan_Dengue4.txt
awk 'BEGIN{FS="\t"; OFS=","} {print $1, $2, $3, $4, $5, $6, $7, $8, $9, $10, $11, $12}' VectorScan_Dengue4.txt > VectorScan_Dengue4.csv

```{r}
DENV1_peptides <- read.csv('/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision/NHP/VectorScan_Dengue1.csv', header=FALSE)
DENV1_peptides$id <- DENV1_peptides[,1]
DENV1_peptides$Species <- VectorScan$Species[match(DENV1_peptides$id, VectorScan$id)]
DENV1_peptides$Protein <- VectorScan$Protein[match(DENV1_peptides$id, VectorScan$id)]
DENV1_peptides$AA <- VectorScan$'AA Sequence'[match(DENV1_peptides$id, VectorScan$id)]
DENV1_peptides$ForAlignment <- paste0(">", DENV1_peptides$V2, " ",DENV1_peptides$AA)
DENV1_peptides$AANumber <- DENV1_peptides$V9  + (DENV1_peptides$V8 - DENV1_peptides$V7)/2

DENV2_peptides <- read.csv('/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision/NHP/VectorScan_Dengue2.csv', header=FALSE)
DENV2_peptides$id <- DENV2_peptides[,1]
DENV2_peptides$Species <- VectorScan$Species[match(DENV2_peptides$id, VectorScan$id)]
DENV2_peptides$Protein <- VectorScan$Protein[match(DENV2_peptides$id, VectorScan$id)]
DENV2_peptides$AA <- VectorScan$'AA Sequence'[match(DENV2_peptides$id, VectorScan$id)]
DENV2_peptides$ForAlignment <- paste0(">", DENV2_peptides$V2, " ",DENV2_peptides$AA)
DENV2_peptides$AANumber <- DENV2_peptides$V9  + (DENV2_peptides$V8 - DENV2_peptides$V7)/2

DENV4_peptides <- read.csv('/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision/NHP/VectorScan_Dengue4.csv', header=FALSE)
DENV4_peptides$id <- DENV4_peptides[,1]
DENV4_peptides$Species <- VectorScan$Species[match(DENV4_peptides$id, VectorScan$id)]
DENV4_peptides$Protein <- VectorScan$Protein[match(DENV4_peptides$id, VectorScan$id)]
DENV4_peptides$AA <- VectorScan$'AA Sequence'[match(DENV4_peptides$id, VectorScan$id)]
DENV4_peptides$ForAlignment <- paste0(">", DENV4_peptides$V2, " ",DENV4_peptides$AA)
DENV4_peptides$AANumber <- DENV4_peptides$V9  + (DENV4_peptides$V8 - DENV4_peptides$V7)/2

combined_data <- full_join(DENV1_peptides, DENV2_peptides, by = 'id')
combined_data <- full_join(combined_data, DENV4_peptides, by = 'id')
VectorScan_Dengue_PercentIDtoSerotypes <- data.frame('id' = combined_data$id, 'DENV1_Percent' = combined_data$V3.x, 'DENV2_Percent' = combined_data$V3.y, 'DENV4_Percent' = combined_data$V3)
VectorScan_Dengue_PercentIDtoSerotypes[is.na(VectorScan_Dengue_PercentIDtoSerotypes)] <- 0
write_xlsx(combined_data, "/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision/NHP/VectorScan_Dengue_PercentIDtoSerotypes.xlsx")
```

```{r}
df1 <- DENV1_peptides
df2 <- DENV2_peptides
df4 <- DENV4_peptides

combined_data <- bind_rows(
  df1 %>% mutate(Source = "DENV1"),
  df2 %>% mutate(Source = "DENV2"),
  df4 %>% mutate(Source = "DENV4")
)

combined_data$Source <- as.factor(combined_data$Source)

plot <- ggplot(combined_data, aes(x = AANumber, fill = Source)) +
  geom_density(alpha = 0.5, adjust = 0.05) +  
  labs(title = "Density Plot of all Dengue-derived peptides",
       x = "AANumber",
       y = "Density",
       fill = "Source") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0, max(combined_data$AANumber, na.rm = TRUE), by = 100)) + 
  scale_fill_manual(values = c("DENV1" = "#96362E", "DENV2" = "#CB713C", "DENV4" = "#A6C392")) +
      geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 114, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 280, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 775, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 1127, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 1345, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 1475, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 2093, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 2220, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 2243, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 2491, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 3391, linetype = "dashed", color = "black", size = 0.2) +
  theme(legend.position = c(.85, .85), 
        panel.grid = element_blank(),
        panel.border = element_rect(color = 'black', fill = NA, size = .25),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) 

print(plot)
```


```{r}
# To make Fig. 2G

NHP1_df <- Plate13_VectorScan_Seroreactive_results_list[["I1"]] %>%
  mutate(
    NHP      = "NHP1",
    AANumber = DENV1_peptides$AANumber[match(id, DENV1_peptides$id)]
  ) %>%
  filter(!is.na(AANumber))

NHP2_df <- Plate13_VectorScan_Seroreactive_results_list[["I2"]] %>%
  mutate(
    NHP      = "NHP2",
    AANumber = DENV2_peptides$AANumber[match(id, DENV2_peptides$id)]
  ) %>%
  filter(!is.na(AANumber))

NHP4_df <- Plate13_VectorScan_Seroreactive_results_list[["I4"]] %>%
  mutate(
    NHP      = "NHP4",
    AANumber = DENV4_peptides$AANumber[match(id, DENV4_peptides$id)]
  ) %>%
  filter(!is.na(AANumber))

all_NHP <- bind_rows(NHP1_df, NHP2_df, NHP4_df) %>%
  pivot_longer(
    cols      = c(Early_v_Pre_Difference, Late_v_Pre_Difference),
    names_to  = "Timepoint",
    values_to = "FoldChange"
  ) %>%
  mutate(
    Timepoint = ifelse(Timepoint == "Early_v_Pre_Difference",
                       "Early hit", "Late hit"),
    # make a combined key so each NHP×timepoint can have its own colour
    NHP_Time  = interaction(NHP, Timepoint, drop = TRUE)
  )

cols <- c(
  "NHP1.Early hit" = "#96362E",
  "NHP1.Late hit"  = "#96369E",
  "NHP2.Early hit" = "#CB713C",
  "NHP2.Late hit"  = "#CB719C",
  "NHP4.Early hit" = "#A6C392",
  "NHP4.Late hit"  = "#395E12"
)

vlines <- c(0, 114, 280, 775, 1127, 1345, 1475, 2093, 2220, 2243, 2491, 3391)

ggplot(all_NHP, aes(x = AANumber, y = (FoldChange),
                    colour = NHP_Time)) +
  geom_point(alpha = 0.6, size = 1.5) +
  scale_color_manual(values = cols,
                     name   = "Timepoint",
                     labels = c("NHP1.Early hit" = "NHP1 Early",
                                "NHP1.Late hit"  = "NHP1 Late",
                                "NHP2.Early hit" = "NHP2 Early",
                                "NHP2.Late hit"  = "NHP2 Late",
                                "NHP4.Early hit" = "NHP4 Early",
                                "NHP4.Late hit"  = "NHP4 Late")) +
  facet_wrap(~ NHP, ncol = 1,  scales = "free_y") +
  labs(
    x = "AANumber",
    y = "Fold change RPK (Post-infection+0.1 / pre-infection+0.1)"
  ) +
  theme_minimal() +
  theme(
    legend.position       = "right",
    panel.grid            = element_blank(),
    legend.box.background = element_rect(color = "black", size = 0.25),
    panel.border          = element_rect(color = "black", fill = NA, size = 0.25)
  ) +
  geom_vline(xintercept = vlines,
             linetype   = "dashed",
             color      = "black",
             size       = 0.2)
```

Identify serotype/strain specific peptides 

Benchmarking analysis: 

```{r}
for (threshold in seq(50, 100, by = 5)) {
  
  DENV1_Specific <- VectorScan_Dengue_PercentIDtoSerotypes
  DENV1_Specific <- DENV1_Specific %>%
    filter(DENV1_Percent >= threshold) %>%
    inner_join(DENV1_peptides, by = 'id') %>%
    filter(V7 == 1, V8 == 56, !is.na(AANumber))

  df_long <- DENV1_Specific %>%
    pivot_longer(
      cols = c(DENV1_Percent, DENV2_Percent, DENV4_Percent),
      names_to = "variable",
      values_to = "value"
    )

  p <- ggplot(df_long, aes(x = variable, y = value, color = variable)) +
    geom_boxplot(lwd=1.5, show.legend = FALSE) +
    scale_color_manual(values = c(
      DENV1_Percent = "#96362E",
      DENV2_Percent = "#CB713C",
      DENV4_Percent = "#A6C392"
    )) +
    theme_minimal(base_size = 28) +
    labs(
      title = paste("Threshold \u2265", threshold),
      x = "Serotype",
      y = "Percent Identity",
      color = "Serotype"
    )+
    scale_x_discrete(labels=c("DENV1","DENV2","DENV4"))

  print(p)
}
```

```{r}
for (threshold in seq(50, 100, by = 5)) {
  
  DENV2_Specific <- VectorScan_Dengue_PercentIDtoSerotypes
  DENV2_Specific <- DENV2_Specific %>%
    filter(DENV2_Percent >= threshold) %>%
    inner_join(DENV2_peptides, by = 'id') %>%
    filter(V7 == 1, V8 == 56, !is.na(AANumber))

  df_long <- DENV2_Specific %>%
    pivot_longer(
      cols = c(DENV1_Percent, DENV2_Percent, DENV4_Percent),
      names_to = "variable",
      values_to = "value"
    )

  p <- ggplot(df_long, aes(x = variable, y = value, color = variable)) +
    geom_boxplot(lwd=1.5, show.legend = FALSE) +
    scale_color_manual(values = c(
      DENV1_Percent = "#96362E",
      DENV2_Percent = "#CB713C",
      DENV4_Percent = "#A6C392"
    )) +
    theme_minimal(base_size = 28) +
    labs(
      title = paste("Threshold \u2265", threshold),
      x = "Serotype",
      y = "Percent Identity",
      color = "Serotype"
    )+
    scale_x_discrete(labels=c("DENV1","DENV2","DENV4"))

  print(p)
}
```


```{r}
for (threshold in seq(50, 100, by = 5)) {
  
  DENV4_Specific <- VectorScan_Dengue_PercentIDtoSerotypes
  DENV4_Specific <- DENV4_Specific %>%
    filter(DENV4_Percent >= threshold) %>%
    inner_join(DENV4_peptides, by = 'id') %>%
    filter(V7 == 1, V8 == 56, !is.na(AANumber))

  df_long <- DENV4_Specific %>%
    pivot_longer(
      cols = c(DENV1_Percent, DENV2_Percent, DENV4_Percent),
      names_to = "variable",
      values_to = "value"
    )

  p <- ggplot(df_long, aes(x = variable, y = value, color = variable)) +
    geom_boxplot(lwd=1.5, show.legend = FALSE) +
    scale_color_manual(values = c(
      DENV1_Percent = "#96362E",
      DENV2_Percent = "#CB713C",
      DENV4_Percent = "#A6C392"
    )) +
    theme_minimal(base_size = 28) +
    labs(
      title = paste("Threshold \u2265", threshold),
      x = "Serotype",
      y = "Percent Identity",
      color = "Serotype"
    )+
    scale_x_discrete(labels=c("DENV1","DENV2","DENV4"))

  print(p) 
}
```

For the winning benchmarks (>85% to 1 strain and <80% to the others) 

```{r}
DENV1_Specific <- inner_join(VectorScan_Dengue_PercentIDtoSerotypes, DENV1_peptides, by = 'id')
DENV1_Specific <- DENV1_Specific[as.logical(DENV1_Specific$V7 == 1 & DENV1_Specific$V8 == 56),]
DENV1_Specific <- DENV1_Specific[as.logical(DENV1_Specific$DENV1_Percent >= 85 & DENV1_Specific$DENV2_Percent < 80 & DENV1_Specific$DENV4_Percent < 80),]
DENV1_Specific <- DENV1_Specific %>%  filter(!is.na(AANumber))

df_long <- DENV1_Specific %>%
  pivot_longer(
    cols = c(DENV1_Percent, DENV2_Percent, DENV4_Percent),
    names_to = "variable",
    values_to = "value"
  ) 

p <- ggplot(df_long, aes(x = variable, y = value, color = variable)) +
  geom_boxplot() +
  scale_color_manual(values = c(
    DENV1_Percent = "#96362E",
    DENV2_Percent = "#CB713C",
    DENV4_Percent = "#A6C392"
  )) +
  theme_minimal() +
  labs(
    title = paste("% Identity to each strain among 'DENV1-specific' peptides"),
    x = "Serotype",
    y = "Percent Identity",
    color = "Serotype"
  )

print(p)  

DENV2_Specific <- inner_join(VectorScan_Dengue_PercentIDtoSerotypes, DENV2_peptides, by = 'id')
DENV2_Specific <- DENV2_Specific[as.logical(DENV2_Specific$V7 == 1 & DENV2_Specific$V8 == 56),]
DENV2_Specific <- DENV2_Specific[as.logical(DENV2_Specific$DENV1_Percent < 80 & DENV2_Specific$DENV2_Percent >= 85 & DENV2_Specific$DENV4_Percent < 80),]
DENV2_Specific <- DENV2_Specific %>%  filter(!is.na(AANumber))

df_long <- DENV2_Specific %>%
  pivot_longer(
    cols = c(DENV1_Percent, DENV2_Percent, DENV4_Percent),
    names_to = "variable",
    values_to = "value"
  )

p <- ggplot(df_long, aes(x = variable, y = value, color = variable)) +
  geom_boxplot() +
  scale_color_manual(values = c(
    DENV1_Percent = "#96362E",
    DENV2_Percent = "#CB713C",
    DENV4_Percent = "#A6C392"
  )) +
  theme_minimal() +
  labs(
    title = paste("% Identity to each strain among 'DENV2-specific' peptides"),
    x = "Serotype",
    y = "Percent Identity",
    color = "Serotype"
  )

print(p)

DENV4_Specific <- inner_join(VectorScan_Dengue_PercentIDtoSerotypes, DENV4_peptides, by = 'id')
DENV4_Specific <- DENV4_Specific[as.logical(DENV4_Specific$V7 == 1 & DENV4_Specific$V8 == 56),]
DENV4_Specific <- DENV4_Specific[as.logical(DENV4_Specific$DENV1_Percent < 80 & DENV4_Specific$DENV2_Percent < 80 & DENV4_Specific$DENV4_Percent >= 85),]
DENV4_Specific <- DENV4_Specific %>%  filter(!is.na(AANumber))

df_long <- DENV4_Specific %>%
  pivot_longer(
    cols = c(DENV1_Percent, DENV2_Percent, DENV4_Percent),
    names_to = "variable",
    values_to = "value"
  )

p <- ggplot(df_long, aes(x = variable, y = value, color = variable)) +
  geom_boxplot() +
  scale_color_manual(values = c(
    DENV1_Percent = "#96362E",
    DENV2_Percent = "#CB713C",
    DENV4_Percent = "#A6C392"
  )) +
  theme_minimal() +
  labs(
    title = paste("% Identity to each strain among 'DENV4-specific' peptides"),
    x = "Serotype",
    y = "Percent Identity",
    color = "Serotype"
  )

print(p)  
```

```{r} 
Strain_Specific <- rbind(DENV1_Specific, DENV2_Specific, DENV4_Specific)
    
Strain_Specific <- Strain_Specific[!apply(Strain_Specific, 1, function(x) all(is.na(x))), ]
Strain_Specific[is.na(Strain_Specific)] <- 0

write_xlsx(Strain_Specific, "/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision/NHP/Strain_Specific.xlsx")

Strain_Specific <- read_xlsx("/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision/NHP/Strain_Specific.xlsx")
```

```{r}
df1 <- DENV1_Specific
df2 <- DENV2_Specific
df4 <- DENV4_Specific

combined_data <- bind_rows(
  df1 %>% mutate(Source = "DENV1"),
  df2 %>% mutate(Source = "DENV2"),
  df4 %>% mutate(Source = "DENV4")
)

combined_data$Source <- as.factor(combined_data$Source)

# Create the density plot
plot <- ggplot(combined_data, aes(x = AANumber, fill = Source)) +
  geom_density(alpha = 0.5, adjust = 0.05) +  
  labs(title = "Density Plot of all strain-specific peptides",
       x = "AANumber",
       y = "Density",
       fill = "Source") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0, max(combined_data$AANumber, na.rm = TRUE), by = 100)) + 
  scale_fill_manual(values = c("DENV1" = "#96362E", "DENV2" = "#CB713C", "DENV4" = "#A6C392")) +
      geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 114, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 280, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 775, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 1127, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 1345, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 1475, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 2093, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 2220, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 2243, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 2491, linetype = "dashed", color = "black", size = 0.2) + 
  geom_vline(xintercept = 3391, linetype = "dashed", color = "black", size = 0.2) +
  theme(legend.position = c(.85, .85), 
        panel.grid = element_blank(),
        panel.border = element_rect(color = 'black', fill = NA, size = .25),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) 

print(plot)
```

```{r}
# To get 2H

NHP1_Hits <- Plate13_VectorScan_Seroreactive_results_list[["I1"]]
NHP1_Hits <- NHP1_Hits[as.logical(NHP1_Hits$Species == "DV"),]
NHP1_Hits <- NHP1_Hits[as.logical(NHP1_Hits$EarlyImmune_seropositive=="1" | NHP1_Hits$LateImmune_seropositive=="1"),]
NHP1_Hits <- inner_join(NHP1_Hits, VectorScan_Dengue_PercentIDtoSerotypes, by = 'id')

NHP2_Hits <- Plate13_VectorScan_Seroreactive_results_list[["I2"]]
NHP2_Hits <- NHP2_Hits[as.logical(NHP2_Hits$Species == "DV"),]
NHP2_Hits <- NHP2_Hits[as.logical(NHP2_Hits$EarlyImmune_seropositive=="1" | NHP2_Hits$LateImmune_seropositive=="1"),]
NHP2_Hits <- inner_join(NHP2_Hits, VectorScan_Dengue_PercentIDtoSerotypes, by = 'id')

NHP4_Hits <- Plate13_VectorScan_Seroreactive_results_list[["I4"]]
NHP4_Hits <- NHP4_Hits[as.logical(NHP4_Hits$Species == "DV"),]
NHP4_Hits <- NHP4_Hits[as.logical(NHP4_Hits$EarlyImmune_seropositive=="1" | NHP4_Hits$LateImmune_seropositive=="1"),]
NHP4_Hits <- inner_join(NHP4_Hits, VectorScan_Dengue_PercentIDtoSerotypes, by = 'id')


hits_list <- list(
  NHP1 = NHP1_Hits,
  NHP2 = NHP2_Hits,
  NHP4 = NHP4_Hits
)

serotypes <- c("DENV1", "DENV2", "DENV4")

results <- data.frame()   

for (animal in names(hits_list)) {
  df_hits <- hits_list[[animal]]
  
  for (sero in serotypes) {
    others <- setdiff(serotypes, sero)
    
    cond_target  <- df_hits[[paste0(sero, "_Percent")]] >= 85
    cond_other1  <- df_hits[[paste0(others[1], "_Percent")]] < 80
    cond_other2  <- df_hits[[paste0(others[2], "_Percent")]] < 80
    temp1 <- sum(cond_target & cond_other1 & cond_other2, na.rm = TRUE)

    temp2 <- sum(Strain_Specific[[paste0(sero, "_Percent")]] >= 85, na.rm = TRUE) - temp1
    temp3 <- nrow(df_hits) - temp1
    temp4 <- nrow(VectorScan_Dengue_PercentIDtoSerotypes) - temp1 - temp2 - temp3
    
    contingency_table <- matrix(c(temp1, temp2,
                                  temp3, temp4),
                                nrow = 2,
                                byrow = TRUE,
                                dimnames = list(
                                  c(paste0(sero, "-Specific"), paste0("Not ", sero, "-Specific")),
                                  c("Hit", "Not hit")
                                ))
    
    ft <- fisher.test(contingency_table)

    results <- rbind(
      results,
      data.frame(
        Animal    = animal,
        Serotype  = sero,
        temp1     = temp1,
        temp2     = temp2,
        temp3     = temp3,
        temp4     = temp4,
        OddsRatio = unname(ft$estimate),
        Pvalue    = ft$p.value,
        ConfLow   = ft$conf.int[1],
        ConfHigh  = ft$conf.int[2],
        stringsAsFactors = FALSE
      )
    )
  }
}

results$Pvalue_adj <- p.adjust(results$Pvalue, method = "bonferroni")

View(results)
```