```{r}
# Load relevant libraries 
library(Biostrings)
library('dplyr')
library('corrplot')
library('writexl')
library('readxl')
library('seqinr')
library(ggplot2)
library(gridExtra)
library(ggfortify)
library(pheatmap)
library(Biostrings)
library(tidyverse)
library(igraph)
library(RColorBrewer)
```

```{r}
setwd('/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision')
VectorScan <- read_xlsx("VectorScan_Library_1_2.xlsx") ## Or file name of the relevant file that contains the library information

setwd('/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Manuscript_1/Revision')
VectorScan_cleaned <- read_xlsx("VectorScan_cleaned.xlsx")
```

PLATE 23
----
Read 1 Trim: CAGGTGTGATGCTCGGGGATCCAGGAATTCGGAGCGGT
Read 2 Trim: GCTTATCGTCGTCATCCTTGTAATCGCGGCCGCAAGCTTGTCGAGTGCAGTG

cd '/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Phage Display/VectorScan/Sequencing data/BauerCore_Plate23'

Cut off the first part so that only the actual peptide part is there:
for fq in *R1_001.fastq.gz; do cutadapt -g CAGGTGTGATGCTCGGGGATCCAGGAATTCGGAGCGGT -o ${fq%%.*}.cut.fastq.gz $fq; done 
for fq in *R2_001.fastq.gz; do cutadapt -g GCTTATCGTCGTCATCCTTGTAATCGCGGCCGCAAGCTTGTCGAGTGCAGTG -o ${fq%%.*}.cut.fastq.gz $fq; done 


```{r}
setwd('/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Phage Display/VectorScan/Sequencing data/BauerCore_Plate23')

Bowtie_fasta <- data.frame(id = VectorScan$id, Seq = VectorScan$'DNA Sequence')

# Create an AAStringSet object
seqs <- AAStringSet(Bowtie_fasta$Seq)
  # Add names from the sequence header column
names(seqs) <- paste0(Bowtie_fasta$id)
writeXStringSet(seqs, filepath ="VectorScan_Bowtie.fasta")
```

Make the bowtie2 index: 
bowtie2-build -f VectorScan_Bowtie.fasta VectorScan_Bowtie

align_reads.sh -- 
#!/bin/bash
# Define a function that processes a pair of FASTQ files
align_paired_reads() {
  base=${1%_R1_001.cut.fastq.gz}
  fq1="${base}_R1_001.cut.fastq.gz"
  fq2="${base}_R2_001.cut.fastq.gz"
  # Run Bowtie2 and redirect standard output and error
  bowtie2 -x VectorScan_Bowtie --very-sensitive -1 "$fq1" -2 "$fq2" -S "${base}.sam" 2>&1 | tee "${base}_bowtie2.log"
}
# Export the function to be used by parallel
export -f align_paired_reads
# Find all R1 files and pass them to GNU Parallel
parallel align_paired_reads ::: *_R1_001.cut.fastq.gz

Back to terminal --

chmod +x align_reads.sh
./align_reads.sh

 
Turn into count files
for i in *.sam; do samtools view -bS $i > ${i%.*}.bam; done
for i in *.bam; do samtools sort $i -o ${i%.*}.sorted.bam; done
for i in *.sorted.bam; do samtools index $i; done
for i in *.sorted.bam; do samtools idxstats $i | cut -f 1,3 | gsed -e'/^\*\t/d' -e'1 i id\t'${i%%.*}| tr "\\t" "," > ${i%%.*}.count.csv; done


[main_samview] fail to read the header from "P23-BITE64-Day44-D01_S123_L007.sam".  -- Fixed
[main_samview] fail to read the header from "P23-BITE66-Day0-D05_S126_L007.sam".  --  Fixed
[main_samview] fail to read the header from "P23-BITE66-Day44-G08_S162_L007.sam". -- Fixed 
[main_samview] fail to read the header from "P23-BITE68-Day0-A03_S91_L007.sam". -- Fixed 
[main_samview] fail to read the header from "P23-BITE68-Day0-E12_S143_L007.sam". -- In Progress

**
for fq in P23-BITE64-Day44-D01_S123_L007_R2_001.fastq.gz; do cutadapt -g GCTTATCGTCGTCATCCTTGTAATCGCGGCCGCAAGCTTGTCGAGTGCAGTG -o ${fq%%.*}.cut.fastq.gz $fq; done 

   bowtie2 -x VectorScan_Bowtie --very-sensitive -1 "P23-BITE64-Day44-D01_S123_L007_R1_001.cut.fastq.gz" -2 "P23-BITE64-Day44-D01_S123_L007_R2_001.cut.fastq.gz" -S "P23-BITE64-Day44-D01_S123_L007.sam" 2>&1 | tee "P23-BITE64-Day44-D01_S123_L007_bowtie2.log"
   
 **
for fq in  P23-BITE66-Day0-D05_S126_L007_R1_001.fastq.gz; do cutadapt -g CAGGTGTGATGCTCGGGGATCCAGGAATTCGGAGCGGT -o ${fq%%.*}.cut.fastq.gz $fq; done 
 
  bowtie2 -x VectorScan_Bowtie --very-sensitive -1 "P23-BITE66-Day0-D05_S126_L007_R1_001.cut.fastq.gz" -2 "P23-BITE66-Day0-D05_S126_L007_R2_001.cut.fastq.gz" -S "P23-BITE66-Day0-D05_S126_L007.sam" 2>&1 | tee "P23-BITE66-Day0-D05_S126_L007_bowtie2.log"

**
for fq in  P23-BITE66-Day44-G08_S162_L007_R1_001.fastq.gz; do cutadapt -g CAGGTGTGATGCTCGGGGATCCAGGAATTCGGAGCGGT -o ${fq%%.*}.cut.fastq.gz $fq; done 

  bowtie2 -x VectorScan_Bowtie --very-sensitive -1 "P23-BITE66-Day44-G08_S162_L007_R1_001.cut.fastq.gz" -2 "P23-BITE66-Day44-G08_S162_L007_R2_001.cut.fastq.gz" -S "P23-BITE66-Day44-G08_S162_L007.sam" 2>&1 | tee "P23-BITE66-Day44-G08_S162_L007_bowtie2.log"
   
**
for fq in  P23-BITE68-Day0-A03_S91_L007_R1_001.fastq.gz; do cutadapt -g CAGGTGTGATGCTCGGGGATCCAGGAATTCGGAGCGGT -o ${fq%%.*}.cut.fastq.gz $fq; done 
 
  bowtie2 -x VectorScan_Bowtie --very-sensitive -1 "P23-BITE68-Day0-A03_S91_L007_R1_001.cut.fastq.gz" -2 "P23-BITE68-Day0-A03_S91_L007_R2_001.cut.fastq.gz" -S "P23-BITE68-Day0-A03_S91_L007.sam" 2>&1 | tee "P23-BITE68-Day0-A03_S91_L007_bowtie2.log"

**
for fq in  P23-BITE68-Day0-E12_S143_L007_R1_001.fastq.gz; do cutadapt -g CAGGTGTGATGCTCGGGGATCCAGGAATTCGGAGCGGT -o ${fq%%.*}.cut.fastq.gz $fq; done 

  bowtie2 -x VectorScan_Bowtie --very-sensitive -1 "P23-BITE68-Day0-E12_S143_L007_R1_001.cut.fastq.gz" -2 "P23-BITE68-Day0-E12_S143_L007_R2_001.cut.fastq.gz" -S "P23-BITE68-Day0-E12_S143_L007.sam" 2>&1 | tee "P23-BITE68-Day0-E12_S143_L007_bowtie2.log"


Turn into count files
for i in *.sam; do samtools view -bS $i > ${i%.*}.bam; done
for i in *.bam; do samtools sort $i -o ${i%.*}.sorted.bam; done
for i in *.sorted.bam; do samtools index $i; done
for i in *.sorted.bam; do samtools idxstats $i | cut -f 1,3 | gsed -e'/^\*\t/d' -e'1 i id\t'${i%%.*}| tr "\\t" "," > ${i%%.*}.count.csv; done

Combine all the count files together 
paste -d ',' *.count.csv > 2025_04_16_VectorScan_Plate23_counts.csv

Only including the BITE samples for analysis in this manuscript, so the relevant samples have been excised from this .csv file and put into a new one for public viewing 
2025_04_16_VectorScan_Plate23_BITE_counts.csv

```{r}
Plate23_VectorScan_BITE_counts <- read.csv("/Users/melodi/Library/CloudStorage/OneDrive-SharedLibraries-HarvardUniversity/The Antibody Observatory (ABO) - Documents/Phage Display/VectorScan/Sequencing data/BauerCore_Plate23/2025_04_16_VectorScan_Plate23_BITE_counts.csv")

cor_matrix <- cor(Plate23_VectorScan_BITE_counts[,2:ncol(Plate23_VectorScan_BITE_counts)],Plate23_VectorScan_BITE_counts[,2:ncol(Plate23_VectorScan_BITE_counts)], method = "pearson")
corrplot(cor_matrix, method="shade", tl.cex = 0.4, tl.col = "black", col=COL2('RdBu'))
```

Remove BITE-61 due to low counts

```{r}
cols_to_remove <- grepl("BITE61", colnames(Plate23_VectorScan_BITE_counts))
Plate23_VectorScan_BITE_counts <- Plate23_VectorScan_BITE_counts[,!cols_to_remove]
```

```{r}
selected_PBS_columns <- grep("PBS", names(Plate23_VectorScan_BITE_counts), value = TRUE)
Plate23_counts_PBS <- Plate23_VectorScan_BITE_counts[, selected_PBS_columns]

Plate23_PBS_RPK <- sweep(Plate23_counts_PBS, 2, colSums(Plate23_counts_PBS), FUN = "/") * 1e5
Plate23_PBS_RPK$mean <-  apply(Plate23_PBS_RPK, 1, mean) 
Plate23_PBS_RPK$stdev <-  apply(Plate23_PBS_RPK, 1, sd) 
Plate23_PBS_RPK$LOD <- Plate23_PBS_RPK$mean + 5*Plate23_PBS_RPK$stdev
```

```{r}
Plate23_BITE_counts <- Plate23_VectorScan_BITE_counts[,2:ncol(Plate23_VectorScan_BITE_counts)]

colnames(Plate23_BITE_counts) <- c('BITE60_Day0','BITE60_Day0','BITE60_Day44','BITE60_Day44','BITE62_Day0','BITE62_Day0','BITE62_Day44','BITE62_Day44','BITE63_Day0','BITE63_Day0','BITE63_Day44','BITE63_Day44','BITE64_Day0','BITE64_Day0','BITE64_Day44','BITE64_Day44','BITE65_Day0','BITE65_Day0','BITE65_Day44','BITE65_Day44','BITE66_Day0','BITE66_Day0','BITE66_Day44','BITE66_Day44','BITE68_Day0','BITE68_Day0','BITE68_Day44','BITE68_Day44','BITE69_Day0','BITE69_Day0','BITE69_Day44','BITE69_Day44','BITE70_Day0','BITE70_Day0','BITE70_Day44','BITE70_Day44','BITE71_Day0','BITE71_Day0','BITE71_Day44','BITE71_Day44','BITE73_Day0','BITE73_Day0','BITE73_Day44','BITE73_Day44','BITE88_Day0','BITE88_Day0','BITE88_Day44','BITE88_Day44','BITE90_Day0','BITE90_Day0','BITE90_Day44','BITE90_Day44','BITE94_Day0','BITE94_Day0','BITE94_Day44','BITE94_Day44')

colnames(Plate23_BITE_counts) <- make.unique(colnames(Plate23_BITE_counts))
```

```{r}
# Find the seroreactive peptides within each sample 

identifiers <- c('BITE60','BITE62','BITE63','BITE64','BITE65','BITE66','BITE68','BITE69','BITE70','BITE71','BITE73','BITE88','BITE90','BITE94')

Plate23_BITE_VectorScan_All_results_list <- list()
Plate23_BITE_VectorScan_Seroreactive_results_list <- list()
Plate23_BITE_VectorScan_Discordance_results_list <-  list()
Plate23_BITE_VectorScan_ConcordantPeptides_results_list <- list()
discordance_temp <- data.frame()

# Loop over each identifier
for (identifier in identifiers) {
  
  Day0_Rep1_col <- paste0(identifier, "_Day0")  
  Day0_Rep2_col <- paste0(identifier, "_Day0.1")  
  Day44_Rep1_col <- paste0(identifier, "_Day44")  
  Day44_Rep2_col <- paste0(identifier, "_Day44.1")  
  
  selected_PBS_columns <- grep("PBS", names(Plate23_VectorScan_BITE_counts), value = TRUE)
   
  selected_sample_columns <- c(Day0_Rep1_col, Day0_Rep2_col,
                       Day44_Rep1_col, Day44_Rep2_col) 
  
  Pt <- Plate23_BITE_counts[, selected_sample_columns]
  Pt <- cbind(Pt, Plate23_VectorScan_BITE_counts[, selected_PBS_columns])
  
  Pt$id <- VectorScan$id
  
  Pt$PBS_LOD <- Plate23_PBS_RPK$LOD

  # To compare between timepoints, first take the RPK for each sample 
  
  Pt$Day0_Rep1_RPK <- Pt[[Day0_Rep1_col]]/sum(Pt[[Day0_Rep1_col]])*1e5
  Pt$Day0_Rep2_RPK <- Pt[[Day0_Rep2_col]]/sum(Pt[[Day0_Rep2_col]])*1e5
  
  Pt$Day44_Rep1_RPK <- Pt[[Day44_Rep1_col]]/sum(Pt[[Day44_Rep1_col]])*1e5
  Pt$Day44_Rep2_RPK <- Pt[[Day44_Rep2_col]]/sum(Pt[[Day44_Rep2_col]])*1e5
  
  # To be seropositive, both replicates from that sample need to be above the noise threshold 
  # Also enforcing a count limit, where the peptide needs a count >= 5
  
  rep1_high <- (Pt$Day0_Rep1_RPK > Pt$PBS_LOD) &  (Pt[[Day0_Rep1_col]] >= 5)
  rep2_high <-  (Pt$Day0_Rep2_RPK > Pt$PBS_LOD)  &  (Pt[[Day0_Rep2_col]] >= 5)
  
  Pt$Day0_seropositive <- ifelse(rep1_high == 1 & rep2_high == 1, 1, 0)
  Pt$Day0_Discordant <- ifelse(Pt$Day0_seropositive == 0 & (rep1_high != rep2_high), 1, 0)
    
  rep1_high <- (Pt$Day44_Rep1_RPK > Pt$PBS_LOD) &  (Pt[[Day44_Rep1_col]] >= 5)
  rep2_high <-  (Pt$Day44_Rep2_RPK > Pt$PBS_LOD)  &  (Pt[[Day44_Rep2_col]] >= 5)
  
  Pt$Day44_seropositive <- ifelse(rep1_high == 1 & rep2_high == 1, 1, 0)
  Pt$Day44_Discordant <- ifelse(Pt$Day44_seropositive == 0 & (rep1_high != rep2_high), 1, 0)
  
  Pt$Discordant_in_both <- ifelse(Pt$Day0_Discordant == 1 & Pt$Day44_Discordant == 1, 1, 0)
  
  discordance_temp <- data.frame(Day0 = sum(Pt$Day0_Discordant), Day44 = sum(Pt$Day44_Discordant), Both = sum(Pt$Discordant_in_both))
 
  Plate23_BITE_VectorScan_Discordance_results_list[[identifier]] <- discordance_temp
  
  Plate23_BITE_VectorScan_All_results_list[[identifier]] <- Pt
    
  # Limit the peptides to the ones in the library that do not have long GS linkers and have representation in the original library
  # The number of peptides in this cleaned library (VectorScan_cleaned) should be the denominator for all future Fishers tests
  
  Pt <- inner_join(Pt, VectorScan_cleaned, by = 'id')
  
  Pt$ForAlignment <- paste0(">", Pt$id, "_", Pt$Species, " ", Pt$`AA Sequence`)
  
  # Want to limit the pool of peptides to ones that are concordant at both timepoints 
  
  Pt <- Pt[as.logical(Pt$Day0_Discordant == 0),]
  Pt <- Pt[as.logical(Pt$Day44_Discordant == 0),]
  
  Pt$Day0_Avg <- (Pt$Day0_Rep1_RPK + Pt$Day0_Rep2_RPK)/2
  Pt$Day44_Avg <- (Pt$Day44_Rep1_RPK + Pt$Day44_Rep2_RPK)/2
  Pt$Day44vDay0_Difference <- (Pt$Day44_Avg+0.1) / (Pt$Day0_Avg+0.1)

  Pt$Day0_Seropositive_Average <- Pt$Day0_Avg * Pt$Day0_seropositive
  Pt$Day44_Seropositive_Average <- Pt$Day44_Avg * Pt$Day44_seropositive
  
  Plate23_BITE_VectorScan_ConcordantPeptides_results_list[[identifier]] <- Pt
  
  # Then want to limit the pool to ones that are seroreactive at one of the timepoints 
  
  Pt <- Pt[as.logical(Pt$Day0_seropositive == 1 | Pt$Day44_seropositive == 1),]
  
  Plate23_BITE_VectorScan_Seroreactive_results_list[[identifier]] <- Pt
}
```

```{r}
# Find the discordance rates for the Supp
discordance_df <- bind_rows(Plate23_BITE_VectorScan_Discordance_results_list, .id = "source_df")
```

```{r}
Plate23_BITE_Day0_Seropositive_RPKs <- Plate23_BITE_VectorScan_ConcordantPeptides_results_list %>%
  map(~ dplyr::select(.x, id, Day0_Seropositive_Average)) %>% 
      bind_rows(.id = "Sample") %>%
          pivot_wider(
            names_from = Sample, 
            values_from = Day0_Seropositive_Average, 
            values_fill = 0  
          )

colnames(Plate23_BITE_Day0_Seropositive_RPKs) <- c('id', 'BITE60_Day0','BITE62_Day0','BITE63_Day0','BITE64_Day0','BITE65_Day0','BITE66_Day0','BITE68_Day0','BITE69_Day0','BITE70_Day0','BITE71_Day0','BITE73_Day0','BITE88_Day0','BITE90_Day0','BITE94_Day0')

Plate23_BITE_Day44_Seropositive_RPKs <- Plate23_BITE_VectorScan_ConcordantPeptides_results_list %>%
  map(~ dplyr::select(.x, id, Day44_Seropositive_Average)) %>% 
      bind_rows(.id = "Sample") %>%
          pivot_wider(
            names_from = Sample, 
            values_from = Day44_Seropositive_Average, 
            values_fill = 0  
          )

colnames(Plate23_BITE_Day44_Seropositive_RPKs) <- c('id', 'BITE60_Day44','BITE62_Day44','BITE63_Day44','BITE64_Day44','BITE65_Day44','BITE66_Day44','BITE68_Day44','BITE69_Day44','BITE70_Day44','BITE71_Day44','BITE73_Day44','BITE88_Day44','BITE90_Day44','BITE94_Day44')

Plate23_BITE_BothTimepoints_Seropositive_RPKs <- full_join(Plate23_BITE_Day0_Seropositive_RPKs, Plate23_BITE_Day44_Seropositive_RPKs)
```

```{r}
# Can't save because some of the columns are tibbles
# to fix that: 

Plate23_BITE_BothTimepoints_Seropositive_RPKs_df <- Plate23_BITE_BothTimepoints_Seropositive_RPKs

is_df_col <- vapply(Plate23_BITE_BothTimepoints_Seropositive_RPKs_df, is.data.frame, logical(1))
for (nm in names(Plate23_BITE_BothTimepoints_Seropositive_RPKs_df)[is_df_col]) {
  Plate23_BITE_BothTimepoints_Seropositive_RPKs_df[[nm]] <- Plate23_BITE_BothTimepoints_Seropositive_RPKs_df[[nm]][[1]]
}

write_xlsx(Plate23_BITE_BothTimepoints_Seropositive_RPKs_df, "Plate23_BITE_BothTimepoints_Seropositive_RPKs_df.xlsx")
```

```{r}
# To check seroprevalence rate of particular peptides 

peptide <- "174749"
temp <- Plate23_BITE_Day0_Seropositive_RPKs[as.logical(Plate23_BITE_Day0_Seropositive_RPKs$id == peptide),]
sum(temp[,2:ncol(temp)]>0)/14*100

temp <- Plate23_BITE_Day44_Seropositive_RPKs[as.logical(Plate23_BITE_Day44_Seropositive_RPKs$id == peptide),]
sum(temp[,2:ncol(temp)]>0)/14*100

temp <- Plate23_BITE_BothTimepoints_Seropositive_RPKs[as.logical(Plate23_BITE_BothTimepoints_Seropositive_RPKs$id == peptide),]
sum(temp[,2:ncol(temp)]>0)/28*100
```

```{r}
temp <- Plate23_BITE_BothTimepoints_Seropositive_RPKs  
temp <- inner_join(temp, VectorScan_cleaned, by = 'id')
temp <- temp[,2:29]
temp <- temp[as.logical(rowSums(temp) > 0),]
nrow(temp)

temp <- temp[, sort(names(temp))]
cor_matrix <- cor(temp,temp, method = "spearman")
corrplot(cor_matrix, method="shade", tl.cex = 0.4, tl.col = "black", col=COL2('RdBu'))
```

```{r}
# Looking at signal at a Group level from each of the individuals

group_vec <- sort(unique(VectorScan_cleaned$Group))

run_mw_for_df <- function(df, group_vec) {
  
  # Rank by the difference in Day 44 v Day 0 signal that was calculated in the code above 
  
  df <- df %>%
    arrange(-Day44vDay0_Difference)

  df$rank      <- seq_len(nrow(df))
  df$log2_diff <- log2(df$Day44vDay0_Difference)

  mw_results <- map_df(group_vec, function(sp) {

    # Label each peptide by the group it's a part of 
    df$flag <- (df$Group == sp)

    if (length(unique(df$flag)) < 2) {
      return(data.frame(
        Group = sp,
        W       = NA_real_,
        p_value = NA_real_
      ))
    }

    # Run the Mann-Whitney 
    test_res <- wilcox.test(
      log2_diff ~ flag,
      data = df,
      alternative = "less"
    )

    data.frame(
      Group = sp,
      W       = unname(test_res$statistic),
      p_value = test_res$p.value
    )
  })

  mw_results$Signif <- mw_results$p_value <= 0.05
  mw_results
}

Plate23_mw_results_all <- imap_dfr(
  Plate23_BITE_VectorScan_Seroreactive_results_list,
  ~ run_mw_for_df(.x, group_vec) %>%
      mutate(Sample = .y),  
  .id = NULL
)

# After you have one big data frame with every sample and group
Plate23_mw_Day44vDay0_results_all_Group <- Plate23_mw_results_all

# Do the p-adjustment for all the possible comparisons 
Plate23_mw_Day44vDay0_results_all_Group$padj_global <- p.adjust(Plate23_mw_Day44vDay0_results_all_Group$p_value, method = "BH")

Plate23_mw_Day44vDay0_results_all_Group$`-log10p` <- -log10(Plate23_mw_Day44vDay0_results_all_Group$padj_global)
Plate23_mw_Day44vDay0_results_all_Group$Significant <- Plate23_mw_Day44vDay0_results_all_Group$`-log10p` >=1.3
```

```{r}
temp <- Plate23_BITE_BothTimepoints_Seropositive_RPKs
temp <- inner_join(temp, VectorScan, by = 'id')
temp <- temp[as.logical(temp$Group == "Mosquito"),]
temp <- temp[as.logical(rowSums(temp[,2:29])>0),]

counts_of_interest <- data.frame(
  column = names(temp[,2:29]),
  n_counts  = colSums(temp[,2:29] > 0, na.rm = TRUE))

```

