Updated Jan 2026 -  Using the newer version of OrthoMCL (7.0 release)

Get the protein sequences used to make the vector portion of the library 

```{r}
Vector_Sequences <- readAAStringSet("Library_1_2_SignalP.faa")
```

Performed DIAMOND mapping to identify OrthoMCL entries for each protein.

```{r}
OrthoMCL_DIAMOND <- read_delim("2025_01_06_OrthoMCL_DIAMONDMapping.txt")
```

```{r}
paste0('Number of proteins without an Orthogroup label: ',  sum(OrthoMCL_DIAMOND$`OrthoMCL group id` == -1))
paste0('Number of proteins with an Orthogroup label: ',  sum(OrthoMCL_DIAMOND$`OrthoMCL group id` != -1))
```

Map the Orthogroup back to the proteins in VectorScan
```{r}
VectorScan_Vector_Orthogroups <- VectorScan

for(i in 1:nrow(OrthoMCL_DIAMOND)) {
#for(i in 1:100) {
  # Get the current Query sequence id
  query_id <- OrthoMCL_DIAMOND$`Query sequence id`[i]
  
  # Use str_detect to find matching descriptions
  matches <- str_detect(VectorScan_Vector_Orthogroups$Description, fixed(query_id))
  
  # Add columns from the matching OrthoMCL_DIAMOND row to VectorScan_Vector_Orthogroups
  if(any(matches)) {
    for(col_name in names(OrthoMCL_DIAMOND)) {
      if(col_name != "Query sequence id") {
        new_col_name <- paste0(col_name, "_from_Protein")
        if(!new_col_name %in% names(VectorScan_Vector_Orthogroups)) {
          VectorScan_Vector_Orthogroups[[new_col_name]] <- NA
        }
        VectorScan_Vector_Orthogroups[matches, new_col_name] <- OrthoMCL_DIAMOND[i, col_name]
      }
    }
  }
}
```

```{r}
VectorScan_Mosquito_Orthogroups <- VectorScan_Vector_Orthogroups[as.logical(VectorScan_Vector_Orthogroups$Group == "Mosquito"),]
```

Manually adding information for the peptides that didn't get an Orthogroup searched (i.e., the anopheles sequences taken from the Falciparome library)

```{r}
current_na <- VectorScan_Mosquito_Orthogroups[is.na(VectorScan_Mosquito_Orthogroups$`OrthoMCL group id_from_Protein`),]
```

```{r}
seqs <- AAStringSet(current_na$'AA Sequence')
names(seqs) <- paste0(current_na$id)

writeXStringSet(seqs, filepath = "current_na.fasta")
```

Performed DIAMOND mapping to identify OrthoMCL entries for each protein.

```{r}
na_DIAMOND <- read_delim("Falciparome_Anopheles_OrthoMCL_DIAMONDMapping.txt")
```

Map the Orthogroup back to the proteins in VectorScan
```{r}
na_DIAMOND$id <- as.numeric(na_DIAMOND$`Query sequence id`)

for(i in 1:nrow(na_DIAMOND)) {
  query_id <- na_DIAMOND$`Query sequence id`[i]
  
  # Use str_detect to find matching descriptions
  matches <- str_detect(VectorScan_Mosquito_Orthogroups$id, fixed(query_id))
  
  # Add columns from the matching OrthoMCL_DIAMOND row to VectorScan_Vector_Orthogroups
  if(any(matches)) {
    for(col_name in names(na_DIAMOND)) {
      if(col_name != "Query sequence id") {
        new_col_name <- paste0(col_name, "_from_Protein")
        if(!new_col_name %in% names(VectorScan_Mosquito_Orthogroups)) {
          VectorScan_Mosquito_Orthogroups[[new_col_name]] <- NA
        }
        VectorScan_Mosquito_Orthogroups[matches, new_col_name] <- na_DIAMOND[i, col_name]
      }
    }
  }
}
```

```{r}
VectorScan_Mosquito_Orthogroups <- VectorScan_Mosquito_Orthogroups[VectorScan_Mosquito_Orthogroups$id %in% VectorScan_cleaned$id, ]
```

```{r}
sum(VectorScan_Mosquito_Orthogroups$`OrthoMCL group id_from_Protein` == -1)
sum(VectorScan_Mosquito_Orthogroups$`OrthoMCL group id_from_Protein` != -1)
nrow(VectorScan_Mosquito_Orthogroups)
```
  
  
```{r}
write_xlsx(VectorScan_Mosquito_Orthogroups, 'VectorScan_Mosquito_Orthogroups.xlsx')
```
